\documentclass[11pt,a4paper,twoside]{article}
\input{myPackage.tex}
\title{SPT indices emerging from translation invariance in two-dimensional quantum spin systems}
\author{Tijl Jappens\footnote{Institute for Theoretical Physics, Katholieke Universiteit Leuven.}}
\date{\today}

\numberwithin{equation}{section}
\begin{document}
\maketitle 
\begin{abstract}
	We consider SPT-phases with on-site $G$ (where $G$ is any finite group) symmetry for two-dimensional quantum spin systems. We then impose translation invariance in one direction and observe that on top of the $H^3(G,\TT)$-valued index constructed in \cite{ogata2021h3gmathbb}, an additional $H^2(G,\TT)$-valued index emerges. We also show that if we impose translation invariance in two directions, on top of the expected $H^3(G,\TT)\oplus H^2(G,\TT)\oplus H^2(G,\TT)$ valued index, an additional $H^1(G,\TT)$-valued index emerges.
\end{abstract}
\section{Introduction}
In 2010, Chen, Gu and Wen \cite{chen_gu_wen_2011} introduced the notion of symmetry-protected topological phases of matter (SPT). They first considered one dimensional matrix product states and later on, Chen, Liu and Wen \cite{Chen_2011}, extended this to two dimensional projective entangled pair models. Afterwards, in \cite{Chen_2013} this was extended to other dimensions. This last reference used a setup involving so-called lattice nonlinear sigma models and provided an $H^{d+1}(G,U(1))$ valued index for any $d$-dimensional lattice nonlinear sigma model. Another possible setup in which one can define SPT phases is in quantum spin systems (defined in section \ref{sec:QuasiLocalC*Algebra}). In order to define SPT phases in this setting, one needs to fix a finite group $G$ with an on-site group action $g\mapsto U_g$ (with $g\in G$), defining a global group action $\beta_g$ (also defined in section \ref{sec:QuasiLocalC*Algebra}). A state $\omega$, is then called $G$-invariant, if $\omega\circ\beta_g=\omega$. Afterwards, one needs to impose a restriction on the space of states. We\footnote{There are other definitions possible like for instance the concept of invertible G-invariant states used in \cite{kapustin2021classification} or the unique gapped ground state of a G invariant interaction presented in the introduction of \cite{ogata2021h3gmathbb}.} ask that our states are short range entangled (SRE), see definition \ref{def:sre}. A state $\omega$ is short range entangled if there is a disentangler $\gamma$. This is a locally generated automorphism, produced by a one parameter family of interactions $\Phi\in\BB_{F_\phi}([0,1])$ ($\gamma=\gamma_{0;1}^\Phi$ as defined in section \ref{sec:Interactions}) satisfying that $\omega\circ\gamma$ is a product state. Combining these two definitions, we say that $\omega$ is an SPT state if it is short range entangled and $G$-invariant.
\\\\
One then defines an equivalence relation on these SPT states by saying that $\omega_1$ is equivalent to $\omega_2$ with respect to the on site group action $U$ if there exists a $G$-invariant one parameter family of interactions $\Phi\in\BB_{F_\phi}([0,1])$ such that $\omega_1\circ\gamma^\Phi_{0;1}=\omega_2$ (again, see section \ref{sec:Interactions} for the definitions). One can then extend this equivalence to the stronger notion of being stably equivalent. This goes as follows: one defines an operation called stacking that takes two SPT states $\omega_1$ and $\omega_2$ and outputs a third one $\omega_1\otimes_{\text{stack}}\omega_2$ (and similarly for the group action). This $\otimes_\text{stack}$ is defined in section \ref{sec:QuasiLocalC*Algebra}. In short, it is the tensor product at the level of the on site Hilbert space. One then defines another equivalence relation and says that two SPT states with on site group actions $(\omega_1,U_1)$ and $(\omega_2,U_2)$ are stably equivalent if and only if there exist trivial\footnote{A trivial state is a $G$-invariant product state that transforms trivially under the on site group action (see remark \ref{rem:NontrivialProductState}).} SPTs with their group actions, $(\phi_1,\tilde{U}_1)$ and $(\phi_2,\tilde{U}_2)$ and a ($G$ independent) unitary $V$ mapping between the respective on site Hilbert spaces\footnote{The reader can think of this $V$ as being a unitary transformation of the on site group action.}, such that
\begin{enumerate}
	\item $V^\dagger U_{1,g}\otimes \tilde{U}_{1,g}V=U_{2,g}\otimes \tilde{U}_{2,g}$ for all $g\in G$.
	\item $\omega_1\otimes_{\text{stack}}\phi_1\circ i_V$ (where $i_V$ is again defined in section \ref{sec:QuasiLocalC*Algebra}) is equivalent to $\omega_2\otimes_{\text{stack}}\phi_2$ with respect to the above on site group action.
\end{enumerate}
In one spatial dimension so called matrix product states (\cite{Chen_2011},\cite{pollman2012symmetry},\cite{schuch2011MatrixProduct}) can be used to construct non-trivial SPT states. Later on and more generally it was shown in \cite{ogata2019classification} that any $G$-invariant state satisfying the split property (this includes any SRE state) carries an $H^2(G,\TT)$-valued\footnote{By $H^n(G,\TT)$ we mean the n-th (Borel) group cohomology of $G$ with coefficients in the torus $\TT$ (seen as a (group) module under addition with trivial group action). For the definition of these group cohomology modules we refer to \cite{benson1991representations}.} index and that this index is constant on the (stable) equivalence classes. Later on in \cite{kapustin2021classification} it was then shown that this classification problem is complete (the index, seen as a map from the set of stable equivalence classes to $H^2(G,\TT)$ is injective.). In two spatial dimensions, more recently in \cite{ogata2021h3gmathbb}, it was proven there is an $H^3(G,\TT)$-valued index that is constant on the (stable) equivalence classes\footnote{In \cite{ogata2021h3gmathbb}, there is no mention of the stacking operation but using remark \ref{rem:StackingH3ValuedIndex} and remark \ref{rem:OnSiteUnitaryTransformationH3ValuedIndex}, one can clearly extend it to the stable equivalence class.}.
\\\\
We've used stacking to define the stable equivalence relation. Stacking however plays a more general role. It widely believed that it allows us to define an (abelian) group structure on the set of stable equivalence classes\footnote{The stacking with a trivial state will then be related to the identity of this group}. Although it is nowhere stated explicitly, the author thinks that the literature (like for example \cite{kapustin2021classification}) suggests the following conjecture:
\begin{conjecture}\label{conj:StableEquivGroupStructure}
	Let $S$ be the set of stable SPT classes for some fixed group and a fixed lattice. Let $*$ be the map
	\begin{equation}
		*:S^2\rightarrow S:(\expval{\omega_1,U_1}_{\sim},\expval{\omega_2,U_2}_{\sim})\mapsto \expval{\omega_1\otimes_\text{stack}\omega_2,U_1\otimes U_2}_{\sim}.
	\end{equation}
	Then $*$ is well defined (independent of the choice of representative) and $S$ together with the $*$ operation forms an abelian group.
\end{conjecture}
Before proceeding, we make three remarks on this conjecture:
\begin{enumerate}
	\item The claim that $*$ is well defined and abelian is trivial. Namely, by letting $i_V$ be the automorphism that exchanges the two algebras that are being stacked, one can exchange the order of the stacking freely. By using
	\begin{equation}
		\omega_1\circ\gamma^{\Phi_1}_{0;1}\otimes_\text{stack}\omega_2\circ\gamma^{\Phi_2}_{0;1}=(\omega_1\otimes_{\text{stack}}\omega_2)\circ\gamma^{\Phi_1\otimes\id+\id\otimes\Phi_2}_{0;1}\sim\omega_1\otimes_{\text{stack}}\omega_2,
	\end{equation}
	one can show that this is a well-defined map.
	\item A representative of the inverse is sometimes called a $G$-inverse.
	\item From a category point of view, if one assumes that this conjecture is true (for some subclass of groups that is a category), it is not hard to see that it gives rise to a contravariant functor from this category of groups to the category of abelian groups (say $S[G]$). More specifically, to each group morphism $f:G_1\rightarrow G_2$, one can find a group morphism $\tilde{f}:S[G_2]\rightarrow S[G_1]:\expval{\omega,U}_\sim\mapsto \expval{\omega,U\circ f}_\sim$ and this $\tilde{f}$ is indeed invariant on the choice of representative (if two states can be connected while preserving the symmetry action $\beta$, they can certainly be connected while preserving the symmetry $\beta\circ f$).
\end{enumerate}
In what follows, we will call $S$ with the above group structure the stable SPT classification. In this paper we consider the 2D case with the (stable) equivalence relation as presented here but with one notable difference. We will only consider states, interactions and on site symmetries that have a translation symmetry in one direction. There is a conjecture about the SPT classification of such states, see section 3.1.5.1 of \cite{xiong2019classification} for a more general and detailed exposition (which was partially based on \cite{Chen_2013}).
\begin{conjecture}\label{conj}
	The set of translation invariant SPTs under stable equivalence\footnote{In the stable equivalence relation for translation invariant states we ask that the on site symmetry is translation invariant and that any path connecting two states and each trivial state is not only G-invariant but also translation invariant.} also satisfies conjecture \ref{conj:StableEquivGroupStructure}. Let $g$ be the inclusion map from the space of 2d translation invariant SPT states to the more general set of 2d SPT states. Let $f$ be the map that takes a 1d SPT state and outputs a translation invariant 2d SPT state by taking the tensor product in the direction of the translation symmetry. The sequence
	\begin{equation}
		0\rightarrow\{\text{1d SPT states}\}\stackrel{f}{\rightarrow}\{\text{2d translation invariant SPT states}\}\stackrel{g}{\rightarrow}\{\text{2d SPT states}\}\rightarrow 0
	\end{equation}
	induces a sequence (of group morphisms) on the stable equivalence classes. By this we mean that the class of $f(\phi)$ only depends on the class of $\phi$ and similarly for $g$. Moreover this induced sequence is exact and split.
\end{conjecture}
Clearly this implies that
\begin{equation}
	\{\text{2d translation invariant SPT classification}\}\simeq \{\text{1d SPT classification}\}\oplus \{\text{2d SPT classification}\}.
\end{equation}
Since a 1d SPT state carries an $H^2(G,\TT)$ valued index and a 2d SPT state carries an $H^3(G,\TT)$ valued index, this means that 2d SPT states with a translation symmetry should carry an $H^2(G,\TT)\oplus H^3(G,\TT)$ valued index. This is consistent with the result of section XII of \cite{Chen_2013}.
\\\\
The first result of this paper is the construction of an $H^2(G,\TT)$ valued index (which we will denote by $\textrm{Index}$) on the space of translation invariant SPT states that is consistent with conjectures \ref{conj:StableEquivGroupStructure} and \ref{conj}. By being consistent with the conjecture it is meant (among other things) that, if $\textrm{Index}_1$ is the one dimensional SPT index from \cite{ogata2019classification}, then $\textrm{Index}(f(\omega))=\textrm{Index}_1(\omega)$ for any 1d SPT $\omega$. This construction highly relies on the objects that are present in the construction of the 2d SPT index in \cite{ogata2021h3gmathbb}.
\\\\
We also look at the case where there is a second translation symmetry (so the system is translation invariant in both $x$ and $y$ directions). For such systems there is the following conjecture conjecture (see again \cite{xiong2019classification} and \cite{Chen_2013}):
\begin{conjecture}\label{conj2}
	The space of SPTs, translation invariant in two directions under stable equivalence also satisfies conjecture \ref{conj:StableEquivGroupStructure}. Let $g$ be the inclusion map from the space of 2d SPT states that are translation invariant in both $x$ and $y$ directions to the more general set of 2d SPT states with translation invariance in the $x$ direction only. Let $f$ be the map that takes a 1d translation invariant SPT state and outputs a 2d SPT state that is translation invariant in both $x$ and $y$ directions by taking the tensor product in the $y$ direction. The sequence
	\begin{equation}
		0\rightarrow\left\{\begin{matrix}\text{1d translation invariant}\\ \text{SPT states}\end{matrix}\right\}\stackrel{f}{\rightarrow}\left\{\begin{matrix}\text{2d SPT states with two}\\ \text{translation symmetries}\end{matrix}\right\}\stackrel{g}{\rightarrow}\left\{\begin{matrix}\text{2d SPT states translation}\\ \text{invariant in $x$ direction}\end{matrix}\right\}\rightarrow 0
	\end{equation}
	induces a sequence (of group morphisms) on the stable equivalence classes. By this we mean that the class of $f(\phi)$ only depends on the class of $\phi$ and similarly for $g$. Moreover, this induced sequence is exact and split.
\end{conjecture}
Translation invariant SPT states in one spatial dimension are known to carry an $H^2(G,\TT)\oplus H^1(G,\TT)$ valued index (see appendix \ref{sec:OneDimensionalIndices}). From this and the last two conjectures, we expect there is an
\begin{equation}\label{eq:2TranslationsIntroduction}
	H^3(G,\TT)\oplus H^2(G,\TT)\oplus H^2(G,\TT)\oplus H^1(G,\TT)
\end{equation}
valued index. The first part of the index is just $\textrm{Index}_{2d}$. The following two parts can be related to the case of a single translation symmetry as follows. Let $\mu$ be the automorphism that rotates the lattice by 90° and let $\textrm{Index}(\omega)$ be the index as constructed before (this is the second part of \ref{eq:2TranslationsIntroduction}). The third part of the index is now given by $\textrm{Index}(\omega\circ\mu)$ (the state rotated by 90°). The last part of the index requires a different construction altogether. It can be thought of as being the charge in the Brillouin zone.
\\\\
A final remark:
\begin{remark}
	As noticed in \cite{Chen_2013}. The groups in which these indices take values can be concisely written out. Using that
	\begin{align}
	H^0(\ZZ,\TT)&\cong \TT& H^1(\ZZ,\TT)&\cong \TT& H^2(\ZZ,\TT)&\cong 0&H^3(\ZZ,\TT)&\cong 0
	\end{align}
	and inserting this into the K\"unneth formula for $\ZZ\times G$ gives
	\begin{align}
	H^2(\ZZ \times G,\TT)&\cong \bigoplus_{i=0}^2 H^i(\ZZ,\TT)\otimes H^{2-i}(G,\TT)\cong H^2(G,\TT)\oplus H^1(G,\TT)\\
	H^3(\ZZ \times G,\TT)&\cong \bigoplus_{i=0}^3 H^i(\ZZ,\TT)\otimes H^{3-i}(G,\TT)\cong H^3(G,\TT)\oplus H^2(G,\TT).
	\end{align}
	This result can in turn be used to work out the K\"unneth formula for $\ZZ^2\times G$
	\begin{equation}
	H^3(\ZZ^2\times G,\TT)\cong \bigoplus_{i=0}^3 H^i(\ZZ,\TT)\otimes H^{3-i}(\ZZ\times G,\TT)\cong H^3(G,\TT)\oplus H^2(G,\TT)\oplus H^2(G,\TT)\oplus H^1(G,\TT).
	\end{equation}
\end{remark}
The layout of this paper is as follows: First in section \ref{sec:Setup} we explain the setup, define the concept of locally generated automorphisms and give the algebraic definition of group cohomology. In section \ref{sec:Results_1} we state the two results for SRE states. In section \ref{sec:Results_2}, we state the first result using the weaker assumption \ref{assumption} and the second result using the weaker assumption \ref{assumption:2Translations}. It is using these weaker assumptions that we then prove the statements. Section \ref{sec:ProofFirstStatement} provides a proof of the first statement whereas section \ref{sec:TwoDirectionTraslationInvariance} provides a proof of the second statement. The results in this paper rely heavily on the methods that where developed in \cite{ogata2021h3gmathbb}.
\subsection*{Acknowledgements}
T.J. was supported in part by the FWO under grant G098919N.\\\\
We are grateful to the referees of Communications in Mathematical Physics for their constructive input during the review process. For example, we are very grateful for the proposed changes of lemma \ref{lem:SplittingOfUnitary} and the mistake in subsection \ref{sec:OneTranslationDirectionExample} (the previous assumption was too weak).
\subsection*{Data availability statement}
No new data were created or analyzed in this study. Data sharing is not applicable to this article.
\section{Setup and definitions}\label{sec:Setup}
\begin{remark}
	This paper is a shorter version of the ArXiv paper \cite{jappens2023spt} and will often refer to it for many of the proofs and some of the definitions.
\end{remark}
In this paper we work in the two dimensional lattice $\ZZ^2$. We will first need some specific subsets of $\ZZ^2$, so let
\begin{align}
	L&\defeq \left\{(x,y)\in\ZZ^2\left|x<0\right.\right\},&R&\defeq \left\{(x,y)\in\ZZ^2\left|x\geq 0\right.\right\}\\
	U&\defeq \left\{(x,y)\in\ZZ^2\left|y\geq 0\right.\right\},&D&\defeq \left\{(x,y)\in\ZZ^2\left|y<0\right.\right\}
\end{align}
be the left, right, upper and lower half planes respectively and let
\begin{equation}
	C_\theta\defeq \left\{(x,y)\in\ZZ^2\left|\tan(\theta)\leq\abs{\frac{y}{x}}\right.\right\}
\end{equation}
be the horizontal cone (the green area in figure \ref{fig:SetupWithQAutomorphism}). We will use $\tau$ to denote the bijection that moves every element of $\ZZ^2$ one site upward. Similarly we let $\nu$ denote the bijection that translates every element of $\ZZ^2$ by one site to the right. In what follows we will sometimes need to widen our cone or other subsets of $\ZZ^2$ vertically by one site. For this purpose we define $W$ such that for any $\Gamma\subset\ZZ^2$,
\begin{equation}
	W(\Gamma)\defeq \Gamma\cup\tau(\Gamma)\cup\tau^{-1}(\Gamma).
\end{equation}
For example, the red area in figure \ref{fig:SetupWithQAutomorphism} is $W(C_\theta)^c$. In the later part we will also need to rotate our lattice by $90^\circ$ (clockwise) so call $\mu$ the bijection on $\ZZ^2$ that does precisely this.\footnote{We will not discuss rotation invariant states in this paper. The $\mu$ is only defined to make certain constructions work.} Finally we will need to define the horizontal lines and the finite horizontal line
\begin{align}
	L_j&\defeq \{(i,j)|i\in\ZZ\}&L_j^n&\defeq \{(i,j)|i\in\ZZ\cap[-n,n]\}.
\end{align}
\subsection{Quasi local $C^*$-algebra}\label{sec:QuasiLocalC*Algebra}
The setup in this paper will be very similar to the setup in \cite{ogata2021h3gmathbb} and is just the standard setup for defining quantum spin systems. For the rest of this paper, take $d\in\NN_+$ arbitrary. This number will be called the on site dimension\footnote{In principle in the case were there is only one translation we can let $d$ be $x$-dependent but for simplicity let us take $d$ constant over the lattice.}. For each $z\in\ZZ^2$, let $\AA_{\{z\}}$ be an isomorphic copy of $\BB(\CC^d)$ (the bounded operators on $\CC^d$). In what follows, let $\mathfrak{G}_{\ZZ^2}$ be the set of finite subsets of $\ZZ^2$. For any $\Lambda\in\mathfrak{G}_{\ZZ^2}$, we set $\AA_\Lambda=\bigotimes_{z\in\Lambda}\AA_{\{z\}}$. We define the local algebra as $\AA_{\text{loc}}=\bigcup_{\Lambda\in \mathfrak{G}_{\ZZ^2}}\AA_{\Lambda}$ and define the quasi local $C^*$ algebra as the norm closure of the local algebra ($\AA=\overline{\AA_{\text{loc}}}$). Similarly, for any (possibly infinite) subset $\Gamma\subset\ZZ^2$ we set $\AA_{\text{loc},\Gamma}=\bigcup_{\Lambda\in \mathfrak{G}_{\Gamma}}\AA_{\Lambda}$ and $\AA_\Gamma=\overline{\AA_{\text{loc},\Gamma}}$.\\\\
Throughout this paper we will sometimes require a stronger form of locality than merely being in the norm completion of the local algebra. Specifically when $\Gamma=L_j$ is a horizontal line. We will say that an operator $A\in\AA_{L_j}$ is summable if and only if there exists a sequence $A_n\in\AA_{L_{j}^n}$ on the finite horizontal lines such that
\begin{equation}
	\sum_{i=0}^{\infty}\norm{A-A_n}<\infty.
\end{equation}
We will need to define some automorphisms on this algebra using the bijections defined previously. To this end, define the isomorphisms
\begin{align}
\tau&:\AA_\Gamma\rightarrow\AA_{\tau(\Gamma)}&\nu&:\AA_\Gamma\rightarrow\AA_{\nu(\Gamma)}&\mu&:\AA_\Gamma\rightarrow\AA_{\mu(\Gamma)}
\end{align}
as the translation upwards, the translation to the right and the right-handed rotation respectively. By construction, these isomorphisms are automorphisms if $\Gamma$ is taken to be $\ZZ^2$ (because $d$ is a constant throughout the lattice). Clearly if $\Gamma=\ZZ$ (by which we mean again the $x$-axis $(\ZZ,0)$) only one of these translation automorphisms descends to an automorphism on $\AA_{\ZZ}$. This automorphism is then also simply denoted as $\nu$.\\\\
We will need to define one additional set of automorphisms. For any set of unitaries $V_i\in\UU(\CC^d)$ (labelled by $i\in\ZZ^2$), we define the (unique) automorphism $i_V^\Gamma\in\Aut{\AA_\Gamma}$ (for all $\Gamma\subset \ZZ^2$) such that
\begin{equation}
i_V^\Gamma (A)=\Ad{\otimes_{i\in I} V_i}(A)
\end{equation}
for all $I\subset\Gamma$ finite and $A\in\AA_I$. More specifically, let $G$ be a finite group and let $U_i\in\hom(G,\UU(\AA_i))$ (for $i\in\ZZ^2$) be the on site group action. Let $\beta^\Gamma\in\hom(G,\Aut{\AA_\Gamma})$ (for any $\Gamma\subset\ZZ^2$) be such that
\begin{equation}
\beta^\Gamma_g(A)=i_{U(g)}^\Gamma=\Ad{\otimes_{i\in I} U_i(g)}(A)
\end{equation}
for any $g\in G$, $I\subset\Gamma$ finite and $A\in\AA_I$. Clearly, any unitary transformation of our representation $U(\cdot)\rightarrow V^\dagger U(\cdot) V$ induces a transformation of the group action $\beta_g\rightarrow i_{V}^{-1}\circ\beta_g\circ i_V$.\\\\
Throughout our paper when we are discussing translation invariance in the vertical direction we will ask that the group action is translation invariant in the vertical direction ($\tau\circ\beta_g^\Gamma=\beta_g^{\tau(\Gamma)}\circ\tau$). If we also have translation invariance in the horizontal direction, we will also ask that the group action be translation invariant in that direction as well ($\nu\circ\beta_g^\Gamma=\beta_g^{\nu(\Gamma)}\circ\nu$). As it turns out, in showing that the $H^1$-valued index is consistent with all the conjectures of the introduction, we will even require that the on site group action $U_i(g)$ is the same at each site. In what follows we will always assume this. This means that when we denote an on site symmetry action we merely have to give one representation $U\in\hom(G,\UU(\CC^d))$ and when we denote a unitary transformation of the on site Hilbert space we only have to give a single unitary $V\in \UU(\CC^d)$, we will use this notation frequently.\\\\
Clearly by construction there is a tensor product operation on this $C^*$ algebra in the sense that for any $\Gamma_1,\Gamma_2\subset\ZZ^2$ satisfying that $\Gamma_1\cap\Gamma_2=\emptyset$ we can define a bilinear, surjective map
\begin{equation}
\otimes:\AA_{\Gamma_1}\times\AA_{\Gamma_2}\rightarrow \AA_{\Gamma_1\cup\Gamma_2}.
\end{equation}
There is however a second tensor product operation on this $C^*$ algebra that we will use. We will call it the stacking operation. It is such that for any $\Gamma\subset\ZZ^2$ we define the bilinear, surjective map
\begin{equation}
	\otimes_{\text{stack}}:\AA_{\Gamma}\times\AA_{\Gamma}\rightarrow \AA^2_{\Gamma}
\end{equation}
where $\AA^2$ is the quasi local $C^*$ algebra on $\ZZ^2$ constructed from an on site algebra $\BB(\CC^d)\otimes\BB(\CC^d)\simeq \BB(\CC^{d\times d})$\footnote{Clearly this can also be used to stack two $C^*$-algebras with different on site Hilbert spaces, this was used in the introduction. In the rest of the paper we will for simplicity of notation (but without loss of generality) only stack two identical $C^*$-algebras on top of each other.}. We will also need to define the stacking of the group action by which we mean
\begin{equation}
	(\beta_g\otimes_{\text{stack}}\beta_g)^\Lambda=\bigotimes_{z\in\Lambda}\Ad{U(g)\otimes U(g)_z}
\end{equation}
for any $\Lambda\in\mathfrak{G}_{\ZZ^2}$ (in fact stacking can be defined for any automorphism, not just the group action).
\subsection{States on $\AA$}\label{sec:States}
We will use $\PP(\AA)$ to denote the set of pure states on $\AA$ (see \cite{bratteli1979operator}). In this paper we will often refer to the GNS triple. For its definition, construction and properties we refer to \cite{bratteli1979operator}. We will sometimes write the tensor product of states $\omega\otimes\phi$ to be such that $(\omega\otimes\phi)(a\otimes b)=\omega(a)\phi(b)$ and similarly for the stacking tensor product. We will call a pure state $\phi$ on $\AA_\Gamma$ a product state if for any $\Lambda\subset\Gamma$, the restriction $\phi|_{\AA_\Lambda}$ is still pure. We will call a state $\omega$, $G$-invariant if $\omega\circ\beta_g=\omega$ (where $\beta_g=i_{U(g)}$ with $U$ an on site group action). Moreover, let $U$ we say that a $G$-invariant product state $\phi$ is trivial with respect to $U$ (we will sometimes denote this as $(\phi,U)$ is trivial) if $\phi(U_i(g))=1$ for all $i\in\ZZ^2$.\\\\
There is a natural way to construct a pure $G$-invariant state on the quasi local $C^*$-algebra over $\ZZ^2$, $\AA_{\ZZ^2}$ using a pure $G$-invariant state on the quasi local $C^*$-algebra over $\ZZ$, $\AA_{L_0}$\footnote{When applied to a trivial state on $\AA_{L_0}$ this will also give a trivial state on $\AA_{\ZZ^2}$.}.
\begin{definition}\label{def:InfiniteTensorProduct}
	Let $\phi\in\PP(\AA_{L_0})$ be a state that is $G$-invariant under a group action $\beta_g^{L_0}$. Define $\phi_i\in\PP(\AA_{L_i})$ as $\phi_i:=\phi_0\circ\tau^{-i}$. We define the infinite tensor product state $\omega_\phi$ as
	\begin{equation}
		\omega_\phi:=\bigotimes_{j\in\ZZ}\phi_j.
	\end{equation}
	This is a $G$-invariant pure state over $\ZZ^2$ that is invariant under the automorphism $\tau$.
\end{definition}
The proof that this is a well defined state is done in definition \ref{def:InfiniteTensorProductState}.
\subsection{Interactions and locally generated automorphisms}\label{sec:Interactions}
An interaction $\Phi$ is a map
\begin{equation}
	\Phi: \mathfrak{G}_{\ZZ^2}\rightarrow \AA_{\text{loc}}: I \mapsto \Phi(I)
\end{equation}
where $\Phi(I)\in\AA_I$ is hermitian ($\Phi(I)=\Phi(I)^*$). We will sometimes require a norm on the space of interactions that indicates how local an interaction acts. Take $F:\NN\rightarrow \RR^+$ any monotonically decreasing positive function then we define an $F$-norm on the space of interactions by:
\begin{equation}
	\norm{\Phi}_F\defeq \sup_{x,y\in\ZZ^2}\frac{1}{F(\abs{x-y})}\sum_{Z\in\mathfrak{G}_{\ZZ^2},Z\ni x,y}\norm{\Phi(Z)}.
\end{equation}
Following \cite{ogata2021h3gmathbb} we will fix a specific family of monotonically decreasing positive functions by saying that for any $0<\phi<1$ we define
\begin{equation}\label{eq:OurFFunction}
	F_\phi:\RR^+\rightarrow\RR^+:r\mapsto \frac{\exp(-r^\phi)}{(1+r)^4}.
\end{equation}
We will sometimes use the restriction of an interaction. For some $\Gamma\subset\ZZ^2$ we define $\Phi_\Gamma$ by
\begin{equation}
	\Phi_\Gamma:\mathfrak{G}_{\ZZ^2}\rightarrow \AA_{\text{loc}}:I\mapsto\left\{\begin{matrix}
		\Phi(I)&\text{if }I\subset\Gamma\\0&\text{otherwise}.
	\end{matrix}\right.
\end{equation}
The set of interactions with this norm (for a fixed $F$) is a Banach space. One of the properties of $F$-local interactions is that they can be used to generate automorphisms. Let
\begin{equation}
	\Phi:\mathfrak{G}_{\ZZ^2}\times [0,1]\rightarrow \AA_{\text{loc}}:(I,t)\mapsto \Phi(I,t)
\end{equation}
be a norm continuous\footnote{By which we mean that $\Phi(I,\cdot)$ is norm continuous for each $I\in\mathfrak{G}_{\ZZ^2}$.} one parameter family of interactions such that the $F$-norm is uniformly bounded ($\sup_{t\in[0,1]}\norm{\Phi(\cdot,t)}_F<\infty$). We will denote the set of one parameter families of interactions that satisfy this property by $\BB_{F}([0,1])$. For any $\Phi\in\BB_{F_\phi}([0,1])$, we define the locally generated automorphism (LGA) $\gamma^{\Phi}_{s;t}$ such that for any $A\in\AA$, $\gamma^{\Phi}_{s;t}(A)$ is given as the solution to the differential equation
\begin{equation}
	\frac{\d}{\d t}\gamma^{\Phi}_{s;t}(A)=-i\sum_{I\in\mathfrak{G}_{\ZZ^2}}\gamma^{\Phi}_{s;t}([\Phi(I,t),A])
\end{equation}
with initial condition $\gamma^{\Phi}_{s;s}(A)=A$ (the existence of this automorphism is proven in \cite{doi:10.1063/1.5095769}). This satisfies the condition that if $\sup_t\norm{\sum_{I\in\mathfrak{B}_{\ZZ^2}}\Phi(I,t)}<\infty$ then
\begin{align}
	\gamma^\Phi_{s;t}&=\Ad{u^\Phi_{s;t}}&u^\Phi_{s;t}&\defeq\mathcal{T}\exp(-i\int_t^s\d s'\sum_{I\in\mathfrak{B}_{\ZZ^2}}\Phi(s',t)).
\end{align}
Sometimes we will say that an interaction is $G$-invariant. By this we simply mean that $\beta_g(\Phi(I))=\Phi(I)$ (for all $I\in\mathfrak{G}_{\ZZ^2}$). Similarly if we say an interaction is translation invariant we mean that $\tau(\Phi(I))=\Phi(\tau(I))$ (for all $I\in\mathfrak{G}_{\ZZ^2}$). It should be clear that if an interaction is $G$-invariant (translation invariant) that then the LGA it generates commutes with the group action (the translation automorphism) as well.
\subsection{The stable equivalence class}\label{sec:StableEquivalenceClasses}
We will now define a subset of these states that we will call short range entangled (SRE):
\begin{definition}\label{def:sre}
	Let $\omega\in\PP(\AA)$. We say that $\omega$ is an SRE state if and only if there exists a $\phi\in]0,1[$ such that there exists an interaction $\Phi\in\BB_{F_\phi}([0,1])$ such that $\omega\circ\gamma^\Phi_{0;1}$ is a product state. We then call $\gamma^\Phi_{0;1}$ a disentangler for $\omega$.
\end{definition}
On the set of $G$-invariant SRE states we will now define three stable equivalence classes depending on the additional imposed symmetry:
\begin{definition}
	Take $(\omega_1,U_1)$ and $(\omega_2,U_2)$ elements of
	\begin{equation}
		S_0=\{(\omega,U)\in\PP(\AA)\times\hom(G,U(\CC^d))|\omega\text{ is SRE},\:\omega\circ i_{U(g)}=\omega\:\forall g\in G\}
	\end{equation}
	for two algebras $\AA_1$ and $\AA_2$\footnote{With two different algebras we simply mean two different on site dimensions because we already fixed each on site dimension to be identical.}. We say that $\expval{\omega_1,U_1}_\sim=\expval{\omega_2,U_2}_\sim$ if and only if there exists a $\phi\in]0,1[$ such that there exists a $G$-invariant interaction $\Phi\in\BB_{F_\phi}([0,1])$, trivial elements of $S_0$ (see subsection \ref{sec:States}), $(\phi_1,\tilde U_1)$ and $(\phi_2,\tilde U_2)$ for algebras $\tilde\AA_1$ and $\tilde\AA_2$ respectively and an on site unitary such that
	\begin{align}
		\omega_1\otimes_{\text{stack}}\phi_1\circ i_V&=\omega_2\otimes_{\text{stack}}\phi_2\circ\gamma^\Phi_{0;1}&V^\dagger U_{1}(g)\otimes \tilde{U}_{1}(g)V&=U_{2}(g)\otimes \tilde{U}_{2}(g).
	\end{align}
\end{definition}
We also define similar equivalence classes $\expval{\cdot}_\sim^1,\expval{\cdot}_\sim^2$ and $\expval{\cdot}_\sim^3$ on
\begin{align}
	S_1&=\{(\omega,U)\in\PP(\AA)\times\hom(G,U(\CC^d))|\omega\text{ is SRE},\:\omega\circ i_{U(g)}=\omega\:\forall g\in G,\:\omega\circ\tau=\omega\}\\
	S_2&=\{(\omega,U)\in\PP(\AA)\times\hom(G,U(\CC^d))|\omega\text{ is SRE},\:\omega\circ i_{U(g)}=\omega\:\forall g\in G,\:\omega\circ\nu=\omega\}\\
	S_3&=\{(\omega,U)\in\PP(\AA)\times\hom(G,U(\CC^d))|\omega\text{ is SRE},\:\omega\circ i_{U(g)}=\omega\:\forall g\in G,\:\omega\circ\tau=\omega,\:\omega\circ\nu=\omega\}
\end{align}
respectively. Here we now also demand that the interactions and the trivial states are invariant under the additional translation symmetries.
\section{Results}
This section will contain three different parts. First we discuss the main result starting from some rather abstract assumptions. In the second part we present the claim that these assumptions are implied by some more natural assumptions relating to short range entanglement. In the last part of the section we compare our assumptions to those made in \cite{ogata2021h3gmathbb}.
\subsection{Statement of the result in terms of Q-automorphisms}\label{sec:Results_2}
\input{Figures/Figure1}
Similarly what was done in \cite{ogata2021h3gmathbb}, we will define an index on the space of states that can be disentangled by a Q-automorphism. This class of automorphisms is defined as:
\begin{definition}
	Take $\alpha\in\Aut{\AA}$. We say that $\alpha\in\QAut{\AA}$ if and only if $\forall\theta\in]0,\pi/2[$ there exists an $\alpha_L\in\Aut{\AA_L},\alpha_R\in\Aut{\AA_R},V_1\in\UU(\AA)$ and a $\Theta\in\Aut{\AA_{W(C_\theta)^c}}$\footnote{Note that our definition of $\QAut{\AA}$ is slightly different from the definition of $\textrm{QAut}(\AA)$ from \cite{ogata2021h3gmathbb} because of this widening $W$.} such that
	\begin{equation}
		\alpha=\Ad{V_1}\circ\alpha_L\otimes\alpha_R\circ\Theta.
	\end{equation}
\end{definition}
We will often write $\alpha_0$ to mean $\alpha_L\otimes\alpha_R$. In this paper we will consider states that satisfy the following property (see figure \ref{fig:SetupWithQAutomorphism} for the support of the automorphisms):
\begin{restatable}{assumption}{assumptionOne}\label{assumption}
	Let $\omega\in\PP(\AA)$ be
	\begin{enumerate}
		\item such that there exists an automorphism $\alpha\in\QAut{\AA}$ and a product state $\omega_0\in\PP(\AA)$ satisfying
		\begin{align}
			\omega=\omega_0\circ\alpha.
		\end{align}
		\item such that there exists a $\theta\in]0,\pi/2[$ for which there exists a map
		\begin{equation}
			\tilde\beta:G\rightarrow\Aut{\AA}:g\mapsto\tilde\beta_g
		\end{equation}
		satisfying
		\begin{align}
			\omega\circ\tilde\beta_g&=\omega&\tilde\beta_g=\Ad{V_{g,2}}\circ\eta^L_g\otimes\eta^R_g\circ\beta^U_g
		\end{align}
		for some $V_{g,2}\in\UU(\AA),\eta^L_g\in\Aut{\AA_{C_\theta\cap L}}$ and $\eta^R_g\in\Aut{\AA_{C_\theta\cap R}}$.
		\item translation invariant ($\omega\circ\tau=\omega$).
	\end{enumerate}
\end{restatable}
We will also require a similar subclass of automorphisms and states on the quasi local $C^*$-algebra over $\ZZ$, $\AA_{L_0}$. We now define the assumption
\begin{restatable}{assumption}{assumptionOneDimensionalOne}\label{assumption1d}
	Take $\phi\in\PP(\AA_{L_0})$ such that
	\begin{enumerate}
		\item $\phi\circ\beta_g=\phi$.
		\item there exist automorphisms $\tilde\alpha_L\in\Aut{\AA_{L_0\cap L}}$, $\tilde\alpha_R\in\Aut{\AA_{L_0\cap R}}$ and a summable operator $b\in\UU(\AA_{L_0})$ such that
		\begin{equation}
			\phi_0=\phi\circ\Ad{b}\circ\tilde\alpha_{L}\otimes\tilde\alpha_{R}
		\end{equation}
		is a product state.
	\end{enumerate}
\end{restatable}
We now state the result that using assumption \ref{assumption} we can define an $H^2(G,\TT)$-valued index.
\begin{theorem}\label{thrm:ExistenceFirstIndex}
	For any $\AA$ satisfying the construction from section \ref{sec:QuasiLocalC*Algebra} and any choice of on site group action $U\in\hom(G,U(\CC^d))$, there exists a map
	\begin{equation}
		\textrm{Index}^{\AA,U}:\{\omega\in\PP(\AA)|\omega\text{ satisfies assumption \ref{assumption}}\}\rightarrow H^2(G,\TT)
	\end{equation}
	that is well defined (doesn't depend on any of the choices in assumption \ref{assumption}). This map will be consistent with conjecture \ref{conj} by which we mean that:
	\begin{enumerate}
		\item For any $G$ invariant and translation invariant family of interactions $\Phi\in\BB_{F_{\phi}}([0,1])$ (for some $0<\phi<1$) we have that
		\begin{equation}
			\textrm{Index}^{\AA,U}(\omega)=\textrm{Index}^{\AA,U}(\omega\circ\gamma^{\Phi}_{0;1}).
		\end{equation}
		\item For $\phi\in\PP(\AA_{L_0})$, any a one dimensional $G$-invariant state satisfying assumption \ref{assumption1d}, the state $\omega_\phi$ as defined in definition \ref{def:InfiniteTensorProduct} satisfies
		\begin{equation}
			\textrm{Index}^{\AA_{L_0},U}_{1d}(\phi)=\textrm{Index}^{\AA,U}(\omega).
		\end{equation}
		\item This index is a group homomorphism under the stacking operator. By this we mean that
		\begin{equation}
			\textrm{Index}^{\AA^2,U\otimes U}(\omega_1\otimes_{\text{stack}}\omega_2)=\textrm{Index}^{\AA,U}(\omega_1)+\textrm{Index}^{\AA,U}(\omega_2).
		\end{equation}
		\item The index is independent on the choice of basis for the on site Hilbert space by which we mean that for any on site unitary $V$ we get that
		\begin{equation}
			\textrm{Index}^{\AA,\Ad{V^\dagger}(U)}(\omega\circ i_V)=\textrm{Index}^{\AA,U}(\omega).
		\end{equation}
	\end{enumerate}
\end{theorem}
\begin{proof}
	This statement is proven in subsection \ref{sec:ProofOf:thrm:ExistenceFirstIndex}.
\end{proof}
\input{Figures/Figure5}
Now we will present the assumption from which we can define the $H^1(G,\TT)$-valued index (see figure \ref{fig:SetupForTwoTranslationsNearProof} for the support of the automorphisms).
\begin{restatable}{assumption}{assumptionTwo}\label{assumption:2Translations}
	Let $\omega\in\PP(\AA)$ be
	\begin{enumerate}
		\item such that there exists an automorphism $\alpha\in\QAut{\AA}$ and a product state $\omega_0\in\PP(\AA)$ satisfying
		\begin{align}
			\omega=\omega_0\circ\alpha.
		\end{align}
		\item such that there exists a $\theta\in]0,\pi/2[$ for which there exists a map
		\begin{equation}
			\tilde\beta:G\rightarrow\Aut{\AA}:g\mapsto\tilde\beta_g
		\end{equation}
		satisfying
		\begin{align}
			\label{eq:2TranslationsCondition3part1}
			\omega\circ\tilde\beta_g&=\omega&\tilde\beta_g&=\Ad{V_{g,2}}\circ\eta^L_g\otimes\eta^R_g\circ\beta^U_g
		\end{align}
		for some $V_{g,2}\in\UU(\AA),$ $\eta^L_g\in\Aut{\AA_{\nu^{-1}(C_\theta\cap L)}}$ and  $\eta^R_g\in\Aut{\AA_{\nu(C_\theta\cap R)}}$.
		\item translation invariant in both directions
		\begin{align}
			\omega\circ\tau&=\omega&\omega\circ\nu&=\omega.
		\end{align}
	\end{enumerate}
\end{restatable}
Similar to before, we also require an assumption for states on the quasi local $C^*$-algebra over $\ZZ$.
\begin{restatable}{assumption}{assumptionOneDimensionalTwo}\label{assumption1dWithTranslation}
	Take $\phi\in\PP(\AA_{L_0})$ such that
	\begin{enumerate}
		\item $\phi\circ\beta_g=\phi$.
		\item there exist automorphisms $\tilde\alpha_L\in\Aut{\AA_{L_0\cap L}}$, $\tilde\alpha_R\in\Aut{\AA_{L_0\cap R}}$ and a summable (see subsection \ref{sec:QuasiLocalC*Algebra} for the definition) operator $b\in\UU(\AA_{L_0})$ such that
		\begin{equation}
			\phi_0=\phi\circ\Ad{b}\circ\tilde\alpha_L\otimes\tilde\alpha_R
		\end{equation}
		is a product state.
		\item $\phi\circ\nu=\phi$.
	\end{enumerate}
\end{restatable}
This is almost completely identical to assumption \ref{assumption1d}, the only difference is the added translation symmetry. We are now ready to state the second main result:
\begin{theorem}\label{thrm:ExistenceSecondIndex}
	For any $\AA$ satisfying the construction from section \ref{sec:QuasiLocalC*Algebra} and any choice of on site group action $U\in\hom(G,U(\CC^d))$, there exists a map
	\begin{equation}
		\textrm{Index}^{\AA,U}_{2\text{ trans}}:\{\omega\in\PP(\AA)| \omega\text{ satisfies assumption \ref{assumption:2Translations}}\}\rightarrow H^1(G,\TT)
	\end{equation}
	that is well defined (doesn't depend on any of the choices made in assumption \ref{assumption:2Translations}). This map will be consistent with conjecture \ref{conj2} by which we mean the following:
	\begin{enumerate}
		\item For any $G$ invariant family of interactions that is translation invariant in both directions $\Phi\in\BB_{F_\phi}([0,1])$ we have that
		\begin{equation}
			\textrm{Index}^{\AA,U}_{2\text{ trans}}(\omega)=\textrm{Index}^{\AA,U}_{2\text{ trans}}(\omega\circ\gamma^\Phi_{0;1}).
		\end{equation}
		\item For $\phi\in\PP(\AA_{L_0})$, any a one dimensional $G$-invariant and translation invariant state satisfying assumption \ref{assumption1d}, the state $\omega_\phi$ as defined in \ref{def:InfiniteTensorProduct} satisfies
		\begin{equation}
			\textrm{Index}^{\AA_{L_0},U}_{1d\text{ trans}}(\phi)=\text{Index}^{\AA,U}_{2\text{ trans}}(\omega_\phi).
		\end{equation}
		\item This index is a group homomorphism under the stacking operator by which we mean that
		\begin{equation}
			\textrm{Index}_{\text{2 trans}}^{\AA^2,U\otimes U}(\omega_1\otimes_{\text{stack}}\omega_2)=\textrm{Index}_{\text{2 trans}}^{\AA,U}(\omega_1)+\textrm{Index}_{\text{2 trans}}^{\AA,U}(\omega_2).
		\end{equation}
		\item The index is independent on the choice of basis for the on site Hilbert space by which we mean that for any on site unitary $V$ we get that
		\begin{equation}
			\textrm{Index}^{\AA,\Ad{V^\dagger}(U)}_{\text{2 trans}}(\omega\circ i_V) =\textrm{Index}^{\AA,U}_{\text{2 trans}}(\omega).
		\end{equation}
	\end{enumerate}
\end{theorem}
\begin{proof}
	This statement is proven in subsection \ref{sec:ProofOf:thrm:ExistenceSecondIndex}.
\end{proof}
\subsection{SRE implies previous assumptions}\label{sec:Results_1}
The assumptions in the previous subsection are rather technical. In this section we show that these assumptions are strictly weaker than assumptions that are more natural. The assumptions on the states will now be that they are short range entangled (see definition \ref{def:sre}).\\\\
We will use the exact same definition (with the same $F$-function) for states over the quasi local $C^*$-algebra over $\ZZ$, $\AA_{L_0}$. We are now ready to show that SRE implies the previous assumptions.
\begin{restatable}{lemma}{SREImpliesQDisentanglableOneTranslation}\label{lem:SRE_Implies_QDisentanglable_OneTranslation}
	Take $\omega\in\PP(\AA)$ a short range entangled state that is $G$-invariant and translation invariant then it satisfies assumption \ref{assumption}.
\end{restatable}
\begin{proof}
	See subsection \ref{sec:ProofOfMainResult1}.
\end{proof}
\begin{restatable}{lemma}{SREImpliesAssumptionOneDimensional}\label{lem:SRE_Implies_Assumption_1d}
	Any $G$-invariant SRE state $\phi\in\PP(\AA_{L_0})$ satisfies assumption \ref{assumption1d}.
\end{restatable}
\begin{proof}
	See subsection \ref{sec:ProofOfMainResult1}.
\end{proof}
These two results imply that to any $G$-invariant translation invariant SRE state I can associate a consistent LGA invariant $H^3(G,\TT)\oplus H^2(G,\TT)$-valued SPT index. The first index is the index when there are no translations and the last index is the one from theorem \ref{thrm:ExistenceFirstIndex}.
\begin{restatable}{lemma}{SREImpliesQDisentanglableTwoTranslations}\label{lem:SRE_Implies_QDisentanglable_TwoTranslations}
	Let $\omega$ be a short range entangled state that is $G$-invariant and translation invariant in two directions then it satisfies assumption \ref{assumption:2Translations}.
\end{restatable}
\begin{proof}
	See subsection \ref{sec:ProofOfMainResult2}.
\end{proof}
\begin{restatable}{lemma}{SREImpliesAssumptionOneDimensionalTwoTranlations}\label{lem:SRE_Implies_Assumption_1dTwoTranslations}
	Any $G$-invariant, translation invariant SRE state $\phi\in\PP(\AA_{L_0})$ satisfies assumption \ref{assumption1dWithTranslation}.
\end{restatable}
\begin{proof}
	Trivially follows from lemma \ref{lem:SRE_Implies_Assumption_1d}.
\end{proof}
This shows that if a $G$-invariant SRE state is translation invariant in two directions I can find a consistent LGA invariant $H^3(G,\TT)\oplus H^2(G,\TT)\oplus H^2(G,\TT)\oplus H^1(G,\TT)$ valued SPT index. The first index is again the index when there are no translations, the second and third index are given by
\begin{align}
	\omega&\mapsto \textrm{Index}(\omega)&&\text{and}&\omega\mapsto \textrm{Index}(\omega\circ\mu)
\end{align}
where $\mu$ was the rotation automorphism and Index was defined in theorem \ref{thrm:ExistenceFirstIndex}. Finally the $H^1(G,\TT)$-valued index is defined in theorem \ref{thrm:ExistenceSecondIndex}. We now only have to show that there is no additional $H^1(G,\TT)$-valued index:
\begin{restatable}{lemma}{RotationDoesntChangeHOneIndex}\label{lem:RotationDoesn'tChangeH1Index}
	Let $\mu$ be the automorphism that rotates every element of the $C^*$ algebra by $90^\circ$ degrees then
	\begin{equation}
		\textrm{Index}_{\text{2 trans}}^{\AA,U}(\omega)=\textrm{Index}_{\text{2 trans}}^{\AA,U}(\omega\circ\mu).
	\end{equation}
\end{restatable}
\begin{proof}
	This is proven in subsection \ref{sec:H1ValuedIndexInvariantUnderRotations}.
\end{proof}
Now all that is left to show is that the indices defined here are constant on the stable equivalence classes introduced in the introduction and later on clarified in subsection \ref{sec:StableEquivalenceClasses}. To this end let $\expval{\cdot}_\sim$, $\expval{\cdot}_\sim^1$, $\expval{\cdot}_\sim^2$ and $\expval{\cdot}_\sim^3$ be the stable equivalence classes without translation symmetry, with only the $\tau$ translation symmetry, with only the $\nu$ translation symmetry and with both the $\tau$ and $\nu$ translation symmetry respectively. We now show the following lemma:
\begin{lemma}\label{lem:IndicesConstantOnStableEquivalenceClasses}
	Take $(\omega_1,U_1)$ and $(\omega_2,U_2)$ elements of $S_0$ (see subsection \ref{sec:StableEquivalenceClasses}) for algebras $\AA_1$ and $\AA_2$. The following three statements now hold true:
	\begin{enumerate}
		\item If $\expval{\omega_1,U_1}_\sim=\expval{\omega_2,U_2}_\sim$ then
		\begin{equation}
			\textrm{Index}^{\AA_1,U_1}_{\text{no trans}}(\omega_1)=\textrm{Index}^{\AA_2,U_2}_{\text{no trans}}(\omega_2)
		\end{equation}
		where $\textrm{Index}_{\text{no trans}}$ is the SPT index introduced in \cite{ogata2021h3gmathbb} (see subsection \ref{sec:SomeRemarks} for why this is well defined in this context).
		\item If additionally $(\omega_1,U_1),(\omega_2,U_2)\in S_1$ and $\expval{\omega_1,U_1}_\sim^1=\expval{\omega_2,U_2}_\sim^1$ then
		\begin{equation}
			\textrm{Index}^{\AA_1,U_1}(\omega_1)=\textrm{Index}^{\AA_2,U_2}(\omega_2)
		\end{equation}
		where $\textrm{Index}$ is the index introduced in theorem \ref{thrm:ExistenceFirstIndex}.
		\item If additionally $(\omega_1,U_1),(\omega_2,U_2)\in S_2$ and $\expval{\omega_1,U_1}_\sim^2=\expval{\omega_2,U_2}_\sim^2$ then
		\begin{equation}
			\textrm{Index}^{\AA_1,U_1}(\omega_1\circ\mu)=\textrm{Index}^{\AA_2,U_2}(\omega_2\circ\mu)
		\end{equation}
		where $\mu$ was the rotation automorphism.
		\item If additionally $(\omega_1,U_1),(\omega_2,U_2)\in S_3$ and $\expval{\omega_1,U_1}_\sim^3=\expval{\omega_2,U_2}_\sim^3$ then
		\begin{equation}
			\textrm{Index}^{\AA_1,U_1}_{\text{2 trans}}(\omega_1)=\textrm{Index}^{\AA_2,U_2}_{\text{2 trans}}(\omega_2)
		\end{equation}
		where $\textrm{Index}_{\text{2 trans}}$ is the index introduced in theorem \ref{thrm:ExistenceSecondIndex}.
	\end{enumerate}
\end{lemma}
\begin{proof}
	This is shown in appendix \ref{sec:ProofOf:lem:IndicesConstantOnStableEquivalenceClasses}.
\end{proof}
\subsection{Comparison with \cite{ogata2021h3gmathbb}}\label{sec:SomeRemarks}
The first thing we would like to remark is that in \cite{ogata2021h3gmathbb}, a different equivalence class on states is used. First of all the set of states considered is a priori different. Namely, for any state $\psi\in \PP(\AA)$, we define two different conditions
\begin{enumerate}
	\item There exists a $\Phi\in\PP_{\text{SL}}$\footnote{This is defined in \cite{ogata2021h3gmathbb} but it essentially means bounded interaction that is connected to a trivial (without overlapping terms) interaction.} such that $\psi$ is the unique gapped groundstate of $\Phi$.
	\item $\psi$ is an SRE state.
\end{enumerate}
However in theorem 5.1 of \cite{ogata2021h3gmathbb} it is proven that the first item implies the second item. If one then looks at the definition of the index there, one could as well have started from the second condition. This is precisely what we did in this paper. As a side note, one should also be able to prove that the second item implies the first item by using theorem D.5 of \cite{ogata2021h3gmathbb} with $\mathcal{K}_t$ the disentangler and $\Phi$ a gapped interaction that has the product state as its groundstate. However, we won't work this out explicitly in this paper.\\\\
When we add the group, the story changes considerably. Let us define the two different equivalence classes. To this end, let $\psi_1$ and $\psi_2$ be two (pure) $G$-invariant states that are unique gapped groundstates of $\Phi_0$ and $\Phi_1\in\PP_{\text{SL},\beta}$ respectively. The following two conditions define different equivalence classes:
\begin{enumerate}
	\item There exists a $G$-invariant, bounded path of gapped interactions $\lambda\mapsto\tilde\Phi(\lambda)$ (see \cite{ogata2021h3gmathbb} for precise definitions) such that $\psi_1$ and $\psi_2$ are unique gapped groundstates of $\tilde{\Phi}(0)$ and $\tilde{\Phi}(1)$ respectively.
	\item There exists a $G$-invariant LGA, $\gamma^\Psi_{0;1}$ such that $\psi_1\circ\gamma^H_{0;1}=\psi_2$.
\end{enumerate}
A priori those two conditions are not equivalent. However in \cite{ogata2021h3gmathbb} it is proven that, the first equivalence implies the second one. The proof that equivalent states have the same index only uses the second condition. This means that one could also have taken the second equivalence condition as the starting point. This is exactly what we do in this paper. One should also be able to show that the first condition implies the second one using a similar construction as in the above remark without the group and averaging the resulting interaction over the group (where one then has to use that a finite group has a normalised Haar measure).\\\\
There where two things that are in theorems \ref{thrm:ExistenceFirstIndex} and \ref{thrm:ExistenceSecondIndex} but where not discussed in \cite{ogata2021h3gmathbb}. This is the part that the index is a group homomorphism under stacking and the part that the index is independent on the choice of basis for the on site Hilbert space. However, on inspection of the arguments used in subsections \ref{sec:StackingOneTranslation} and \ref{sec:the-h2-valued-index-is-invariant-of-choice-of-basis-of-on-site-hilbert-space} one can conclude that these also hold for the $H^3$-valued index.\\\\
All in all we have provided a proof that the work done in \cite{ogata2021h3gmathbb} also implies the following theorem:
\begin{theorem}\label{thrm:ExistenceOriginalIndex}
	For any $\AA$ satisfying the construction from section \ref{sec:QuasiLocalC*Algebra} and any choice of on site group action $U\in\hom(G,U(\CC^d))$, there exists a map
	\begin{equation}
		\textrm{Index}^{\AA,U}_{\text{no trans}}:\{\omega\in\PP(\AA)| \omega\text{ is SRE and }G\text{-invariant}\}\rightarrow H^3(G,\TT)
	\end{equation}
	that is well defined (doesn't depend on the choice of disentangler). This map will satisfy:
	\begin{enumerate}
		\item For any $G$ invariant family of interactions $\Phi\in\BB_{F_\phi}([0,1])$ we have that
		\begin{equation}
			\textrm{Index}^{\AA,U}_{\text{no trans}}(\omega)=\textrm{Index}^{\AA,U}_{\text{no trans}}(\omega\circ\gamma^\Phi_{0;1}).
		\end{equation}
		\item This index is a group homomorphism under the stacking operator by which we mean that
		\begin{equation}
			\textrm{Index}_{\text{no trans}}^{\AA^2,U\otimes U}(\omega_1\otimes_{\text{stack}}\omega_2)=\textrm{Index}_{\text{no trans}}^{\AA,U}(\omega_1)+\textrm{Index}_{\text{no trans}}^{\AA,U}(\omega_2).
		\end{equation}
		\item The index is independent on the choice of basis for the on site Hilbert space by which we mean that for any on site unitary $V$ we get that
		\begin{equation}
			\textrm{Index}^{\AA,\Ad{V^\dagger}(U)}_{\text{no trans}}(\omega\circ i_V) =\textrm{Index}^{\AA,U}_{\text{no trans}}(\omega).
		\end{equation}
	\end{enumerate}
\end{theorem}
\section{The $H^2(G,\TT)$-valued index}\label{sec:ProofFirstStatement}
In this section we will define the $H^2(G,\TT)$-valued index starting from assumption \ref{assumption}. In what follows, we will first fix certain objects to define the index and then in section \ref{sec:IndexIsInvariantUnderChoices} we will show that it is independent of all these choices. Fix an $\omega_0$ and an $\alpha$. Fix $(\HH_0=\HH_L\otimes\HH_R,\pi_0=\pi_L\otimes\pi_R,\Omega_0)$ a GNS triple (see theorem \ref{thrm:ExistenceGNS}) of $\omega_0$ where ($\forall\sigma\in\{L,R\}$) $\pi_\sigma:\AA_\sigma\rightarrow\BB(\HH_\sigma)$ is a GNS representation of the restriction of $\omega_0$ to $\sigma$. Fix as well $V_1,\alpha_0=\alpha_L\otimes\alpha_R$ and $\Theta$ a choice of decomposition for $\alpha$ such that $\Theta$ and $\eta_g$ commute (see figure \ref{fig:SetupWithQAutomorphism}). Because we will be working with states that are translation invariant it make sense to define the translation action on the GNS space of $\omega_0$:
\begin{lemma}\label{lem:Definition_v}
	There exists a unique $v\in\UU(\HH_0)$ such that
	\begin{align}
		\Ad{v}\circ\pi_0&=\pi_0\circ\alpha_0\circ\Theta\circ\tau\circ\Theta^{-1}\circ\alpha_0^{-1}&&\text{and}&\pi_0(V_1)v\pi_0(V_1^\dagger)\Omega_0&=\Omega_0.
	\end{align}
\end{lemma}
\begin{proof}
	Since $\omega\circ\tau=\omega$ we get by the uniqueness of the GNS triple (see corollary \ref{cor:ExistenceOfUnitary}) that there exists a unique $\tilde{v}\in\UU(\HH_0)$ satisfying
	\begin{align}
		\Ad{\tilde{v}}\circ\pi_0\circ\alpha&=\pi_0\circ\alpha\circ\tau&\tilde{v}\Omega_0&=\Omega_0.
	\end{align}
	Since $\alpha=\Ad{V_1}\circ\alpha_0\circ\Theta$ we get that
	\begin{align}
		\Ad{\pi_0(V_1^\dagger)\tilde{v}\pi_0(V_1)}\circ\pi_0\circ\alpha_0\circ\Theta&=\pi_0\circ\alpha_0\circ\Theta\circ\tau&\tilde{v}\Omega_0&=\Omega_0.
	\end{align}
	Choosing $v=\pi_0(V_1^\dagger)\tilde{v}\pi_0(V_1)$  concludes the proof.
\end{proof}
\subsection{Cone operators}
 We now define a subgroup of $\UU(\HH_0)$ that includes the representations of cone automorphisms:
\begin{definition}\label{def:ConeOperators}
	Take $0<\theta<\pi/2$, $\alpha_L\in\Aut{\AA_{L}}$, $\alpha_R\in\Aut{\AA_{R}}$ and $\alpha_0\defeq \alpha_L\otimes\alpha_R$. Take $\sigma\in\{L,R\}$ and $x\in\UU(\HH_{\sigma})\otimes\id_{\HH_{\ZZ^2/\sigma}}$ then we say that $x$ is a cone operator on $\sigma$ (or in short $x\in\textrm{Cone}_{\sigma}(\alpha_0,\theta)$) if and only if there exists a $\xi\in\Aut{\AA_{W(C_\theta)\cap\sigma}}$ such that
	\begin{equation}
		\Ad{x}\circ\pi_0\circ\alpha_0=\pi_0\circ\alpha_0\circ\xi.
	\end{equation}
	$\textrm{Cone}_\sigma(\alpha_0,\theta)$ is a subgroup of $\UU(\HH_\sigma)\otimes\id_{\ZZ^2/\sigma}$. We have that
	\begin{align}\label{eq:CommutantPropertyCones}
		\textrm{Cone}_R(\alpha_0,\theta)&\subseteq\textrm{Cone}_L(\alpha_0,\theta)'&\textrm{Cone}_L(\alpha_0,\theta)&\subseteq\textrm{Cone}_R(\alpha_0,\theta)'.
	\end{align}
	If additionally $\xi\in\Aut{\AA_{C_\theta\cap\sigma}}$ we will say that $x\in\textrm{Cone}_L^W(\alpha_0,\theta)$.
\end{definition}
\begin{proof}
	The proof of equation \eqref{eq:CommutantPropertyCones} just follows from the fact that we defined $\textrm{Cone}_\sigma(\alpha_0,\theta)$ such that
	\begin{align}
		\textrm{Cone}_L(\alpha_0,\theta)&\subseteq \UU(\HH_L)\otimes\id_{\HH_R}&\textrm{Cone}_R(\alpha_0,\theta)&\subseteq \id_{\HH_L} \otimes \UU(\HH_R).
	\end{align}
\end{proof}
We will also define a generalisation of this. We will define a subgroup of $\UU(\HH_0)$ that includes both the group $\pi_0\circ\alpha_0\circ\Theta(\UU(\AA_R))$ and the representations of cone automorphisms:
\begin{definition}
	Take $0<\theta<\pi/2$, $\alpha_L\in\Aut{\AA_{L}}$, $\alpha_R\in\Aut{\AA_{R}}$ and $\Theta\in\Aut{\AA_{W(C_\theta)^c}}$. Take $\sigma\in\{L,R\}$ and take $x\in\UU(\HH_0)$ then we say that $x$ is an inner after cone operator on $\sigma$ (or in short $x\in \IAC_\sigma(\alpha_0,\theta,\Theta)$) if there exists an $A\in\UU(\AA_\sigma)$ and a $y\in\textrm{Cone}_\sigma(\alpha_0,\theta)$ such that
	\begin{equation}
		x=\pi_0\circ\alpha_0\circ\Theta(A)y.
	\end{equation}
	$\IAC_\sigma$ is a subgroup of $\UU(\HH_0)$. We get that
	\begin{align}\label{eq:CommutantProperty}
		\IAC_R(\alpha_0,\theta,\Theta)&\subseteq\IAC_L(\alpha_0,\theta,\Theta)'&\IAC_L(\alpha_0,\theta,\Theta)&\subseteq\IAC_R(\alpha_0,\theta,\Theta)'.
	\end{align}
	If additionally $y\in \textrm{Cone}_L^W(\alpha_0,\theta)$ we will say that $x\in \IAC_\sigma^W(\alpha_0,\theta,\Theta)$.
\end{definition}
\begin{proof}
	Take $u_L\in\IAC_L(\alpha_0,\theta,\Theta)$ and $u_R\in\IAC_R(\alpha_0,\theta,\Theta)$ arbitrary. Take $A_\sigma\in\UU(\AA_\sigma)$ and $v_\sigma\in\textrm{Cone}_\sigma(\alpha_0,\theta)$ (for $\sigma\in\{L,R\}$) such that $u_\sigma=\pi_0\circ\alpha_0\circ\Theta(A_\sigma)v_\sigma$. We then get
	\begin{align}
		&[u_L,u_R]=u_Lu_R-u_Ru_L\\
		&=\pi_0\circ\alpha_0\circ\Theta(A_L)v_L\pi_0\circ\alpha_0\circ\Theta(A_R)v_R-\pi_0\circ\alpha_0\circ\Theta(A_R)v_R\pi_0\circ\alpha_0\circ\Theta(A_L)v_L\\
		&=\pi_0\circ\alpha_0\circ\Theta(A_L)\Ad{v_L}\circ\pi_0\circ\alpha_0\circ\Theta(A_R)v_Lv_R-\pi_0\circ\alpha_0\circ\Theta(A_R)v_R\pi_0\circ\alpha_0\circ\Theta(A_L)v_L.
	\end{align}
	If we now take $\xi_\sigma\in\Aut{\AA_{W(C_\theta)}\cap\AA_\sigma}$ such that $\Ad{v_\sigma}\circ\pi_0\circ\alpha_0=\pi_0\circ\alpha_0\circ\xi_\sigma$ we get that
	\begin{align}
		&=\pi_0\circ\alpha_0\circ\Theta(A_L)\pi_0\circ\alpha_0\circ\Theta\circ\xi_L(A_R)v_Lv_R-\pi_0\circ\alpha_0\circ\Theta(A_R)v_R\pi_0\circ\alpha_0\circ\Theta(A_L)v_L\\
		&=\pi_0\circ\alpha_0\circ\Theta(A_L)\pi_0\circ\alpha_0\circ\Theta(A_R)v_Lv_R-\pi_0\circ\alpha_0\circ\Theta(A_R)v_R\pi_0\circ\alpha_0\circ\Theta(A_L)v_L\\
		&=\pi_0\circ\alpha_0\circ\Theta(A_R)\pi_0\circ\alpha_0\circ\Theta(A_L)v_Lv_R-\pi_0\circ\alpha_0\circ\Theta(A_R)v_R\pi_0\circ\alpha_0\circ\Theta(A_L)v_L.
	\end{align}
	Using property \eqref{eq:CommutantPropertyCones} we now get that
	\begin{align}
		&=\pi_0\circ\alpha_0\circ\Theta(A_R)\pi_0\circ\alpha_0\circ\Theta(A_L)v_Rv_L-\pi_0\circ\alpha_0\circ\Theta(A_R)v_R\pi_0\circ\alpha_0\circ\Theta(A_L)v_L\\
		&=\pi_0\circ\alpha_0\circ\Theta(A_R)v_R\pi_0\circ\alpha_0\circ\Theta\circ\xi_R^{-1}(A_L)v_L-\pi_0\circ\alpha_0\circ\Theta(A_R)v_R\pi_0\circ\alpha_0\circ\Theta(A_L)v_L\\
		&=0
	\end{align}
	concluding the proof.
\end{proof}
\begin{remark}
	The main reason for the introduction of the $\textrm{Cone}_\sigma^W(\alpha_0,\theta)$ and $\IAC^W_\sigma(\alpha_0,\theta,\Theta)$ subgroups is that they are still (inner after) cone operators when translated. More specifically, let $x\in\textrm{Cone}_\sigma^W(\alpha_0,\theta)$ then both $vxv^\dagger$ and $v^\dagger x v$ are elements of $\textrm{Cone}_\sigma(\alpha_0,\theta)$. The analogous statement is also true for the $\IAC$ operators.
\end{remark}
The following lemma shows that if a unitary on the GNS space of $\omega_0$ has an adjoint action that is the product of cones then it is a product of cone operators:
\begin{lemma}\label{lem:UsingIrreducibilityAndWignerTheorem}
	Take $x\in\UU(\HH_0)$ such that there exist $\xi_\sigma\in\Aut{\AA_{C_\theta}\cap\AA_\sigma}$ (for $\sigma\in\{L,R\}$) satisfying
	\begin{equation}
		\Ad{x}\circ\pi_0\circ\alpha_0=\pi_0\circ\alpha_0\circ\xi_L\otimes\xi_R
	\end{equation}
	then there exist $x_\sigma\in\textrm{Cone}_\sigma(\alpha_0,\theta)$ such that
	\begin{equation}
		x=x_L\otimes x_R.
	\end{equation}
	These are unique up to a phase.
\end{lemma}
\begin{proof}
Using lemma \ref{lem:SplittingOfUnitary} the result follows.
\end{proof}
Following Yoshiko Ogata \cite{ogata2021h3gmathbb} we now define objects using the following lemma:
\begin{lemma}\label{lem:Definition_W_And_u}
	There unitaries $W_g\in\UU(\HH_0)$ and $u_{\sigma}(g,h)\in\UU(\HH_{\sigma})$ for all $g,h\in G$ and for all $\sigma\in\{L,R\}$ satisfying
	\begin{align}
		\Ad{W_g}\circ\pi_0&=\pi_0\circ\alpha_0\circ\Theta\circ\eta_g\circ\beta_g^U\circ\Theta^{-1}\circ\alpha_0^{-1}\\
		\Ad{u_\sigma(g,h)}\circ\pi_\sigma&=\pi_\sigma\circ\alpha_\sigma\circ\eta_g^\sigma\circ\beta_g^{\sigma U}\circ\eta_h^{\sigma}\circ(\beta_g^{\sigma U})^{-1}\circ(\eta^\sigma_{gh})^{-1}\circ\alpha_\sigma^{-1}\\
		u_L(g,h)\otimes u_R(g,h)&=W_gW_hW_{gh}^{-1}.
	\end{align}
\end{lemma}
\begin{proof}
	The result follows from the fact that assumption \ref{assumption} is sufficient to define the objects used in lemma 2.1 and definition 2.2 of \cite{ogata2021h3gmathbb}.
\end{proof}
These objects will be the starting point for our definition. Clearly the $u_\sigma(g,h)$ are elements of $\textrm{Cone}_\sigma^W(\alpha_0,\theta)$. The $W_g$ have the following property:
\begin{lemma}\label{lem:AdjointOverConeIsInCone}
	Take $\Xi^{\sigma}\in\textrm{Cone}_\sigma(\alpha_0,\theta)$ (for all $\sigma\in\{L,R\}$) then $\Ad{W_g}(\Xi^\sigma)\in\textrm{Cone}_\sigma(\alpha_0,\theta)$ (for all $g\in G$).	If more generally we take $\Xi^\sigma\in\IAC_\sigma(\alpha_0,\Theta)$ then $\Ad{W_g}(\Xi^\sigma)\in\IAC_\sigma(\alpha_0,\Theta)$. Similarly if $\Xi^{\sigma}\in\textrm{Cone}_\sigma^W(\alpha_0,\theta)$ then $\Ad{W_g}(\Xi^\sigma)\in\textrm{Cone}_\sigma^W(\alpha_0,\theta)$.
\end{lemma}
\begin{proof}
	Take $\tilde{\Xi}^\sigma$ such that $\Xi^\sigma=\tilde{\Xi}^\sigma\otimes\id_{\HH_{\sigma^c}}$. Take $\xi_\sigma\in\Aut{\AA_{W(C_\theta)\cap\sigma}}$ such that
	\begin{equation}
		\Ad{\tilde\Xi^\sigma}\circ\pi_\sigma\circ\alpha_\sigma=\pi_\sigma\circ\alpha_\sigma\circ \xi_\sigma.
	\end{equation}
	We have that
	\begin{equation}
		\Ad{\Ad{W_g}(\Xi^R)}\circ\pi_0\circ\alpha_0\circ\Theta=\pi_0\circ\alpha_0\circ\Theta\circ\zeta_{g,R}
	\end{equation}
	where
	\begin{equation}
		\zeta_{g,\sigma}\defeq \eta_g\circ\beta_g^{U}\circ\xi_\sigma\circ(\beta_g^{U})^{-1}\circ\eta_g^{-1}.
	\end{equation}
	Since $\zeta_{g,\sigma}\in\Aut{\AA_{C_\theta}\cap\AA_{\sigma}}$ we get that
	\begin{equation}
		\Ad{\Ad{W_g}(\Xi^R)}\circ\pi_0\circ\alpha_0=\pi_L\circ\alpha_L\otimes\pi_R\circ\alpha_R\circ\zeta_{g,R}.
	\end{equation}
	Using lemma \ref{lem:SplittingOfUnitary} there exists a $Z_{g,R}\in\UU(\HH_R)$ satisfying that $\Ad{W_g}(\Xi^R)=\id_{\HH_L}\otimes Z_{g,R}$. To show the second result we only need to observe that for any $A\in\UU(\AA_R)$ we get that
	\begin{align}
		\Ad{W_g}\left(\pi_0\circ\alpha_0\circ\Theta(A)\Xi_R\right)&=\Ad{W_g}\circ\pi_0\circ\alpha_0\circ\Theta(A)\Ad{W_g}(\Xi_R)\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\xi_R(A)\Ad{W_g}(\Xi_R).
	\end{align}
	By the previous result, this is clearly in $\IAC_R(\alpha_0,\theta,\Theta)$ concluding the proof.
\end{proof}
We now have to define one more object (remember that $v$ was defined in lemma \ref{lem:Definition_v}):
\begin{lemma}\label{lem:Definition_K}
	There exist $K_g^L\in\textrm{Cone}_L(\alpha_0,\theta)$ and $K_g^R\in\textrm{Cone}_R(\alpha_0,\theta)$ such that
	\begin{equation}
		v^\dagger W_g v W_g^\dagger=K_g^L\otimes K_g^R=K_g
	\end{equation}
	and they are unique (up to a phase). They satisfy the identity
	\begin{equation}
		\Ad{K^R_g}\circ\pi_0=\pi_0\circ \alpha_0\circ \tau^{-1}\circ \eta_g^R\circ\beta_g^{RU}\circ\tau\circ(\beta_g^{RU})^{-1}\circ(\eta_g^{R})^{-1}\circ\alpha_0^{-1}.\quad\footnote{Observe in particular that $\Theta$ has cancelled out}
	\end{equation}
\end{lemma}
\begin{proof}
	By some straightforward calculation we have that
	\begin{align}
		\Ad{K_g}\circ\pi_0&=\Ad{v^\dagger W_g v W_g^\dagger}\circ\pi_0\\
		&=\bigotimes_{\sigma=L,R}\pi_\sigma\circ\alpha_\sigma\circ\tau^{-1}\circ \eta_g^\sigma\circ\beta_g^{\sigma U}\circ\tau\circ(\beta_g^{\sigma U})^{-1}\circ(\eta_g^{\sigma})^{-1}\circ\alpha_\sigma^{-1}.
	\end{align}
	Using lemma \ref{lem:UsingIrreducibilityAndWignerTheorem} concludes the proof that these unitaries exist and are unique up to a $G-$dependent phase.
\end{proof}
\subsection{Definition of the index}\label{sec:DefinitionH2Index}
\begin{lemma}\label{lem:Definition2Cochain}
	There exists a $C:G^2\rightarrow U(1)$ such that 
	\begin{equation}\label{eq:Definition2Cochain}
		K_g^R\Ad{W_g}\left(K_h^R\Ad{W_hW_{gh}^\dagger}\left((K_{gh}^R)^\dagger\right)\right)u_
		R(g,h)=C(g,h)v^\dagger u_R(g,h)v
	\end{equation}
	for all $g,h\in G.$
\end{lemma}
\begin{proof}
	Since the GNS representation is irreducible this is equivalent to showing that the left and righthandside of equation \eqref{eq:Definition2Cochain} have the same adjoint action on the GNS representation. We first prove the result for the full tensor product. By using the definition of $u(g,h)$ we get
	\begin{align}\label{eq:ProofOf:lem:Definition2CochainFirstEquation}
		v^\dagger u_L(g,h)v v^\dagger u_R(g,h) v&=v^\dagger (u_L(g,h)\otimes u_R(g,h)) v\\
		&=v^\dagger W_g W_h W_{gh}^{-1}v.
	\end{align}
	Now using the definition of $K_g$ gives:
	\begin{align}
		\eqref{eq:ProofOf:lem:Definition2CochainFirstEquation}&=K_gW_g v^\dagger W_h W_{gh}^{-1}v\\
		&=K_gW_g K_h W_h v^\dagger W_{gh}^{-1}v\\
		&=K_gW_g K_h W_h W_{gh}^\dagger K_{gh}^\dagger\\
		&=K_gW_g K_h W_h W_{gh}^\dagger K_{gh}^\dagger W_{gh}W_h^\dagger W_g^\dagger W_gW_hW_{gh}^\dagger\\
		&=K_g\Ad{W_g}\left(K_h\Ad{W_hW_{gh}^\dagger}\left(K_{gh}^\dagger\right)\right)u_L(g,h)\otimes u_
			R(g,h).
	\end{align}
	Using lemma \ref{lem:AdjointOverConeIsInCone} we get that
	\begin{align}
		&(K_g^L\otimes K_g^R)\Ad{W_g}\left((K_h^L\otimes K_h^R)\Ad{W_hW_{gh}^\dagger}\left((K_{gh}^L\otimes K_{gh}^R)^{-1}\right)\right)\\
		&=K_g^L\Ad{W_g}\left(K_h^L\Ad{W_hW_{gh}^\dagger}\left((K_{gh}^L)^\dagger\right)\right)\otimes K_g^R\Ad{W_g}\left(K_h^R\Ad{W_hW_{gh}^\dagger}\left((K_{gh}^R)^\dagger\right)\right)
	\end{align}
	concluding the proof.
\end{proof}
\begin{lemma}
	The function $C$ as defined in lemma \ref{lem:Definition2Cochain} is a 2-cochain.
\end{lemma}
\begin{proof}
	Take lemma 2.4 from \cite{ogata2021h3gmathbb}. There it is stated that there exists a 3-cochain $C'$ such that
	\begin{equation}\label{eq:defintion3CochainProof2Cochain}
		u_R(g,h)u_R(gh,k)u_R(g,hk)^\dagger\Ad{W_g}(u_R(h,k)^\dagger)=C'(g,h,k)\id.
	\end{equation}
	It is clear that this 3-cochain is invariant under the substitution
	\begin{align}
		W_g&\rightarrow v^\dagger W_g v&u_R(g,h)&\rightarrow v^\dagger u_R(g,h)v.
	\end{align}
	If we now prove that it is also invariant under the substitution
	\begin{align}\label{eq:SubstitutionForProofCochain}
		W_g&\rightarrow K_g W_g&u_R(g,h)&\rightarrow K_g^R\Ad{W_g}\left(K_h^R\Ad{W_hW_{gh}^\dagger}\left((K_{gh}^R)^\dagger\right)\right)u_
		R(g,h)
	\end{align}
	we have proved our result because using equation \eqref{eq:Definition2Cochain} we then get that
	\begin{equation}
		\stkout{C'(g,h,k)}=C(h,k)C(gh,k)^{-1}C(g,hk)C(g,h)^{-1}\stkout{C'(g,h,k)}
	\end{equation}
	proving the result. The invariance of the three cochain is proven in lemma \ref{lem:3cochainIsInvariant}.
\end{proof}
Our translation index is now defined as
\begin{definition}
	Let $C:G^2\rightarrow U(1)$ be the 2-cochain defined in \ref{lem:Definition2Cochain}. Take $\phi:G^2\rightarrow\TT$ such that $C(g,h)=\exp(i\phi(g,h))$ then we define the index as
	\begin{equation}
	\textrm{Index}^{\AA,U}(\theta,\tilde{\beta}_g,\eta_g,\alpha_0,\Theta,\omega,\omega_0)\defeq\expval{\phi}\in H^2(G,\TT)
	\end{equation}
	and (as advertised) it is only a function of the automorphisms (and the product state) not on the choice of the GNS triple of $\omega_0$ or on the choice of phases in $W_g,u_L(g,h),u_R(g,h),v,K_g^L$ and $K_g^R$.\footnote{Even though we explicitly wrote down the on site group action $U$, this index is only dependent on $\Ad{U}$.}
\end{definition}
\begin{proof}
	Clearly the construction is invariant under the choice of GNS triple since this simply amounts to an adjoint action by some unitary on every operator. Now we will show that it is invariant under the choice of phases of our operators. Clearly the 2-cochain $C$ is invariant under
	\begin{align}
		u_L(g,h)&\rightarrow \alpha(g)\alpha(g)\alpha(gh)^{-1}\beta(g,h)^{-1} u_L(g,h)&u_R(g,h)&\rightarrow \beta(g,h)u_R(g,h)\\
		W_g&\rightarrow\alpha(g)W_g&v&\rightarrow \gamma v.
	\end{align}
	Under the transformation
	\begin{align}
		K_g^L&\rightarrow \delta(g)^{-1}K_g^L&K_g^R&\rightarrow \delta(g)K_g^R
	\end{align}
	we get $C(g,h)\rightarrow \delta(g)\delta(h)\delta(gh)^{-1}C(g,h)$ which is clearly still in the same equivalence class concluding the proof.
\end{proof}
\subsection{The index is independent of the choices we made}\label{sec:IndexIsInvariantUnderChoices}
In this section we will show that the index is only dependent on $\omega$ and not on the choices of our automorphisms nor on $\omega_0$. First we show independence of $\alpha$ and its decomposition.
\begin{lemma}
	Take $\omega_{01},\omega_{02}\in\PP(\AA)$ product states and let $\alpha_1,\alpha_2\in\Aut{\AA}$ be such that
	\begin{equation}
		\omega_{01}\circ\alpha_1=\omega_{02}\circ\alpha_2=\omega.
	\end{equation}
	Let $V_{11},V_{12}\in\UU(\AA)$, $\alpha_{L/R,1},\alpha_{L/R,2}\in\Aut{\AA_{L/R}}$ and $\Theta_1,\Theta_2\in \Aut{\AA_{W(C_\theta)^c}}$ be such that
	\begin{align}
		\alpha_1&=\Ad{V_{11}}\circ\alpha_{01}\circ\Theta_1&\alpha_2&=\Ad{V_{12}}\circ\alpha_{02}\circ \Theta_2
	\end{align}
	with $\alpha_{0,i}=\alpha_{L,i}\otimes\alpha_{R,i}$, then
	\begin{equation}
		\textrm{Index}^{\AA,U}(\theta,\tilde{\beta}_g,\eta_g,\alpha_{0,1},\Theta_1,\omega,\omega_{01})=\textrm{Index}^{\AA,U}(\theta,\tilde{\beta}_g,\eta_g,\alpha_{0,2},\Theta_2,\omega,\omega_{02}).
	\end{equation}
\end{lemma}
\begin{proof}
	We will first prove the result in the case that $\omega_0=\omega_{01}=\omega_{02}$ and then generalise this result. Since $\omega_0\circ\alpha_2\circ\alpha_1^{-1}=\omega_0$ there exists a $\tilde{x}\in\UU(\HH_0)$ such that
	\begin{equation}
		\pi_0\circ\alpha_2\circ\alpha_1^{-1}=\Ad{\tilde{x}}\circ\pi_0.
	\end{equation}
	Now define $x\in\UU(\HH_0)$ to be
	\begin{equation}
		x\defeq \pi_0(V_{12}^\dagger)\tilde{x} \pi_0(V_{11})
	\end{equation}
	then
	\begin{equation}
		\pi_0\circ\alpha_{02}\circ\Theta_2=\Ad{x}\circ\pi_0\circ\alpha_{01}\circ\Theta_1.
	\end{equation}
	Now take $W_{g,1},u_{R,1}(g,h)$ and $K^R_{g,1}$ to be the operators belonging to the first choice (with arbitrary phases). 
	We have (see \cite{ogata2021h3gmathbb} lemma 2.11)
	\begin{align}
		\Ad{xW_{g,1}x^\dagger}\circ\pi_0&=\pi_0\circ \alpha_{02}\circ\Theta_2\circ\eta_g\circ\beta_g^U\circ\Theta_2^{-1}\circ\alpha_{02}^{-1},\\
		\Ad{xu_{R,1}(g,h)x^\dagger}\circ\pi_0&=\pi_0\circ \alpha_{02}\circ\eta_g^R\circ\beta_g^{RU}\eta_h^R\beta_{h}^{RU}(\beta_{gh}^{RU})^{-1}(\eta_{gh}^R)^{-1}\circ\alpha_{02}^{-1}
	\end{align}
	and through similar arguments we get
	\begin{align}
		\Ad{xvx^\dagger}\circ\pi_0&=\pi_0\circ\alpha_{02}\circ\Theta_2\circ\tau\circ\Theta_2^{-1}\circ\alpha_{02}^{-1}\\
		\Ad{xK^R_{g,1}x^\dagger}\circ\pi_0&=\pi_0\circ \alpha_{02}\circ\tau^{-1}\circ\eta_g^R\circ\beta_g^{RU}\circ\tau\circ(\beta_g^{RU})^{-1}\circ(\eta^R_g)^{-1}\circ\alpha_{02}^{-1}.
	\end{align}
	This shows that $xW_{g,1}x^\dagger,xu_{R,1}(g,h)x^\dagger$ and $xK^R_{g,1}x^\dagger$ are operators belonging to the second choice (with our new translation operator). Since our index is invariant under this substitution this concludes the proof when $\omega_0=\omega_{01}=\omega_{02}$. Now suppose that $\omega_{01}\neq\omega_{02}$. Since they are both product states there exists a $\gamma\in\Aut{\AA}$ satisfying $\omega_{02}=\omega_{01}\circ\gamma$ that is of the form $\gamma=\gamma^L\otimes\gamma^R$. We now have
	\begin{equation}
		\textrm{Index}(\theta,\tilde{\beta}_g,\eta_g,\alpha_{0,2},\Theta_2,\omega,\omega_{02})=\textrm{Index}(\theta,\tilde{\beta}_g,\eta_g,\alpha_{0,2},\Theta_2,\omega,\omega_{01}\circ\gamma)=\textrm{Index}(\theta,\tilde{\beta}_g,\eta_g,\gamma\circ\alpha_{0,2},\Theta_2,\omega,\omega_{01})
	\end{equation}
	concluding the proof.
\end{proof}
We now show that the index is invariant under some transformation parametrised by the group $\IAC_R$:
\begin{lemma}\label{lem:TransformationUnderDelta}
	Take $\omega_0,\theta,\alpha_0,\Theta$ and $\eta_g$ as usual, take $v,W_{g,1},u_{\sigma,1}(g,h)$ and $K_{g,1}^\sigma$ the operators corresponding to these automorphisms and take $\delta^\sigma_g\in\IAC_\sigma^W(\alpha_0,\theta,\Theta)$ (for all $\sigma\in\{L,R\}$ and all $g\in G$). Define
	\begin{align}
		W_{g,2}&\defeq\delta_g W_{g,1}\\
		u_{\sigma,2}(g,h)&\defeq \delta_g^\sigma W_{g,1}\delta_h^\sigma W_{g,1}^\dagger u_{\sigma,1}(g,h)(\delta_{gh}^\sigma)^\dagger\\
		K^\sigma_{g,2}&\defeq v^\dagger \delta_g^\sigma v K_{g,1}^\sigma (\delta_g^\sigma)^\dagger
	\end{align}
	then equation \eqref{eq:Definition2Cochain}, defining the index of $v,W_{g,1},u_{\sigma,1}(g,h)$ and $K_{g,1}^\sigma$, is still valid when we replace these operators by $v,W_{g,2},u_{\sigma,2}(g,h)$ and $K_{g,2}^\sigma$ respectively. The two cochain also remains unchanged.
\end{lemma}
\begin{proof}
	This is proven in lemma \ref{lem:TransformationUnderDeltaAppendix}.
\end{proof}
We will now show that the index is independent on the choice of $\tilde{\beta}_g$ and its decomposition.
\begin{lemma}\label{lem:InvarianceUnderChoiceBeta}
	Take $\tilde{\beta}_{g,1},\tilde{\beta}_{g,2}\in\Aut{\AA},V_{g,21},V_{g,22}\in\UU(\AA),\eta_{g,1}^L,\eta_{g,2}^L\in \Aut{\AA_L\cap\AA_{C_\theta}}$ and $\eta_{g,1}^R,\eta_{g,2}^R\in \Aut{\AA_R\cap\AA_{C_\theta}}$ such that there exist $V_{g,21},V_{g,22}\in\UU(\AA)$ satisfying
	\begin{align}\label{eq:InvarianceUnderChoiceBetaTwoBetas}
		\tilde{\beta}_{g,1}&=\Ad{V_{g,21}}\circ\eta_{g,1}\circ\beta^U_g&\tilde{\beta}_{g,2}&=\Ad{V_{g,22}}\circ\eta_{g,2}\circ\beta^U_g
	\end{align}
	and
	\begin{equation}
		\omega\circ\tilde{\beta}_{g,1}=\omega\circ\tilde{\beta}_{g,2}=\omega
	\end{equation}
	then
	\begin{equation}
		\textrm{Index}(\theta,\tilde{\beta}_{g,1},\eta_{g,1},\alpha_{0},\Theta,\omega,\omega_0)=\textrm{Index}(\theta,\tilde{\beta}_{g,2},\eta_{g,2},\alpha_{0},\Theta,\omega,\omega_0).
	\end{equation}
\end{lemma}
\begin{proof}
	Take 
	\begin{equation}\label{eq:InvarianceUnderChoiceBetaAlphaDecomposition}
		\alpha=\Ad{V_1}\circ\alpha_{0}\circ\Theta
	\end{equation}
	the usual decomposition. Since
	\begin{equation}
		\omega_0\circ\alpha\circ\tilde{\beta}_{g,1}\circ(\tilde{\beta}_{g,2})^{-1}=\omega_0\circ\alpha
	\end{equation}
	there exist $\tilde{\delta}_g\in\UU(\HH_0)$ such that
	\begin{equation}
		\Ad{\tilde{\delta}_g}\circ\pi_0\circ\alpha=\pi_0\circ\alpha\circ\tilde{\beta}_{g,2}\circ(\tilde{\beta}_{g,1})^{-1}.
	\end{equation}
	Inserting equation \eqref{eq:InvarianceUnderChoiceBetaTwoBetas} and \eqref{eq:InvarianceUnderChoiceBetaAlphaDecomposition} in this gives
	\begin{equation}
		\Ad{\tilde{\delta}_g}\circ\pi_0\circ\Ad{V_1}\circ\alpha_0\circ\Theta=\pi_0\circ\Ad{V_1}\circ\alpha_0\circ\Theta\circ\Ad{V_{g,21}}\circ\eta_{g,1}\circ\eta_{g,2}^{-1}\circ\Ad{V_{g,22}^\dagger}.
	\end{equation}
	Putting the $V_1$'s to the other side gives:
	\begin{equation}
		\Ad{\pi_0(V_1^\dagger) \tilde{\delta}_g\pi_0(V_1)}\circ\pi_0\circ\alpha_0\circ\Theta=\pi_0\circ\alpha_0\circ\Theta\circ\Ad{V_{g,21}}\circ\eta_{g,1}\circ\eta_{g,2}^{-1}\circ\Ad{V_{g,22}^\dagger}.
	\end{equation}
	Doing the same for the $V_{g,21}$ and $V_{g,22}$ now gives
	\begin{align}
		\Ad{\pi_0\circ\alpha_0\circ\Theta(V_{g,21}^\dagger)\pi_0(V_1^\dagger)\tilde{\delta}_g\pi_0(V_1)}\circ\pi_0\circ\alpha_0\circ\Theta\circ\Ad{V_{g,22}}&=\pi_0\circ\alpha_0\circ\Theta\circ\eta_{g,2}\circ(\eta_{g,1})^{-1}\\
		\Ad{\pi_0\circ\alpha_0\circ\Theta(V_{g,21}^\dagger)\pi_0(V_1^\dagger)\tilde{\delta}_g\pi_0(V_1)\pi_0\circ\alpha_0\circ\Theta(V_{g,22})}\circ\pi_0&=\pi_0\circ\alpha_0\circ\eta_{g,2}\circ(\eta_{g,1})^{-1}\circ\alpha_0^{-1}.
	\end{align}
	Since the last equation is split we have by lemma \ref{lem:UsingIrreducibilityAndWignerTheorem} that we can take $\delta_g^L\in\textrm{Cone}_L^W(\alpha_0,\theta)$ and $\delta_g^R\in\textrm{Cone}_R^W(\alpha_0,\theta)$ such that
	\begin{equation}
		\delta_g^L\otimes\delta_g^R=\pi_0\circ\alpha_0\circ\Theta(V_{g,21}^\dagger)\pi_0(V_1^\dagger)\tilde{\delta}_g\pi_0(V_1)\pi_0\circ\alpha_0\circ\Theta(V_{g,22}).
	\end{equation}
	Take $W_{g,1},u_{R,1}(g,h)$ and $K^R_{g,1}$ to be the operators belonging to the first choice (with arbitrary phases). Define
	\begin{align}
		W_{g,2}&\defeq\delta_g W_{g,1}\\
		u_{R,2}(g,h)&\defeq \delta_g^R W_{g,1}\delta_h^R W_{g,1}^\dagger u_{R,1}(g,h)(\delta_{gh}^R)^\dagger\\
		K^R_{g,2}&\defeq v^\dagger \delta_g^R v K_{g,1}^R (\delta_g^R)^\dagger
	\end{align}
	then by construction $W_{g,2},u_{R,2}(g,h)$ and $K^R_{g,2}$ are operators belonging to the second choice. Now using lemma \ref{lem:TransformationUnderDelta} concludes the proof.
\end{proof}
\begin{lemma}
	The index is independent of the choice of angle $\theta$.
\end{lemma}
\begin{proof}
	Take $0<\theta_1<\theta_2<\pi/2$. Take $\alpha\in \QAut{\AA}$ and (for all $\sigma\in\{L,R\}$) take $\eta_{g,1}^\sigma\in\Aut{\AA_L\cap\AA_{C_{\theta_1}}}$ and $\eta_{g,2}^\sigma\in\Aut{\AA_L\cap\AA_{C_{\theta_2}}}$ to be operators belonging to $\tilde{\beta}_{g,1}$ and $\tilde{\beta}_{g,2}$ leaving $\omega$ invariant. Since $\Aut{\AA_L\cap\AA_{C_{\theta_1}}}\subset \Aut{\AA_L\cap\AA_{C_{\theta_2}}}$ the result now follows from lemma \ref{lem:InvarianceUnderChoiceBeta}.
\end{proof}
Due to all these considerations we will write the index as $\textrm{Index}^{\AA,U}(\omega)$ from here on onward.
\subsection{Example (consistency with conjecture \ref{conj})}\label{sec:OneTranslationDirectionExample}
In this section we will give a special class of translation invariant states that satisfy assumption \ref{assumption}. We start our construction by taking a state $\phi\in\PP(\AA_{L_0})$ that satisfies assumption \ref{assumption1d}.
\begin{lemma}\label{lem:phiExampleConsistentWithConjectureSplitProperty}
	This $\phi$ satisfies the split property.
\end{lemma}
\begin{proof}
	Take $(\HH_L\otimes\HH_R,\pi_L\otimes\pi_R,\Omega_L\otimes\Omega_R)$ a GNS triple of $\phi_0$. By construction $(\HH_L\otimes\HH_R,\pi_L\circ\tilde\alpha_L\otimes\pi_R\circ\tilde\alpha_R,\pi_L\otimes\pi_R(b^\dagger)\Omega_L\otimes\Omega_R)$ is a GNS triple of $\phi$. This concludes the proof that $\phi$ satisfies the split property.
\end{proof}
By the result of \cite{ogata2019classification} this implies that $\phi$ has a well defined 1d SPT index (see appendix \ref{sec:OneDimensionalIndices}). For any $j\in\ZZ$ and $n\in\NN$ take
\begin{align}
	L_j&\defeq \{(x,y)\in\ZZ^2|y=j\}&L_{j}^{n}&\defeq \{(x,y)\in\ZZ^2|y=j,x\in[-n,n]\}\\
	L_{<j}&\defeq \{(x,y)\in\ZZ^2|y<j\}&L_{>j}&\defeq \{(x,y)\in\ZZ^2|y>j\}.
\end{align}
We introduce some additional notation, for any automorphism $\alpha\in\Aut{\AA_{L_0}}$ we define 
\begin{equation}
	\alpha_{(\cdot,j)}\defeq \tau^j\circ\alpha\circ\tau^{-j}.
\end{equation}
We will now define the infinite tensor product state.
\begin{definition}\label{def:InfiniteTensorProductState}
	Take $\phi\in\PP(\AA_{L_0})$ arbitrary. There exists a unique state $\omega$ satisfying that for any $i\in\ZZ$ we have that for any $A\in\AA_{L_i}$ and $B\in\AA_{L_i^c}$
	\begin{equation}
		\omega(A\otimes B)=\phi\circ\tau^{-j}(A)\omega(B).
	\end{equation}
\end{definition}
\begin{proof}
	Clearly this condition gives a construction by induction for $\omega(A)$ for each $A\in\AA_{\text{loc}}$. For general elements we define
	\begin{equation}
		\omega(A)\defeq \lim_{n\rightarrow\infty}\omega(A_n)
	\end{equation}
	where $A_n$ is a sequence in $\AA_{\text{loc}}$ converging in $\AA$.
\end{proof}
We have that:
\begin{lemma}\label{lem:TensorProductStateHasWellDefinedH^2Index}
	Let $\omega$ be the infinite tensor product of a state $\phi$ that satisfies assumption \ref{assumption1d} then $\omega$ satisfies assumption \ref{assumption}.
\end{lemma}
\begin{proof}
	The proof is in lemma \ref{lem:TensorProductStateHasWellDefinedH^2IndexAppendix}.
\end{proof}
This shows that $\omega$ has a well defined 2d translation index. We will now show that $\textrm{Index}(\omega)=\textrm{Index}_{1d}(\phi)$. We now fix a GNS triple of $\omega_0$ that is of the form
\begin{equation}
	\left(\HH_0=\bigotimes_{\substack{\sigma\in\{L,R\}\\ \rho\in\{L_{>-1},L_{-1},L_{<-1}\}}}\HH_{\rho,\sigma},\pi_0=\bigotimes_{\substack{\sigma\in\{L,R\}\\ \rho\in\{L_{>-1},L_{-1},L_{<-1}\}}}\pi_{\rho,\sigma},\Omega_0=\bigotimes_{\substack{\sigma\in\{L,R\}\\ \rho\in\{L_{>-1},L_{-1},L_{<-1}\}}}\Omega_{\rho,\sigma}\right)
\end{equation}
where the $\pi_{\rho,\sigma}:\AA_{\rho\cap\sigma}\rightarrow\BB(\HH_{\rho,\sigma})$ are all irreducible representations.
\begin{remark}\label{rem:GNS_One_Dimensional}
	We clearly have (by construction) that
	\begin{equation}
		\pi_{L_{-1},L}\circ\alpha_L|_{L_{-1}}\otimes \pi_{L_{-1},R}\circ\alpha_R|_{L_{-1}}
	\end{equation}
	is a GNS representation of $\phi$. This implies that if we take any $k^R:G\rightarrow \UU(\HH_{L_{-1},R})$ such that
	\begin{equation}
		\Ad{k^R(g)}\circ\pi_{L_{-1},R}\circ\alpha_R|_{L_{-1}}=\pi_{L_{-1},R}\circ\alpha_R|_{L_{-1}}\circ\beta_{g}^{L_{-1}\cap R}
	\end{equation}
	then there exists a 2 cochain $C$ satisfying that
	\begin{equation}
		k^R(g)k^R(h)k^R(gh)^{-1}=C(g,h)\id_{\HH_{L_{-1},R}}
	\end{equation}
	and that the equivalence class this cochain is in, is given by $\textrm{Index}_{1d}(\phi)$.
\end{remark}
Let $\tilde k:G\rightarrow \UU(\HH_{L_{-1}})$ be the unique operator that satisfies
\begin{align}
	\Ad{\tilde{k}_g}\circ\pi_{L_{-1}}&=\pi_{L_{-1}}\circ \circ\alpha|_{L_{-1}}\circ\beta_g^{L_{-1}}\circ \alpha^{-1}|_{L_{-1}}&\tilde k_g\Omega_{L_{-1}}&=\Omega_{L_{-1}}.
\end{align}
Similarly, let $\tilde{w}:G\rightarrow\UU(\HH_{L_{>-1},L}\otimes\HH_{L_{>-1},R})$ be the unique operator such that
\begin{align}
	\Ad{\tilde w_{g}}\circ\pi_{L_{>-1}}&=\pi_{L_{>-1}}\circ\alpha|_{L_{>-1}}\circ\beta_g^{\tau^{i}(U)}\circ \alpha^{-1}|_{L_{>-1}}&\tilde w_{g}\Omega_{L_{>-1}}&=\Omega_{L_{>-1}}.
\end{align}
Clearly both functions are (linear) representation of the group. Now define
\begin{equation}\label{eq:ChoiceOfW_g_ExampleH2Index}
	W_g=\pi_{0}(V_1)^{\dagger}(\tilde{w}_g\otimes\id_{H_{L_{-1}}}\otimes\id_{\HH_{L_{<-1}}}) \pi_{0}(V_1).
\end{equation}
This operator valued function is also a linear representation and satisfies the conditions indicated in lemma \ref{lem:Definition_W_And_u}. Since $W_g$ is a linear representation we get that $W_gW_hW_{gh}^{-1}=\id_{\HH_0}$. This implies that we can take $u_\sigma(g,h)=\id_{\bigotimes_{\rho\in\{L_{>-1},L_{-1},L_{<-1}\}}\HH_{\sigma,\rho}}$ (for any $\sigma\in\{L,R\}$). All that is now left is to calculate $K^\sigma_g\in\UU(\HH_\sigma)$. We get that
\begin{align}
	K_g&=v^\dagger W_g v W_g^\dagger\\
	&=v^\dagger \pi_{0}(V_1)^{\dagger}(\tilde{w}_g\otimes\id_{\HH_{L_{-1}}}\otimes\id_{\HH_{L_{<-1}}}) \pi_{0}(V_1) v W_g^\dagger\\
	&=\pi_{0}(V_1)^{\dagger}\tilde v^\dagger(\tilde{w}_g\otimes\id_{\HH_{L_{-1}}}\otimes\id_{\HH_{L_{<-1}}}) \tilde v \pi_{0}(V_1) W_g^\dagger.
\end{align}
Notice however that $\tilde v^\dagger(\tilde{w}_g\otimes\id_{\HH_{L_{-1}}}\otimes\id_{\HH_{L_{<-1}}}) \tilde v$ and $\tilde{w}_g\otimes\tilde{k}_g\otimes\id_{\HH_{L_{<-1}}}$ both leave the cyclic vector invariant and have the same adjoint action on the GNS representation. By the uniqueness of such operators we get that
\begin{equation}
	K_g=\pi_{0}(V_1)^{\dagger}(\tilde{w}_g\otimes\tilde{k}_g\otimes\id_{\HH_{L_{<-1}}}) \pi_{0}(V_1) W_g^\dagger.
\end{equation}
Using the adjoint of equation \eqref{eq:ChoiceOfW_g_ExampleH2Index} this gives
\begin{align}
	K_g&=\pi_{0}(V_1)^{\dagger}(\id_{H_{L_{>-1}}}\otimes \tilde k_g \otimes\id_{\HH_{L_{<-1}}}) \pi_{0}(V_1)\\
	&=\id_{H_{L_{>-1}}}\otimes \pi_{L_{-1}}(b)^\dagger \tilde k_g \pi_{L_{-1}}(b) \otimes\id_{\HH_{L_{<-1}}}
\end{align}
where $\tilde{v}=\pi_0(V_1)^\dagger v\pi_0(V_1)$. Now there exists a $k^L:G\rightarrow \UU(\HH_{L_{-1},L})$ and a $k^R:G\rightarrow \UU(\HH_{L_{-1},R})$ such that
\begin{equation}
	k^L_g\otimes k^R_g=\pi_{L_{-1}}(b)^\dagger \tilde k_g \pi_{L_{-1}}(b)
\end{equation}
and these $k^\sigma_g$ will satisfy what was written in remark \ref{rem:GNS_One_Dimensional}. Define $K^\sigma_g=k^\sigma_g\otimes\id_{\HH_{L_{>-1},\sigma}}\otimes\id_{\HH_{L_{<-1},\sigma}}$. Notice that we have (by construction) that $\forall g,h\in G$
\begin{equation}
	[K^\sigma_g\otimes\id_{\HH_{\ZZ^2/\sigma}},W_h]=0.
\end{equation}
We now get (using this equation and the fact that $W_g$ is a representation)
\begin{align}
	&K_g^R W_g K_h^R W_h W_{gh}^\dagger (K_{gh}^R)^\dagger \stkout{W_{gh}W_h^\dagger W_g^\dagger u_R(g,h)}\\
	&=\stkout{W_g W_h W_{gh}^\dagger} K_g^R K_h^R (K_{gh}^R)^\dagger\\
	&=k_g^R k_h^R (k_{gh}^R)^\dagger\otimes \id_{\HH_{L_{>-1},\sigma}}\otimes\id_{\HH_{L_{<-1},\sigma}}
\end{align}
and by remark \ref{rem:GNS_One_Dimensional} this gives that $C(g,h)=\tilde{C}(g,h)$.
\subsection{Index is invariant under locally generated automorphisms}\label{sec:IndexInvariantUnderLGA}
The goal of this section is now to show that the index we constructed is invariant under locally generated automorphisms (the final proof of this statement is under theorem \ref{thrm:IndexInvariantUnderLGA}). To this end let $H\in\BB_{F_\phi}([0,1])$ be $G$-invariant, translation invariant (in the vertical direction) one parameter family of interactions. Define furthermore for notational simplicity in this section $\Hsplit=H_L+H_R$ (with $H_L$ and $H_R$ the restrictions of $H$ as defined in \ref{sec:Interactions}). Clearly we have that $\gamma^{\Hsplit}_{t;s}=\gamma^{H_L}_{t;s}\otimes\gamma^{H_R}_{t;s}$ and we still have that $\gamma^{\Hsplit}_{t;s}\circ\tau=\tau\circ\gamma^{\Hsplit}_{t;s}$ (just like we have for $H$).\\\\
For the remainder of the section we will use a decomposition using the following lemma:
\begin{lemma}\label{lem:DefinitionOfGroupMorphismVAutEquation}
	Take $0<\theta<\pi/2$ and $\Theta\in \Aut{\AA_{W(C_\theta)^c}}$. There exist $\Phi^U_{0;1}\in\Aut{\AA_{W(C_\theta)^c\cap U}}$ and $\Phi^D_{0;1}\in\Aut{\AA_{W(C_\theta)^c\cap D}}$, both commuting with $\beta_g$, such that there exists some $a\in\UU(\AA)$ satisfying that
	\begin{equation}\label{eq:DefinitionOfGroupMorphismVAutEquation}
	\gamma^H_{0;1}\circ\gamma^{\Hsplit}_{1;0}=\Ad{a}\circ \Phi^U_{0;1}\otimes\Phi^D_{0;1}.
	\end{equation}
\end{lemma}
\begin{proof}
	This follows from the fact that $\gamma^H_{0;1}\circ\gamma^{\Hsplit}_{1;0}\in \textrm{GVAut}_1(\AA)$ (see lemma \ref{lem:PropertiesLocallyGeneratedAutomorphisms} part 2).
\end{proof}
In what follows, we will define $\tilde{a}\defeq \pi_0\circ\alpha_0\circ\Theta(a)$. The main property we will use of this operator is that it satisfies the following lemma:
\begin{lemma}\label{lem:PropertyTilde_a}
	Let $A\in\UU(\AA_{W(C_\theta)\cap\sigma})$ then
	\begin{equation}
		\Ad{\tilde{a}}\circ\pi_0\circ\alpha_0(A)=\Ad{\tilde{a}}\circ\pi_0\circ\alpha_0\circ\Theta(A)=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{\Hsplit}_{1;0}(A).
	\end{equation}
\end{lemma}
\begin{proof}
	Using lemma \ref{lem:DefinitionOfGroupMorphismVAutEquation} we get that
	\begin{align}
		\Ad{\tilde{a}}\circ\pi_0\circ\alpha_0\circ\Theta(A)&=\pi_0\circ\alpha_0\circ\Theta\circ\Ad{a}(A)\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{\Hsplit}_{1;0}\circ\Phi^U_{1;0}\otimes\Phi^D_{1;0}(A)\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{\Hsplit}_{1;0}(A)
	\end{align}
here $\Phi_{1;0}=\Phi_{0;1}^{-1}$. This concludes the proof.
\end{proof}
We will then use this property to define a morphism:
\begin{lemma}\label{lem:DefinitionOfGroupMorphism}
	Let $\tilde{a}=\pi_0\circ\alpha_0\circ\Theta(a)$ and define the map
	\begin{align}
		\phi_{1,\sigma}&:\IAC_\sigma(\alpha_0,\theta,\Theta) \rightarrow \UU(\HH)\\
		\nonumber
		&:x=\pi_0\circ\alpha_0\circ\Theta(A)y\mapsto \phi_1(x)=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{\Hsplit}_{1;0}(A)\tilde{a}y\tilde{a}^\dagger
	\end{align}
	where $A\in\UU(\AA_\sigma)$ and $y\in\textrm{Cone}_\sigma(\alpha_0,\theta)$. This map satisfies that
	\begin{enumerate}
		\item  for (the unique) $\xi\in\Aut{\AA_{W(C_\theta)\cap\sigma}}$ such that
		\begin{equation}
			\Ad{y}\circ\pi_0\circ\alpha_0=\pi_0\circ\alpha_0\circ\xi
		\end{equation}
		we get that
		\begin{equation}\label{eq:ConditionDefinitionOfGroupMorphism}
			\Ad{\phi_{1,\sigma}(x)}\circ\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{\Hsplit}_{1;0}=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{\Hsplit}_{1;0}\circ\Ad{A}\circ\xi.
		\end{equation}
		\item it is well defined (independent of the choice of $A$ and $y$).
		\item it is a group homomorphism.
		\item $\tilde{a}^\dagger \phi_1(x)\tilde{a}\in\IAC_\sigma(\alpha_0,\theta,\Theta\circ \Phi^U_{0;1}\otimes\Phi^D_{0;1})$.
		\item if $x\in \IAC_\sigma^W(\alpha_0,\theta,\Theta)$ then  $\tilde{a}^\dagger \phi_1(x)\tilde{a}\in\IAC_\sigma^W(\alpha_0,\theta,\Theta\circ \Phi^U_{0;1}\otimes\Phi^D_{0;1})$.
	\end{enumerate}
\end{lemma}
\begin{proof}
	The proof is presented after lemma \ref{lem:DefinitionOfGroupMorphismAppendix}.
\end{proof}
We now have to extend the above definition to the group
\begin{equation}
	\IAC_{L\times R}(\alpha_0,\theta,\Theta)=\{ab=ba|a\in\IAC_{L}(\alpha_0,\theta,\Theta),b\in\IAC_{R}(\alpha_0,\theta,\Theta)\}.
\end{equation}
\begin{lemma}\label{lem:extensionOfPhi1Definition}
	Define
	\begin{equation}
		\phi_1:\IAC_{L\times R}(\alpha_0,\theta,\Theta)\rightarrow\UU(\HH):ab\mapsto \phi_{1,L}(a)\phi_{1,R}(b)
	\end{equation}
	where $a\in \IAC_{L}(\alpha_0,\theta,\Theta)$ and $b\in \IAC_{R}(\alpha_0,\theta,\Theta)$. This satisfies two points.
	\begin{enumerate}
		\item It is well defined, by which we mean that for any $a,\tilde{a}\in \IAC_{L}(\alpha_0,\theta,\Theta)$ and for any $b,\tilde{b}\in \IAC_{R}(\alpha_0,\theta,\Theta)$ such that $ab=\tilde{a}\tilde{b}$ we have that
		\begin{equation}
			\phi_{1,L}(a)\phi_{1,R}(b)=\phi_{1,L}(\tilde a)\phi_{1,R}(\tilde b).
		\end{equation}
		\item It is still a group homomorphism.
	\end{enumerate}
\end{lemma}
\begin{proof}
	This proof is done under lemma  \ref{lem:extensionOfPhi1DefinitionAppendix}.
\end{proof}
\begin{lemma}\label{lem:DefinitionOfWgMap}
	Define again $\tilde{a}$ through equation \eqref{eq:DefinitionOfGroupMorphismVAutEquation}. Let
	\begin{equation}
		\phi_2:\{v^{-p} W_g v^{p}|g\in G,p\in\{-1,0,1\}\}\rightarrow \UU(\HH):v^{-p} W_g v^{p}\mapsto \tilde{a}v^{-p} W_g v^{p}\tilde{a}^\dagger.
	\end{equation}
	This satisfies
	\begin{equation}\label{eq:lemDefinitionOfWgMapCondition}
		\Ad{\phi_2(v^{-p}W_g v^{p})}\circ\pi_0=\pi_0\circ \alpha_0\circ\Theta\circ\gamma^{H}_{0;1}\circ\gamma^{\Hsplit}_{1;0}\circ\tau^{-p}\circ\eta_g\circ\beta_g^U\circ\tau^p\circ\gamma^{\Hsplit}_{0;1}\circ\gamma^{H}_{1;0}\circ\Theta^{-1}\circ\alpha_0^{-1}.
	\end{equation}
\end{lemma}
\begin{proof}
	To show that this indeed satisfies equation \eqref{eq:lemDefinitionOfWgMapCondition} observe that using equation \eqref{eq:DefinitionOfGroupMorphismVAutEquation} we obtain:
	\begin{align}
		&\Ad{\phi_2(v^{-p}W_g v^{p})}\circ\pi_0\\
		&=\pi_0\circ \alpha_0\circ\Theta\circ\Ad{a}\circ\tau^{-p}\circ\eta_g\circ\beta_g^U\circ\tau^p\circ\Ad{a^{\dagger}}\circ\Theta^{-1}\circ\alpha_0^{-1}\\
		&=\pi_0\circ \alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_L}_{1;0}\circ\stkout{\Phi_{0;1}^{-1}}\circ\tau^{-p}\circ\eta_g\circ\beta_g^U\circ\tau^p\circ\stkout{\Phi_{0;1}}\circ\gamma^{\Hsplit}_{0;1}\circ\gamma^H_{1;0}\circ\Theta^{-1}\circ\alpha_0^{-1}.
	\end{align}
	Since $\Phi$ commutes with both the $\tau^{-p}\circ\eta_g\circ\tau^p$ and with the $\beta_g^{\tau^{-p}(U)}$ the result follows.
\end{proof}
\begin{lemma}\label{lem:phi1phi2matchingCondition}
	The $\phi_1$ and $\phi_2$ defined previously satisfy that for any $x\in\IAC_{L\times R}(\alpha_0,\theta,\Theta)$ we have that
	\begin{equation}
		\phi_1(\Ad{W_g}(x))=\Ad{\phi_2(W_g)}(\phi_1(x)).
	\end{equation}
	If additionally $x\in\IAC_{L\times R}^W(\alpha_0,\theta,\Theta)$ we get that
	\begin{align}
		\phi_1(\Ad{v}(x))&=\Ad{v}(\phi_1(x))&\phi_1(\Ad{v^\dagger}(x))&=\Ad{v^\dagger}(\phi_1(x)).
	\end{align}
\end{lemma}
\begin{proof}
	This lemma is proven under lemma \ref{lem:phi1phi2matchingConditionAppendix}.
\end{proof}
\begin{theorem}\label{thrm:IndexInvariantUnderLGA}
	$\textrm{Index}(\omega)=\textrm{Index}(\omega\circ\gamma^H_{0;1})$
\end{theorem}
\begin{proof}
	Take $\alpha\in\QAut{\AA}$ such that $\omega=\omega_0\circ\alpha$ for some product state $\omega_0$. Take $0<\theta_1<\theta_2<\theta_3<\pi/2$ arbitrary. Take $\alpha_L\in\Aut{\AA_L},\alpha_R\in\Aut{\AA_R},V_1\in\UU(\AA)$ and $\Theta\in\Aut{\AA_{W(C_{\theta_3})^c}}$ such that
	\begin{equation}
		\alpha=\Ad{V_1}\circ\alpha_L\otimes\alpha_R\circ\Theta.
	\end{equation}
	Take $\tilde{\beta}_{g,1}$ such that $\omega\circ\tilde{\beta}_{g,1}=\omega$ and such that there exists some $V_{2,g}\in\UU(\AA)$ and some $\eta_g^{L/R}\in\Aut{\AA_{C_{\theta_1}}\cap\AA_{L/R}}$ satisfying
	\begin{equation}
		\tilde{\beta}_{g,1}=\Ad{V_{2,g}}\circ\eta_{g}^L\otimes\eta_{g}^R\circ\beta_g^U.
	\end{equation}
	Take $W_g,u_{L/R}(g,h),v$ and $K_g^{L/R}$ operators belonging to these automorphisms (see lemmas \ref{lem:Definition_W_And_u} and \ref{lem:Definition_K}). Clearly $\alpha\circ\gamma^H_{0;1}$ satisfies $\omega\circ\gamma^{H}_{0;1}=\omega_0\circ\alpha\circ\gamma^{H}_{0;1}$. We also have that $\alpha\circ\gamma^{H}_{0;1}\in\QAut{\AA}$. To show this notice that
	\begin{align}
		\alpha\circ\gamma^{H}_{0;1}&=\Ad{V_1}\circ(\alpha_L\circ\gamma^{H_L}_{0;1}\otimes\alpha_R\circ\gamma^{H_R}_{0;1})\circ\gamma^{\Hsplit}_{1;0}\circ\Theta\circ\gamma^H_{0;1}\\
		&=\Ad{V_1}\circ(\alpha_L\circ\gamma^{H_L}_{0;1}\otimes\alpha_R\circ\gamma^{H_R}_{0;1})\circ\gamma^{\Hsplit}_{1;0}\circ\gamma^{H}_{0;1}\circ\gamma^{H}_{1;0}\circ\Theta\circ\gamma^H_{0;1}.
	\end{align}
	Because of lemma \ref{lem:TwoAngleLemmaPart1} and lemma \ref{lem:PropertiesLocallyGeneratedAutomorphisms} part 2 there exists a $\tilde{\Theta}\in\Aut{\AA_{W(C_{\theta_2})^c}}$ and some $\tilde V_1,A_1\in\UU(\AA)$ such that
	\begin{align}
		\alpha\circ\gamma^H_{0;1}&=\Ad{\tilde V_1}\circ(\alpha_L\circ\gamma^{H_L}_{0;1}\otimes\alpha_R\circ\gamma^{H_R}_{0;1})\circ\tilde\Theta\\
		\label{eq:ProofThatTheH2IndexIsInvariantUnderLGA's_Definition_A1}
		(\alpha_L\circ\gamma^{H_L}_{0;1}\otimes\alpha_R\circ\gamma^{H_R}_{0;1})\circ\tilde\Theta&=\Ad{A_1}\circ \alpha_L\otimes\alpha_R\circ\Theta\circ\gamma^{H}_{0;1}.
	\end{align}
	If we now define the automorphism $\tilde{\beta}_{g,2}=\gamma^{H}_{1;0}\tilde\beta_{g,1}\gamma^{H}_{0;1}$ then this indeed satisfies that $\omega\circ\gamma^{H}_{0;1}\circ\tilde{\beta}_{g,2}=\omega\circ\gamma^{H}_{0;1}$. Define $\tilde\eta_g^\sigma\in\Aut{\AA_{C_{\theta_2}\cap\sigma}}$ through lemma \ref{lem:TwoAngleLemmaPart3}. It satisfies that there exists a $\tilde V_{2,g}\in\UU(\AA),A_{2,g}^{\sigma}\in\UU(\AA_\sigma)$ such that
	\begin{align}
		\label{eq:IndexInvariantUnderLGAEtaTildeDefiniton1}
		\gamma^{H}_{1;0}\tilde{\beta}_g\gamma^{H}_{0;1}&=\Ad{\tilde V_{2,g}}\circ\tilde{\eta}_g^L\otimes\tilde{\eta}_g^R\circ\beta_g^U\\
		\label{eq:IndexInvariantUnderLGAEtaTildeDefiniton2}
		\tilde{\eta}_g^\sigma&=\Ad{A_{2,g}^\sigma}\circ\gamma^{H_\sigma}_{1;0}\circ\eta_g^\sigma\circ\beta_g^{\sigma U}\circ\gamma^{H_\sigma}_{0;1}\circ(\beta_g^{\sigma U})^{-1}.
	\end{align}
	Take $\Phi$ like in equation \eqref{eq:DefinitionOfGroupMorphismVAutEquation} and define
	\begin{equation}
		\phi_1:\IAC_R(\alpha_0,\Theta) \rightarrow \UU(\HH)
	\end{equation}
	the group homomorphism defined from lemma \ref{lem:DefinitionOfGroupMorphism}. Take similarly
	\begin{equation}
		\phi_2:\{W_g|g\in G\}\rightarrow \UU(\HH)
	\end{equation}
	the map defined in \ref{lem:DefinitionOfWgMap} with arbitrary phase. The following operators now belong to $\omega\circ\gamma^{H}_{0;1}:$
	\begin{align}
		\label{eq:IndexInvariantUnderLGANewOperator1}
		\tilde{v}&=\pi_0(A_1)v\pi_0(A_1)^\dagger\\
		\label{eq:IndexInvariantUnderLGANewOperator2}
		\tilde{W}_g&=\pi_0(A_1)\phi_1(\delta^L_g\otimes\delta^R_g)\phi_2( W_g)\pi_0(A_1^\dagger)\\
		\label{eq:IndexInvariantUnderLGANewOperator3}
		\tilde u_\sigma(g,h)&=\pi_0(A_1) \phi_1\left(\delta^\sigma_g W_g\delta^\sigma_h W_g^\dagger u_\sigma(g,h)(\delta^\sigma_{gh})^\dagger\right)\pi_0(A_1)^\dagger\\
		\label{eq:IndexInvariantUnderLGANewOperator4}
		\tilde{K}_g^\sigma&=\pi_0(A_1)\phi_1(v^\dagger \delta_g^\sigma v K_g^\sigma (\delta_g^\sigma)^\dagger) \pi_0(A_1)^\dagger
	\end{align}
	where $\delta^\sigma_g=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^{H_\sigma}_{0;1}(A^\sigma_{2,g})$ and $A_1$ was defined in equation \eqref{eq:ProofThatTheH2IndexIsInvariantUnderLGA's_Definition_A1}. The fact that the index is invariant under $\Ad{\pi_0(A_1)}$ and under $\phi(\cdot)$ is just due to the fact that both transformations are homomorphisms. To show that it is invariant under the transformation with de $\delta^\sigma_g$ we invoke lemma \ref{lem:TransformationUnderDelta}. All that is left to show is that operators \eqref{eq:IndexInvariantUnderLGANewOperator1} through \eqref{eq:IndexInvariantUnderLGANewOperator4} are indeed operators belonging to $\omega\circ\gamma^{H}_{0;1}$. To do this we first state that a small calculation shows that $\forall x\in\UU(\HH_0)$ satisfying that $\exists\xi\in\Aut{\AA}$ such that
	\begin{equation}
		\Ad{x}\circ\pi_0\circ\alpha_0\circ\Theta=\pi_0\circ\alpha_0\circ\Theta\circ\xi
	\end{equation}
	we get that
	\begin{equation}\label{eq:IndexInvariantUnderLGA_A1_Transformation}
		\Ad{\pi_0(A_1)x\pi_0(A_1^\dagger)}\circ\pi_0\circ\alpha_0\circ\gamma^{\Hsplit}_{0;1}\circ\tilde{\Theta}=\pi_0\circ\alpha_0\circ\gamma^{\Hsplit}_{0;1}\circ\tilde{\Theta}\circ\gamma^H_{1;0}\circ\xi\circ\gamma^H_{0;1}.
	\end{equation}
	This already proves that
	\begin{align}
		\Ad{\pi_0(A_1)v\pi_0(A_1^\dagger)}\circ\pi_0\circ\alpha_0\circ\gamma^{\Hsplit}_{0;1}\circ\tilde{\Theta}&=\pi_0\circ\alpha_0\circ\gamma^{\Hsplit}_{0;1}\circ\tilde{\Theta}\circ\gamma^H_{1;0}\circ\tau\circ\gamma^H_{0;1}\\
		&=\pi_0\circ\alpha_0\circ\gamma^{\Hsplit}_{0;1}\circ\tilde{\Theta}\circ\tau.
	\end{align}
	To show the second one we get that
	\begin{align}
		&\Ad{\phi_1(\delta_g)\phi_2(W_g)}\circ\pi_0\circ\alpha_0\circ\Theta\\
		&=\Ad{\phi_1(\delta_g)}\circ\pi_0\circ\alpha_0\circ\Theta\circ\gamma^{H}_{0;1}\circ\gamma^{\Hsplit}_{1;0}\circ\eta_g\circ\beta_g^U\circ\gamma^{\Hsplit}_{0;1}\circ\gamma^H_{1;0}\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^{H}_{0;1}\circ\gamma^{\Hsplit}_{1;0}\circ\Ad{\gamma^{H_L}_{0;1}(A_{2,g}^L)\otimes\gamma^{H_R}_{0;1}(A_{2,g}^R)}\circ\eta_g\circ\beta_g^U\circ\gamma^{\Hsplit}_{0;1}\circ\gamma^H_{1;0}\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^{H}_{0;1}\circ\Ad{A_{2,g}^L\otimes A_{2,g}^R}\circ\gamma^{\Hsplit}_{1;0}\circ\eta_g\circ\beta_g^U\circ\gamma^{\Hsplit}_{0;1}\circ\gamma^H_{1;0}.
	\end{align}
	Using equation \eqref{eq:IndexInvariantUnderLGAEtaTildeDefiniton2} on this we obtain
	\begin{equation}
		=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\tilde{\eta}_g\circ\beta_g^U\circ\gamma^H_{1;0}.
	\end{equation}
	Inserting this in equation \eqref{eq:IndexInvariantUnderLGA_A1_Transformation} with $x=\phi_1(\delta_g)\phi_2(W_g)$ and $\xi=\gamma^H_{0;1}\circ\tilde{\eta}_g\circ\beta_g^U\circ\gamma^H_{1;0}$ now proves the fact that $\tilde{W}_g$ is an operator belonging to $\omega\circ\gamma^H_{0;1}$. Proving that $\tilde u_\sigma(g,h)$ and $\tilde{K}_g^\sigma$ are operators belonging to $\omega\circ\gamma_{0;1}^H$ is completely analogous. This concludes the proof.
\end{proof}
\subsection{Stacking in the $H^2(G,\TT)$-valued index}\label{sec:StackingOneTranslation}
Take $\AA$ a quasi local $C^*$ algebra on a two dimensional lattice and take $U\in\hom(G,U(\CC^d))$ an on site group action arbitrary. Let
\begin{equation}
	\omega_1,\omega_2\in\{\omega\in\PP(\AA)|\omega\text{ satisfies assumption \ref{assumption}}\}
\end{equation}
be two states. The goal of this section is to prove that
\begin{equation}\label{eq:IndexMorphismUnderStacking}
	\textrm{Index}^{\AA^2,U\otimes U}(\omega_1\otimes_{\text{stack}}\omega_2)=\textrm{Index}^{\AA,U}(\omega_1)+\textrm{Index}^{\AA,U}(\omega_2).
\end{equation}
Let $\omega_{0i}$ and $\gamma_{0;1}^{\Phi_i}$ (for all $i\in\{1,2\}$) be product states and disentanglers satisfying that
\begin{equation}
	\omega_i=\omega_{0i}\circ\gamma_{0;1}^{\Phi_i}.
\end{equation}
Let
\begin{equation}
	(\HH_{0i},\pi_{0i},\Omega_{0i})
\end{equation}
be GNS triples for the $\omega_{0i}$. Clearly
\begin{equation}
	(\HH_{01}\otimes\HH_{02},\pi_{01}\otimes\pi_{02},\Omega_{01}\otimes\Omega_{02})
\end{equation}
is a GNS triple for $\omega_{01}\otimes_{\text{stack}}\omega_{02}$. The following lemma now holds:
\begin{lemma}
	Let $W_{g,i},u^\sigma_i(g,h),K_{g,i}^\sigma$ and $v_{i}$ be operators belonging to $\omega_i$ then $W_{g,1}\otimes W_{g,2},u^\sigma_1(g,h)\otimes u^\sigma_2(g,h),K_{g,1}^\sigma\otimes K_{g,2}^\sigma$ and $v_{1}\otimes v_{2}$ are operators belonging to $\omega_1\otimes_{\text{stack}}\omega_2$.
\end{lemma}
\begin{proof}
	To show this we simply have to apply the adjoint action of these operators on $\pi_{01}\otimes\pi_{02}$ and see that these are indeed implementations of the right automorphisms. This is so by construction.
\end{proof}
We are now ready to provide a proof of equation \ref{eq:IndexMorphismUnderStacking}. We have
\begin{align}
	&C(g,h)\\
	\nonumber
	&=(K_{g,1}^R\otimes K_{g,2}^R)\Ad{W_{g,1}\otimes W_{g,2}}\left((K_{h,1}^R\otimes K_{h,2}^R)\Ad{(W_{h,1}\otimes W_{h,2})(W_{gh,1}\otimes W_{gh,2})^\dagger}\left((K_{gh,1}^R\otimes K_{gh,2}^R)^\dagger\right)\right)\\
	&(u^R_1(g,h)\otimes u^R_2(g,h))v^\dagger (u^R_1(g,h)\otimes u^R_2(g,h))^\dagger v\\
	&=C_1(g,h)C_2(g,h)
\end{align}
concluding the proof.
\begin{remark}\label{rem:StackingH3ValuedIndex}
	Clearly the same argument can be used to argue that the $H^3$-valued index is invariant under stacking.
\end{remark}
\subsection{The $H^2$-valued index is invariant of choice of basis of on site Hilbert space}\label{sec:the-h2-valued-index-is-invariant-of-choice-of-basis-of-on-site-hilbert-space}
Let $V \in U(\CC^d)$ be a unitary operator on the on site Hilbert space and take $i_V$ as defined in subsection \ref{sec:QuasiLocalC*Algebra}. In this subsection we will prove that
\begin{align}
	&\textrm{Index}^{\AA,\Ad{V^\dagger}(U)}(\theta,i_V^{-1}\circ\tilde{\beta}_g\circ i_V,i_V^{-1}\circ\eta_g\circ i_V,i_V^{-1}\circ\alpha_0\circ i_V,i_V^{-1}\circ\Theta\circ i_V,\omega\circ i_V,\omega_0\circ i_V)\\
	&=\textrm{Index}^{\AA,U}(\theta,\tilde{\beta}_g,\eta_g,\alpha_0,\Theta,\omega,\omega_0).
\end{align}
We do this by proving the following lemma:
\begin{lemma}
	Let $W_g,u_R(g,h),K^R_g$ be operators belonging to
	\begin{equation}
		\textrm{Index}^{\AA,U}(\theta,\tilde{\beta}_g,\eta_g,\alpha_0,\Theta,\omega,\omega_0)
	\end{equation}
	for a GNS triple for $\omega_0$, $(\HH_0,\pi_0,\Omega_0)$ then $W_g,u_R(g,h),K^R_g$ are also operators belonging to
	\begin{equation}
		\textrm{Index}^{\AA,\Ad{V^\dagger}(U)}(\theta,i_V^{-1}\circ\tilde{\beta}_g\circ i_V,i_V^{-1}\circ\eta_g\circ i_V,i_V^{-1}\circ\alpha_0\circ i_V,i_V^{-1}\circ\Theta\circ i_V,\omega\circ i_V,\omega_0\circ i_V)
	\end{equation}
	for the GNS triple for $\omega_0\circ i_V$ given by $(\HH_0,\pi_0\circ i_V,\Omega_0)$.
\end{lemma}
\begin{proof}
	To show this, we merely have to observe that for any $x\in U(\HH_0)$ satisfying that
	\begin{equation}
		\Ad{x}\circ\pi_0\circ\alpha_0\circ\Theta =\pi_0\circ\alpha_0\circ\Theta\circ\xi
	\end{equation}
	for some $\xi\in\Aut{\AA}$ we get that
	\begin{equation}
		\Ad{x}\circ\pi_0\circ i_V\circ i_V^{-1}\circ\alpha_0\circ i_V\circ i_V^{-1}\circ\Theta\circ i_V =\pi_0\circ i_V\circ i_V^{-1}\circ\alpha_0\circ i_V\circ i_V^{-1}\circ\Theta\circ i_V\circ i_V^{-1}\circ\xi\circ i_V
	\end{equation}
	concluding the proof.
\end{proof}
Clearly the above lemma implies that the $H^2$-valued index is invariant under the desired transformation.
\begin{remark}\label{rem:OnSiteUnitaryTransformationH3ValuedIndex}
	Clearly the same argument can be used to argue that the $H^3$-valued index is invariant under the same transformation.
\end{remark}
\subsection{Proof of theorem \ref{thrm:ExistenceFirstIndex}}\label{sec:ProofOf:thrm:ExistenceFirstIndex}
In this section we summarise the proof of theorem \ref{thrm:ExistenceFirstIndex}:
\begin{proof}
	The 2-cochain was defined in subsection \ref{sec:DefinitionH2Index}. The proof that it wasn't dependent on any of the choices made in assumption \ref{assumption} was done in subsection \ref{sec:IndexIsInvariantUnderChoices}. The first item in the list concerning the invariance under locally generated automorphisms was shown in subsection \ref{sec:IndexInvariantUnderLGA}. The proof of the second item concerning the relation between the 1d SPT index and the 2d translation SPT index is done in subsection \ref{sec:OneTranslationDirectionExample}. The proof of the third item concerning the stacking is done in subsection \ref{sec:StackingOneTranslation}. The proof of the last item concerning a change of basis of the on site Hilbert space is done in subsection \ref{sec:the-h2-valued-index-is-invariant-of-choice-of-basis-of-on-site-hilbert-space}. This concludes the proof.
\end{proof}
\subsection{Proof of lemma \ref{lem:SRE_Implies_QDisentanglable_OneTranslation} and lemma \ref{lem:SRE_Implies_Assumption_1d}}\label{sec:ProofOfMainResult1}
We will provide a proof of lemma \ref{lem:SRE_Implies_QDisentanglable_OneTranslation}.
\begin{proof}
	Let $\gamma^{\Phi'}_{0;1}$ be the disentangler with $\Phi'\in\BB_{F_\phi}([0,1])$ (for some $0<\phi<1$) a one parameter family of interactions. By lemma \ref{lem:PropertiesLocallyGeneratedAutomorphisms} part 5 (which is just a slight modification of section 5 from \cite{ogata2021h3gmathbb}) we have that $\gamma^{\Phi'}_{0;1}\in\textrm{SQAut}_1(\AA)$ (by which we mean the definition of SQAut as presented in appendix \ref{sec:the-one-translation-symmetry}, not the one in \cite{ogata2021h3gmathbb}) since $\textrm{SQAut}_1(\AA)\subset\QAut{\AA}$ this implies that $\gamma^{\Phi'}_{0;1}\in\QAut{\AA}$. The existence of the $\tilde{\beta}_g$ was done in \cite{ogata2021h3gmathbb} section 3, where one has to use the fact that $\gamma^{\Phi'}_{0;1}$ is also an SQAut in the definition by \cite{ogata2021h3gmathbb}. This concludes the proof that assumption \ref{assumption} is satisfied.
\end{proof}
We will now prove lemma \ref{lem:SRE_Implies_Assumption_1d}.
\begin{proof}
	The proof simply uses lemma \ref{lem:PropertiesLocallyGeneratedAutomorphisms1d}.
\end{proof}
\section{The $H^1(G,\TT)$-valued index}\label{sec:TwoDirectionTraslationInvariance}
In this section we discuss translation invariance not just in the vertical direction but in two directions simultaneously. Let $\nu\in\Aut{\AA}$ be the automorphism that translates the lattice to the right by one site. Let $\mu\in\Aut{\AA}$ be the automorphism that rotates the lattice by $90^\circ$ clockwise. There is a relation between these automorphisms. Specifically, the automorphism $\tau$ that translated the lattice upwards by one site can now be written as $\tau=\mu^{-1}\circ\nu\circ\mu$. We now let our state $\omega$ satisfy assumption \ref{assumption:2Translations}. For an overview of the supports see figure \ref{fig:SetupForTwoTranslationsNearProof}. In this section we will need a stronger version of the cone operators (from definition \ref{def:ConeOperators}):
\begin{definition}
	Take $0<\theta<\pi/2$ and $\alpha_L\in\Aut{\AA_{L}}$ and $\alpha_R\in\Aut{\AA_{R}}$. Take $\sigma\in\{L,R\}$ and $x\in\UU(\HH_{\sigma})\otimes\id_{\HH_{\ZZ^2/\sigma}}$ then we say that $x$ is a cone operator on $\nu^\sigma(\sigma)$\footnote{Where we define $\nu^L\defeq \nu^{-1}$ and $\nu^R\defeq \nu$.} (or in short $x\in\textrm{Cone}_{\nu^\sigma(\sigma)}(\alpha_0,\theta)$) if and only if there exists a $\xi\in\Aut{\AA_{W(\nu^\sigma(C_\theta\cap\sigma))}}$ such that
	\begin{equation}
		\Ad{x}\circ\pi_0\circ\alpha_0=\pi_0\circ\alpha_0\circ\xi.
	\end{equation}
	$\textrm{Cone}_{\nu^\sigma(\sigma)}(\alpha_0,\theta)$ is a subgroup of $\UU(\HH_\sigma)\otimes\id_{\ZZ^2/\sigma}$. If additionally $\xi\in\Aut{\AA_{\nu^\sigma(C_\theta\cap\sigma)}}$ we will say that $x\in\textrm{Cone}_{\nu^\sigma(\sigma)}^W(\alpha_0,\theta)$.
\end{definition}
Similarly as before we will also need the generalisation of this definition:
\begin{definition}
	Take $0<\theta<\pi/2$, $\alpha_L\in\Aut{\AA_{L}}$, $\alpha_R\in\Aut{\AA_{R}}$ and $\Theta\in\Aut{\AA_{W(C_\theta)^c}}$. Take $\sigma\in\{L,R\}$ and take $x\in\UU(\HH_0)$ then we say that $x$ is an inner after cone operator on $\nu^\sigma(\sigma)$ (or in short $x\in \IAC_{\nu^\sigma(\sigma)}(\alpha_0,\theta,\Theta)$) if there exists an $A\in\UU(\AA_{\nu^\sigma(\sigma)})$ and a $y\in\textrm{Cone}_{\nu^\sigma(\sigma)}(\alpha_0,\theta)$ such that
	\begin{equation}
		x=\pi_0\circ\alpha_0\circ\Theta(A)y.
	\end{equation}
\end{definition}
\subsection{Definition of the index}\label{sec:DefinitionH1Index}
 First notice that since this assumption is strictly stronger then the assumption in \ref{assumption} we can still define all the objects we did before. So in what follows fix a $v\in U(\HH_0)$, $W_g\in U(\HH_0)$, $u_\sigma(g,h)\in \textrm{Cone}_{\nu^\sigma(\sigma)}^W(\alpha_0,\theta)$ and $K_g^\sigma\in\textrm{Cone}_{\nu^\sigma(\sigma)}(\alpha_0,\theta)$ (for every $g,h\in G$) and then later on we will show independence on the choice of these objects. We remind the reader of some equalities from section \ref{sec:ProofFirstStatement}
\begin{align}
		\Ad{v}\circ\pi_0\circ\alpha_0\circ\Theta&=\pi_0\circ\alpha_0\circ\Theta\circ\tau\\
		\Ad{W_g}\circ\pi_0\circ\alpha_0\circ\Theta&=\pi_0\circ\alpha_0\circ\Theta\circ\eta_g\circ\beta_g^U\\
		\Ad{u_\sigma(g,h)}\circ\pi_\sigma\circ\alpha_\sigma&=\pi_\sigma\circ\alpha_\sigma\circ\eta_g^\sigma\circ\beta_g^{\sigma U}\circ\eta_h^{\sigma}\circ(\beta_g^{\sigma U})^{-1}\circ(\eta^\sigma_{gh})^{-1}\\
		u_L(g,h)\otimes u_R(g,h)&=W_gW_hW_{gh}^{-1}\\
		\Ad{K^R_g}\circ\pi_0\circ\alpha_0&=\pi_0\circ \alpha_0\circ \tau^{-1}\circ \eta_g^R\circ\beta_g^{RU}\circ\tau\circ(\beta_g^{RU})^{-1}\circ(\eta_g^{R})^{-1}.
	\end{align}
In what follows, we will need the vertical analogue of the $v$. We define the horizontal translation operator:
\begin{lemma}\label{lem:Definition_w}
	There exists a unique $w\in\UU(\HH_0)$ such that
	\begin{align}
		\Ad{w}\circ\pi_0&=\pi_0\circ\alpha_0\circ\Theta\circ\nu\circ\Theta^{-1}\circ\alpha_0^{-1}&&\text{and}&\pi_0(V_1)w\pi_0(V_1^\dagger)\Omega_0&=\Omega_0.
	\end{align}
\end{lemma}
\begin{proof}
	Analogous to the proof of \ref{lem:Definition_v}.
\end{proof}
 We can use these objects to define $b^\sigma_g$:
\begin{lemma}
	There exist a $b_g^L\in\textrm{Cone}_{\nu^{-1}(L)}^W(\alpha_0,\theta)$ and a $b_g^R\in\textrm{Cone}_{R}^W(\alpha_0,\theta)$ (both unique up to an exchange of a $G-$dependent phase) satisfying that
	\begin{equation}
		w^\dagger W_g w W_g^\dagger=b_g:=b_g^L\otimes b_g^R.
	\end{equation}
	It will satisfy
	\begin{equation}\label{eq:automorphismBelongingTo_b}
		\Ad{b_g^\sigma\otimes\id_{\HH_{\ZZ^2/\sigma}}}\circ\pi_0\circ\alpha_0=\pi_0\circ\alpha_0\circ\nu^{-1}\circ\eta_g^\sigma\circ\nu\circ(\eta_g^\sigma)^{-1}.
	\end{equation}
\end{lemma}
\begin{proof}
	It is easy enough to show that
	\begin{equation}
		\Ad{w^\dagger W_g w W_g^\dagger}\circ\pi_0=\pi_0\circ (\alpha_L\circ\nu^{-1}\circ\eta_g^L\circ\nu\circ(\eta_g^L)^{-1}\circ\alpha_L^{-1})\otimes(\alpha_R\circ\nu^{-1}\circ\eta_g^R\circ\nu\circ(\eta_g^R)^{-1}\circ\alpha_R^{-1}).
	\end{equation}
	To do this one only has to use that $\beta_g^U$ commutes with $\nu$. By lemma \ref{lem:SplittingOfUnitary} the result now follows.
\end{proof}
\begin{lemma}\label{lem:DefinitionAlpha}
	There exists an $\alpha:G\rightarrow U(1)$ satisfying
	\begin{equation}\label{eq:DefinitionOfTheH_1Index}
		v^\dagger b_g^R vh_g K_g^R (b_g^R)^\dagger=\alpha(g)w^\dagger K_g^R w
	\end{equation}
	where
	\begin{equation}
		h_g\defeq\pi_0\circ\alpha_0\circ\Theta(U_{(-1,-1)}(g)).
	\end{equation}
\end{lemma}
\begin{proof}
	We have that
	\begin{align}
		&\Ad{w^\dagger K_g^R w}\circ\pi_0\circ\alpha_0\circ\Theta\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\nu^{-1}\circ\tau^{-1}\circ\eta_g^R\circ\beta_g^{RU}\circ\tau\circ(\beta_g^{RU})^{-1}\circ(\eta_g^R)^{-1}\circ\nu.
	\end{align}
	Now we will use the fact that because of translation invariance of the group action, we have that $\tau^{-1}\circ\beta_g^{RU}\circ\tau\circ(\beta_g^{RU})^{-1}=\beta_g^{RL_{-1}}$ with $L_j=\{(x,y)\in\ZZ^2|y=j\}$. This leads to
	\begin{align}
		&=\pi_0\circ\alpha_0\circ\Theta\circ\nu^{-1}\circ\underline{\tau^{-1}}\circ\eta_g^R\circ\tau\circ\beta_g^{R,L_{-1}}\circ(\eta_g^R)^{-1}\circ\nu\\
		&=\Ad{\underline{v^\dagger}}\circ \pi_0\circ\alpha_0\circ\Theta\circ\nu^{-1}\circ\eta_g^R\circ\tau\circ\beta_g^{R,L_{-1}}\circ(\eta_g^R)^{-1}\circ\nu.
	\end{align}
	Inserting $b^R_g v v^\dagger (b^R_g)^\dagger$ now gives
	\begin{equation}
		=\Ad{v^\dagger\underline{b^R_g v v^\dagger (b^R_g)^\dagger}}\circ \pi_0\circ\alpha_0\circ\Theta\circ\nu^{-1}\circ\eta_g^R\circ\tau\circ\beta_g^{R,L_{-1}}\circ(\eta_g^R)^{-1}\circ\nu.
	\end{equation}
	 Using the inverse of equation \eqref{eq:automorphismBelongingTo_b} we now get
	\begin{align}
		&=\Ad{v^\dagger b^R_g v }\circ \pi_0\circ\alpha_0\circ\Theta\circ\underline{\tau^{-1}\circ\eta_g^R\circ\nu^{-1}\circ\stkout{(\eta_g^R)^{-1}\circ\nu}}\circ\stkout{\nu^{-1}\circ\eta_g^R}\circ\tau\circ\beta_g^{R,L_{-1}}\circ(\eta_g^R)^{-1}\circ\nu\\
		&=\Ad{v^\dagger b_g^R v}\circ\pi_0\circ\alpha_0\circ\Theta\circ\tau^{-1}\circ\eta_g^R\circ\tau\circ\nu^{-1}\circ\beta_g^{R,L_{-1}}\circ(\eta_g^R)^{-1}\circ\nu.
	\end{align}
	Now we will use the fact that $\nu^{-1}\circ\beta_g^{R,L_{-1}}\circ\nu=\Ad{U_{(-1,-1)}(g)}\circ\beta_g^{R,L_{-1}}$ to obtain
	\begin{equation}
		=\Ad{v^\dagger b_g^R v}\circ\pi_0\circ\alpha_0\circ\Theta\circ\tau^{-1}\circ\eta_g^R\circ\tau\circ\Ad{U_{(-1,-1)}(g)}\circ\beta_g^{R,L_{-1}}\circ\nu^{-1}\circ(\eta_g^R)^{-1}\circ\nu.
	\end{equation}
	Since (as you can check in figure \ref{fig:SetupForTwoTranslationsNearProof}) $\tau^{-1}(\eta_g^R(\tau(U_{(-1,-1)}(g))))=U_{(-1,-1)}(g)$ this gives
	\begin{align}
		&=\Ad{v^\dagger b_g^R v}\circ\pi_0\circ\alpha_0\circ\Theta\circ\Ad{U_{(-1,-1)}(g)}\circ\tau^{-1}\circ\eta_g^R\circ\tau\circ\beta_g^{R,L_{-1}}\circ\nu^{-1}\circ(\eta_g^R)^{-1}\circ\nu\\
		&=\Ad{v^\dagger b_g^R vh_g}\circ\pi_0\circ\alpha_0\circ\Theta\circ\tau^{-1}\circ\eta_g^R\circ\tau\circ\beta_g^{R,L_{-1}}\circ\nu^{-1}\circ(\eta_g^R)^{-1}\circ\nu.
	\end{align}
	Now using again that $\tau\circ\beta_g^{R,L_{-1}}=\beta_{g}^{RU}\circ\tau\circ(\beta_g^{RU})^{-1}$ we get:
	\begin{align}
		&=\Ad{v^\dagger b_g^R vh_g}\circ\pi_0\circ\alpha_0\circ\Theta\circ\tau^{-1}\circ\eta_g^R\circ\beta_{g}^{RU}\circ\tau\circ(\beta_g^{RU})^{-1}\circ\nu^{-1}\circ(\eta_g^R)^{-1}\circ\nu\\
		&=\Ad{v^\dagger b_g^R vh_gK_g^R}\circ\pi_0\circ\alpha_0\circ\Theta\circ\eta_g^R\circ\nu^{-1}\circ(\eta_g^R)^{-1}\circ\nu.
	\end{align}
	After again using \eqref{eq:automorphismBelongingTo_b} we obtain:
	\begin{align}
		=\Ad{v^\dagger b_g^R vh_gK_g^R(b_g^R)^\dagger}\circ\pi_0\circ\alpha_0\circ\Theta.
	\end{align}
	By the irreducibility of $\pi_0$ this implies that there indeed exists such an $\alpha$.
\end{proof}
We have that $h_g\in\IAC_L(\theta,\alpha_0,\Theta)$. On top of that we also have that
\begin{lemma}\label{lem:W_g_And_h_g_Commute}
	For all $g,h\in G$ we have that
	\begin{align}
		[h_g,W_h]&=0&[h_g,b_h^L]&=0.
	\end{align}
\end{lemma}
\begin{proof}
	We have that (see figure \ref{fig:SetupForTwoTranslationsNearProof})
	\begin{align}
		\Ad{W_h}(h_g)&=\pi_0\circ\alpha_0\circ\Theta\circ\eta_h\circ\beta_h^U(U_{(-1,-1)}(g))\\
		&=\pi_0\circ\alpha_0\circ\Theta(U_{(-1,-1)}(g))=h_g
	\end{align}
	concluding the proof of the first item. The second proof is analogous.
\end{proof}
Finally before we can show that the $\alpha$ is a $U(1)$ representation we need to prove an analogue of the equation in the 2-cochain lemma \ref{lem:Definition2Cochain}:
\begin{lemma}\label{lem:translating_u_R_To_The_Right_identity}
The equality
\begin{equation}
\Ad{b_g^R W_g b_h^R W_h W_{gh}^\dagger (b_{gh}^R)^\dagger W_{gh}W_h^\dagger W_g^\dagger u_R(g,h)}\circ\pi_0=\Ad{w^\dagger u_R(g,h) w}\circ\pi_0
\end{equation}
holds.
\end{lemma}
\begin{proof}
The proof is almost completely analogous to the proof of \ref{lem:Definition2Cochain}. We first start by showing that
\begin{equation}
\Ad{b_g W_g b_h W_h W_{gh}^\dagger (b_{gh})^\dagger W_{gh}W_h^\dagger W_g^\dagger u_L(g,h)\otimes u_R(g,h)}\circ\pi_0=\Ad{w^\dagger u_R(g,h)\otimes u_R(g,h) w}\circ\pi_0
\end{equation}
holds. This part is completely the same. The only difference is now that to prove that
\begin{equation}
b_g W_g b_h W_h W_{gh}^\dagger (b_{gh})^\dagger W_{gh}W_h^\dagger W_g^\dagger
\end{equation}
 is split one needs to use the new (shifted) support of $\eta_g^\sigma$.
\end{proof}
Using this we can show that:
\begin{lemma}
	The $\alpha$ defined previously is a $U(1)$-representation.
\end{lemma}
\begin{proof}
	Take the definition of the 2-cochain (lemma \ref{lem:Definition2Cochain})
	\begin{equation}\label{eq:Definition2Cochain2TranslationSection}
		K_g^RW_gK_h^RW_hW_{gh}^\dagger(K_{gh}^R)^\dagger W_{gh}W_{h}^\dagger W_g^\dagger u_R(g,h)=C(g,h)v^\dagger u_R(g,h)v.
	\end{equation}
	Clearly this equation is invariant under the substitution
	\begin{align}
		K_g^R&\mapsto w^\dagger K_g^R w&W_g&\mapsto w^\dagger W_g w&u_R(g,h)&\mapsto w^\dagger u_R(g,h)w.
	\end{align}
	If we now also show that it is invariant under the substitution
	\begin{align}
		K_g^R&\mapsto v^\dagger b_g^R v h_g K_g^R (b_g^R)^\dagger&W_g&\mapsto w^\dagger W_g w&u_R(g,h)&\mapsto w^\dagger u_R(g,h)w
	\end{align}
	then we get using the definition of $\alpha$ that
	\begin{equation}
		\stkout{C(g,h)}=\stkout{C(g,h)}\frac{\alpha(g)\alpha(h)}{\alpha(gh)}
	\end{equation}
	which would clearly conclude the proof. This is proven in lemma \ref{lem:2cochainIsInvariant}.
\end{proof}
\begin{definition}
	Let $\alpha$ be the $U(1)$-representation defined in lemma \ref{lem:DefinitionAlpha}. Take $\phi\in\hom(G,\TT)$ such that $\alpha(g)=\exp(i\phi(g))$. We define the 2 translation index as
	\begin{equation}
		\textrm{Index}_{2\:\text{trans}}^{\AA,U}(\theta,\tilde{\beta}_g,\eta_g,\alpha_0,\Theta,\omega,\omega_0)\defeq \phi\in H^1(G,\TT)
	\end{equation}
	and (as advertised) it is only a function of the automorphisms (and the product state) not on the choice of the GNS triple of $\omega_0$ or on the choice of phases in $W_g,u_L(g,h),u_R(g,h),v,w,K^L_g,K^R_g,b^L_g$ and $b^R_g$.\footnote{It is however explicitly dependent on the on site group action $U$, and not only $\Ad{U}$.}
\end{definition}
\begin{proof}
	Clearly the construction is invariant under the choice of GNS triple since this simply amounts to an adjoint action by some unitary on every operator. The proof that it is independent of the choice of phases is just as trivial.
\end{proof}
One can also define this index starting from operators acting on the left. As the following lemma shows this gives us the opposite index (the complex conjugate of the $U(1)$-representation):
\begin{lemma}
	Define $\tilde{\alpha}(g)$ such that
	\begin{equation}\label{eq:DefinitionOfTheH_1IndexAlternative}
		v^\dagger b_g^L v h_g^\dagger K_g^L (b_g^L)^\dagger=\tilde{\alpha}(g)w^\dagger K_g^L w
	\end{equation}
	then $\alpha(g)\tilde{\alpha}(g)=1$.
\end{lemma}
\begin{proof}
	By multiplying the left hand side of equation \eqref{eq:DefinitionOfTheH_1IndexAlternative} with the left hand side of equation \eqref{eq:DefinitionOfTheH_1Index} we obtain
	\begin{align}
		v^\dagger b_g v K_g b_g^\dagger&=v^\dagger b_g v v^\dagger W_g v W_g^\dagger b_g^\dagger\\
		&=w^\dagger v^\dagger W_g v W_g^\dagger w\\
		&=w^\dagger K_g w
	\end{align}
	whereas by multiplying the right hand sides we obtain
	\begin{equation}
		=\alpha(g)\tilde{\alpha}(g)w^\dagger K_g w.
	\end{equation}
	These two results can only be consistent if the lemma holds.
\end{proof}
\subsection{The $H^1(G,\TT)$-valued index is invariant under choices}\label{sec:IndexIsInvariantUnderChoicesTwoTranslations}
In this section we will show that the index is only dependent on $\omega$ and not on the choices of our automorphisms nor on $\omega_0$. On this last item we remark:
\begin{remark}\label{rem:NontrivialProductState}
	A product state can have a non-trivial $H^1(G,\TT)$ index and the index is not defined relative to $\omega_0$ so in particular
	\begin{equation}
		\textrm{Index}_{2\:\text{trans}}^{\AA,U}(\theta,\beta_g^U,\textrm{Id},\textrm{Id},\textrm{Id},\omega_0,\omega_0)
	\end{equation}
	can still be non-trivial. In fact in this case we get $\alpha(g)=\omega_0(U_{(-1,-1)}(g))$. To show this, notice that we can take $b_g=\id_{\HH}$ and we can chose $K_g^R$ so that it leaves the cyclic vector of $\omega_0$, $\Omega_0$ invariant. Applying the definition of the index on this cyclic vector then gives us $h_g\Omega_0=\alpha(g)\Omega_0$. This obviously implies that $\bra{\Omega_0}\ket{h_g\Omega_0}=\alpha(g)\bra{\Omega_0}\ket{\Omega_0}$ giving us indeed the advertised equation.
\end{remark}
We will now show independence of $\alpha$ and its decomposition.
\begin{lemma}
	Take $\omega_{01},\omega_{02}\in\PP(\AA)$ product states and $\alpha_1,\alpha_2\in\Aut{\AA}$ such that
	\begin{equation}
		\omega_{01}\circ\alpha_1=\omega_{02}\circ\alpha_2=\omega.
	\end{equation}
	Let $V_{11},V_{12}\in\UU(\AA)$, $\alpha_{L/R,1},\alpha_{L/R,2}\in\Aut{\AA_{L/R}}$ and $\Theta_1,\Theta_2\in \Aut{\AA_{W(C_\theta)^c}}$ be such that
	\begin{align}
		\alpha_1&=\Ad{V_{11}}\circ\alpha_{01}\circ\Theta_1&\alpha_2&=\Ad{V_{12}}\circ\alpha_{02}\circ \Theta_2
	\end{align}
	with $\alpha_{0,i}=\alpha_{L,i}\otimes\alpha_{R,i}$, then
	\begin{equation}
		\textrm{Index}_{2\:\text{trans}}^{\AA,U}(\theta,\tilde{\beta}_g,\eta_g,\alpha_{0,1},\Theta_1,\omega,\omega_{01})=\textrm{Index}_{2\:\text{trans}}^{\AA,U}(\theta,\tilde{\beta}_g,\eta_g,\alpha_{0,2},\Theta_2,\omega,\omega_{02}).
	\end{equation}
\end{lemma}
\begin{proof}
	We will first prove the result in the case that $\omega_0=\omega_{01}=\omega_{02}$ and then generalise this result. Since $\omega_0\circ\alpha_2\circ\alpha_1^{-1}=\omega_0$ there exists a $\tilde{x}\in\UU(\HH_0)$ such that
	\begin{equation}
		\pi_0\circ\alpha_2\circ\alpha_1^{-1}=\Ad{\tilde{x}}\circ\pi_0.
	\end{equation}
	Now define $x\in\UU(\HH_0)$ to be
	\begin{equation}
		x\defeq \pi_0(V_{12}^\dagger)\tilde{x} \pi_0(V_{11})
	\end{equation}
	then
	\begin{equation}
		\pi_0\circ\alpha_{02}\circ\Theta_2=\Ad{x}\circ\pi_0\circ\alpha_{01}\circ\Theta_1.
	\end{equation}
	Let $v,w,K_g^\sigma$ and $b_g^\sigma$ be operators belonging to the first choice then by construction $xvx^\dagger,xwx^\dagger,xK_g^\sigma x^\dagger$ and $xb_g^\sigma x^\dagger$ are operators belonging to the second choice. Since the index is invariant under this substitution this concludes the proof in the case that $\omega_0=\omega_{01}=\omega_{02}$. Now suppose that $\omega_{01}\neq\omega_{02}$. Since they are both product states there exists a $\gamma\in\Aut{\AA}$ satisfying $\omega_{02}=\omega_{01}\circ\gamma$ that is of the form $\gamma=\gamma^L\otimes\gamma^R$. We now have
	\begin{align}
		\textrm{Index}_{2\:\text{trans}}^{\AA,U}(\theta,\tilde{\beta}_g,\eta_g,\alpha_{0,2},\Theta_2,\omega,\omega_{02})&=\textrm{Index}_{2\:\text{trans}}^{\AA,U}(\theta,\tilde{\beta}_g,\eta_g,\alpha_{0,2},\Theta_2,\omega,\omega_{01}\circ\gamma)\\
		&=\textrm{Index}_{2\:\text{trans}}^{\AA,U}(\theta,\tilde{\beta}_g,\eta_g,\gamma\circ\alpha_{0,2},\Theta_2,\omega,\omega_{01})
	\end{align}
	concluding the proof.
\end{proof}
In what follows we will need that the index is invariant under the following transformation:
\begin{lemma}\label{lem:TransformationUnderDeltaTwoTranslations}
	Take $\omega_0,\theta,\alpha_0,\Theta$ and $\eta_g$ as usual, take $v,w,W_{g,1},u_{\sigma,1}(g,h),K_{g,1}^\sigma$ and $b_{g,1}^\sigma$ operators corresponding to these automorphisms and take $\delta^\sigma_g\in\IAC_{\nu^\sigma(\sigma)}(\alpha_0,\Theta,\theta)$ (for all $\sigma\in\{L,R\}$ and all $g\in G$). Define
	\begin{align}
		W_{g,2}&\defeq\delta_g W_{g,1}\\
		u_{\sigma,2}(g,h)&\defeq \delta_g^\sigma W_{g,1}\delta_h^\sigma W_{g,1}^\dagger u_{\sigma,1}(g,h)(\delta_{gh}^\sigma)^\dagger\\
		K^\sigma_{g,2}&\defeq v^\dagger \delta_g^\sigma v K_{g,1}^\sigma (\delta_g^\sigma)^\dagger\\
		b_{g,2}^\sigma&\defeq w^\dagger\delta^\sigma_g w b_{g,1}^\sigma (\delta^\sigma_g)^\dagger
	\end{align}
	then the index of $v,w,W_{g,1},u_{\sigma,1}(g,h),K_{g,1}^\sigma,h_g$ and $b_{g,1}^\sigma$ is equal to the index of $v,w,W_{g,2},u_{\sigma,2}(g,h),h_g,K_{g,2}^\sigma$ and $b_{g,2}^\sigma$.
\end{lemma}
\begin{proof}
	We define the index in function of the new variables:
	\begin{align}
		\alpha_2(g)&\defeq v^\dagger b^R_{g,2}v h_g K^R_{g,2}(b^R_{2,g})^\dagger w^\dagger (K^R_{2,g})^\dagger w\\
		&=v^\dagger \left(w^\dagger\delta^R_g w b_{g,1}^R (\delta^R_g)^\dagger\right) v h_g \left(v^\dagger \delta_g^R v K_{g,1}^R (\delta_g^R)^\dagger\right) \left(w^\dagger\delta^R_g w b_{g,1}^R (\delta^R_g)^\dagger\right)^\dagger w^\dagger (v^\dagger \delta_g^R v K_{g,1}^R (\delta_g^R)^\dagger)^\dagger w\\
		&=v^\dagger w^\dagger\delta^R_g w b_{g,1}^R (\delta^R_g)^\dagger v h_g v^\dagger \delta_g^R v K_{g,1}^R \stkout{(\delta_g^R)^\dagger \delta_g^R} (b_{1,g}^R)^\dagger w^\dagger \stkout{(\delta_g^R)^\dagger w w^\dagger \delta_g^R} (K_{g,1}^R)^\dagger v^\dagger (\delta_g^R)^\dagger v  w.
	\end{align}
	If we now insert $vv^\dagger,$ we obtain
	\begin{align}
		\alpha_2(g)&=v^\dagger w^\dagger\delta^R_g w b_{g,1}^R v\stkout{v^\dagger (\delta^R_g)^\dagger v} h_g \stkout{v^\dagger \delta_g^R v} K_{g,1}^R (b_{1,g}^R)^\dagger w^\dagger (K_{g,1}^R)^\dagger v^\dagger (\delta_g^R)^\dagger v  w
	\end{align}
	where the cancelation is due to the fact that $v^\dagger \delta^R_g v\in\textrm{IAC}_{R}(\alpha_0,\theta,\Theta)$ whereas $h_g\in \textrm{IAC}_{L}(\alpha_0,\theta,\Theta)$. Again after inserting $vv^\dagger$ and $ww^\dagger$ we now get
	\begin{align}
		\alpha_2(g)&=v^\dagger w^\dagger\delta^R_g w \underline{v v^\dagger} b_{g,1}^R v h_g K_{g,1}^R (b_{1,g}^R)^\dagger w^\dagger (K_{g,1}^R)^\dagger \underline{ww^\dagger} v^\dagger (\delta_g^R)^\dagger v  w\\
		&=\stkout{v^\dagger w^\dagger\delta^R_g w v} \alpha_1(g) \stkout{w^\dagger v^\dagger (\delta_g^R)^\dagger v  w}\\
		&=\alpha_1(g)
	\end{align}
	concluding the proof.
\end{proof}
We will now show that the index is independent on the choice of $\tilde{\beta}_g$ and its decomposition.
\begin{lemma}\label{lem:InvarianceUnderChoiceBetaTwoTranslations}
	Take $\tilde{\beta}_{g,1},\tilde{\beta}_{g,2}\in\Aut{\AA},V_{g,21},V_{g,22}\in\UU(\AA),\eta_{g,1}^L,\eta_{g,2}^L\in \Aut{\AA_{\nu^{L}(C_\theta\cap L)}}$ and $\eta_{g,1}^R,\eta_{g,2}^R\in \Aut{\AA_{\nu^{R}(C_\theta\cap R)}}$ such that there exist $V_{g,21},V_{g,22}\in\UU(\AA)$ satisfying
	\begin{align}\label{eq:InvarianceUnderChoiceBetaTwoBetasTwoTranslations}
		\tilde{\beta}_{g,1}&=\Ad{V_{g,21}}\circ\eta_{g,1}\circ\beta^U_g&\tilde{\beta}_{g,2}&=\Ad{V_{g,22}}\circ\eta_{g,2}\circ\beta^U_g
	\end{align}
	and
	\begin{equation}
		\omega\circ\tilde{\beta}_{g,1}=\omega\circ\tilde{\beta}_{g,2}=\omega
	\end{equation}
	then
	\begin{equation}
		\textrm{Index}_{\text{2 trans}}(\theta,\tilde{\beta}_{g,1},\eta_{g,1},\alpha_{0},\Theta,\omega,\omega_0)=\textrm{Index}_{\text{2 trans}}(\theta,\tilde{\beta}_{g,2},\eta_{g,2},\alpha_{0},\Theta,\omega,\omega_0).
	\end{equation}
\end{lemma}
\begin{proof}
		Take 
	\begin{equation}\label{eq:InvarianceUnderChoiceBetaAlphaDecompositionTwoTranslations}
		\alpha=\Ad{V_1}\circ\alpha_{0}\circ\Theta
	\end{equation}
	the usual decomposition. Since
	\begin{equation}
		\omega_0\circ\alpha\circ\tilde{\beta}_{g,1}\circ(\tilde{\beta}_{g,2})^{-1}=\omega_0\circ\alpha
	\end{equation}
	there exist $\tilde{\delta}_g\in\UU(\HH_0)$ such that
	\begin{equation}
		\Ad{\tilde{\delta}_g}\circ\pi_0\circ\alpha=\pi_0\circ\alpha\circ\tilde{\beta}_{g,2}(\tilde{\beta}_{g,1})^{-1}.
	\end{equation}
	Inserting equation \eqref{eq:InvarianceUnderChoiceBetaTwoBetasTwoTranslations} and \eqref{eq:InvarianceUnderChoiceBetaAlphaDecompositionTwoTranslations} in this gives
	\begin{equation}
		\Ad{\tilde{\delta}_g}\circ\pi_0\circ\Ad{V_1}\circ\alpha_0\circ\Theta=\pi_0\circ\Ad{V_1}\circ\alpha_0\circ\Theta\circ\Ad{V_{g,21}}\circ\eta_{g,1}\circ\eta_{g,2}^{-1}\circ\Ad{V_{g,22}^\dagger}.
	\end{equation}
	Putting the $V$'s to the other side gives:
	\begin{equation}
		\Ad{\pi_0\circ\alpha_0\circ\Theta(V_{g,21}^\dagger)\pi_0(V_1^\dagger)\tilde{\delta}_g\pi_0(V_1)\pi_0\circ\alpha_0\circ\Theta(V_{g,22})}\circ\pi_0=\pi_0\circ\alpha_0\circ\eta_{g,2}\circ(\eta_{g,1})^{-1}\circ\alpha_0^{-1}.
	\end{equation}
	Since the last equation is split we have again by the same argument used to prove lemma \ref{lem:UsingIrreducibilityAndWignerTheorem} that we can take $\delta_g^L\in\textrm{Cone}_{\nu^{-1}(L)}(\alpha_0,\theta)$ and $\delta_g^R\in\textrm{Cone}_{\nu(R)}(\alpha_0,\theta)$ such that
	\begin{equation}
		\delta_g^L\otimes\delta_g^R=\alpha_0\circ\Theta(V_{g,21}^\dagger)\pi_0(V_1^\dagger)\tilde{\delta}_g\pi_0(V_1)\pi_0\circ\alpha_0\circ\Theta(V_{g,22}).
	\end{equation}
	Take $v,w,W_{g,1},u_{\sigma,1}(g,h),K_{g,1}^\sigma$ and $b_{g,1}^\sigma$ operators corresponding to the first choice (with arbitrary phases). Define
	\begin{align}
		W_{g,2}&\defeq\delta_g W_{g,1}\\
		u_{\sigma,2}(g,h)&\defeq \delta_g^\sigma W_{g,1}\delta_h^\sigma W_{g,1}^\dagger u_{\sigma,1}(g,h)(\delta_{gh}^\sigma)^\dagger\\
		K^\sigma_{g,2}&\defeq v^\dagger \delta_g^\sigma v K_{g,1}^\sigma (\delta_g^\sigma)^\dagger\\
		b_{g,2}^\sigma&\defeq w^\dagger\delta^\sigma_g w b_{g,1}^\sigma (\delta^\sigma_g)^\dagger
	\end{align}
	then $W_{g,2},u_{R,2}(g,h),K^R_{g,2}$ and $b^R_{g,2}$ are operators belonging to the second choice. Now using lemma \ref{lem:TransformationUnderDeltaTwoTranslations} concludes the proof.
\end{proof}
\begin{lemma}
	The index is independent of the choice of angle $\theta$.
\end{lemma}
\begin{proof}
	After what was done so far this result is trivial.
\end{proof}
Due to all these considerations we will write this index as $\textrm{Index}_{2\text{ trans}}^{\AA,U}(\omega)$ from here on onward.
\subsection{Example (consistency with conjecture \ref{conj2})}\label{sec:TwoTranslationDirectionsExample}
This example will be very similar to what was done in section \ref{sec:OneTranslationDirectionExample}. In this case however we will require that the translation morphism $\nu$ acts as an automorphism on the $C^*$ algebra $\AA_{L_i}$ (for all $i$) and that our one dimensional state is invariant under this automorphism. We will need assumption \ref{assumption1dWithTranslation}. Since this state satisfies the split property (see lemma \ref{lem:phiExampleConsistentWithConjectureSplitProperty}) we can define an $H^1(G,\TT)$ valued index for it (see appendix \ref{sec:OneDimensionalIndices}). Now we will take again the infinite tensor product (see definition \ref{def:InfiniteTensorProductState}) of such states then we get:
\begin{lemma}
	Let $\omega_\phi$ be the infinite tensor product of a state $\phi$ that satisfies assumption \ref{assumption1dWithTranslation} then $\omega_\phi$ satisfies assumption \ref{assumption:2Translations}.
\end{lemma}
\begin{proof}
	The proof of this lemma is given in lemma \ref{lem:TensorProductStateHasWellDefinedH^1IndexAppendix}.
\end{proof}
This shows that $\omega_\phi$ indeed has a well defined $H^1(G,\TT)$ index. We will now show that $\textrm{Index}_{\text{2 trans}}(\omega_\phi)=\textrm{Index}_{\text{1d trans}}(\phi)$. Just like in section \ref{sec:OneTranslationDirectionExample}, we fix a GNS triple of $\omega_0$ that is of the form
\begin{equation}
	\left(\HH_0=\bigotimes_{\substack{\sigma\in\{L,R\}\\ \rho\in\{L_{>-1},L_{-1},L_{<-1}\}}}\HH_{\rho,\sigma},\pi_0=\bigotimes_{\substack{\sigma\in\{L,R\}\\ \rho\in\{L_{>-1},L_{-1},L_{<-1}\}}}\pi_{\rho,\sigma},\Omega_0=\bigotimes_{\substack{\sigma\in\{L,R\}\\ \rho\in\{L_{>-1},L_{-1},L_{<-1}\}}}\Omega_{\rho,\sigma}\right)
\end{equation}
where the $\pi_{\rho,\sigma}:\AA_{\rho\cap\sigma}\rightarrow\BB(\HH_{\rho,\sigma})$ are all irreducible representations.
\begin{remark}\label{rem:GNS_One_DimensionalTwoTranslations}
	We clearly have (by construction) that
	\begin{equation}
		\pi_{L_{-1},L}\circ\alpha_L|_{L_{-1}}\otimes \pi_{L_{-1},R}\circ\alpha_R|_{L_{-1}}
	\end{equation}
	is a GNS representation of $\phi$. This implies that if we take any $k^R:G\rightarrow \HH_{L_{-1},R}$ such that
	\begin{equation}
		\Ad{k^R(g)}\circ\pi_{L_{-1},R}\circ\alpha_R|_{L_{-1}}=\pi_{L_{-1},R}\circ\alpha_R|_{L_{-1}}\circ\beta_{g}^{L_{-1}\cap R}
	\end{equation}
	and $w_{L_{-1}}$ to be such that
	\begin{equation}
		\Ad{w_{L_{-1}}}\circ\pi_{L_{-1},L}\otimes \pi_{L_{-1},R}=\pi_{L_{-1},L}\otimes \pi_{L_{-1},R}\circ\nu
	\end{equation}
	then there exists a $U(1)$ representation $\alpha$ satisfying that
	\begin{equation}
		(\pi_{L_{-1},L}(U_{(-1,-1)}(g))\otimes \id_{\HH_{L_{-1},R}}) (\id_{\HH_{L_{-1},L}}\otimes k^R(g))=\alpha(g) w_{L_{-1}}^\dagger(\id_{\HH_{L_{-1},L}}\otimes k^R(g))w_{L_{-1}}
	\end{equation}
	and that it is given by $\textrm{Index}_{\text{1d trans}}(\phi)$.
\end{remark}
Just like in section \ref{sec:OneTranslationDirectionExample}, let $\tilde k:G\rightarrow \UU(\HH_{L_{-1}})$ be the unique operator that satisfies
\begin{align}
	\Ad{\tilde{k}_g}\circ\pi_{L_{-1}}&=\pi_{L_{-1}}\circ \circ\alpha|_{L_{-1}}\circ\beta_g^{L_{-1}}\circ \alpha^{-1}|_{L_{-1}}&\tilde k_g\Omega_{L_{-1}}&=\Omega_{L_{-1}}.
\end{align}
We can take
\begin{equation}
	K_g=\id_{H_{L_{>-1}}}\otimes \pi_{L_{-1}}(b)^\dagger \tilde k_g \pi_{L_{-1}}(b) \otimes\id_{\HH_{L_{<-1}}} =\id_{H_{L_{>-1}}}\otimes (k_g^L\otimes k_g^R) \otimes\id_{\HH_{L_{<-1}}}.
\end{equation}
Similarly we can take $w_\rho\in\HH_\rho$ (where $\rho\in\{L_{>-1},L_{-1},L_{<-1}\}$) satisfying
\begin{equation}
	\Ad{w_\rho}\circ\pi_\rho\circ\alpha_{0}|_\rho\circ\Theta|_\rho=\pi_\rho\circ\alpha_{0}|_\rho\circ\Theta|_\rho\circ\nu
\end{equation}
and then we get that $w=w_{L_{>-1}}\otimes w_{L_{-1}}\otimes w_{L_{<-1}}$. Since $\eta_g=\textrm{Id}_{\AA}$ we can simply take $b_g^\sigma=\id_{\HH_\sigma}$. We now have that
\begin{equation}
	\pi_0\circ\alpha_0\circ\Theta(U_{(-1,-1)})\id_{\HH_L}\otimes K_g^R=\id_{\HH_{L_{>-1}}}\otimes(\pi_{L_{-1},L}\circ\tilde\alpha_L(U_{(-1,-1)})\otimes k^R(g))\otimes\id_{\HH_{L_{>-1}}}.
\end{equation}
By what was written in remark \ref{rem:GNS_One_DimensionalTwoTranslations} we get that
\begin{align}
	&=\id_{H_{L_{>-1}}}\otimes\alpha(g) w_{L_{-1}}(\id_{\HH_{L_{-1},L}}\otimes k^R(g))w_{L_{-1}}^\dagger\otimes \id_{H_{L_{<-1}}}\\
	&=\alpha(g)w^\dagger (\id_{H_{L_{>-1}}}\otimes \id_{\HH_{L_{-1},L}}\otimes k^R(g)\otimes \id_{H_{L_{<-1}}}) w\\
	&=\alpha(g)w^\dagger (\id_{\HH_L}\otimes K^R_g) w
\end{align}
showing that indeed $\textrm{Index}_{\text{2 trans}}(\omega_\phi)=\textrm{Index}_{\text{1d trans}}(\phi)$.
\subsection{The $H^1(G,\TT)$-valued index is invariant under locally generated automorphisms}\label{sec:H1ValuedIndexInvariantUnderLGA's}
The goal of this section is to show that the index we constructed is invariant under locally generated automorphisms. To this end let $H\in \BB_{F_\phi}([0,1])$ be a $G$-invariant, translation invariant (in both directions) one parameter family of interactions. In the rest of this section we will define (for notational simplicity) $\HsplitTilde\defeq H_{\nu^{-1}(L)}+H_{\nu(R)}$. Clearly, this $\HsplitTilde$ is translation invariant in the vertical direction but not in the horizontal direction. The proof is very similar to what was done in theorem \ref{thrm:IndexInvariantUnderLGA} but with some notable differences. We first need a different version of lemma \ref{lem:DefinitionOfGroupMorphismVAutEquation} (in fact it is almost completely identical only the definition of $\Hsplit$ is now slightly different) and use this to define some objects used in the rest of the section:
\begin{lemma}\label{lem:DefinitionOfGroupMorphismVAutEquationTwoTranslations}
	Take $0<\theta<\pi/2$ and $\Theta\in \Aut{\AA_{W(C_\theta)^c}}$. There exist $\Phi^U_{s;t}\in\Aut{\AA_{W(C_\theta)^c\cap U}}$ and $\Phi^D_{s;t}\in\Aut{\AA_{W(C_\theta)^c\cap D}}$, both commuting with $\beta_g$, such that there exists some $a\in\UU(\AA)$ satisfying that
	\begin{equation}\label{eq:DefinitionOfGroupMorphismVAutEquationTwoTranslations}
	\gamma^H_{0;1}\circ\gamma^{\HsplitTilde}_{1;0}=\Ad{a}\circ \Phi^U_{0;1}\otimes\Phi^D_{0;1}.
	\end{equation}
\end{lemma}
\begin{proof}
	This follows from the fact that because of \ref{lem:PropertiesLocallyGeneratedAutomorphisms} part 2 (or a slight modification thereof because of the new definition of $\HsplitTilde$ compared to the definition of $\Hsplit$.) $\gamma^H_{0;1}\circ\gamma^{\HsplitTilde}_{1;0}\in \textrm{GVAut}_1(\AA)$.
\end{proof}
This lemma is almost identical to lemma \ref{lem:DefinitionOfGroupMorphismVAutEquation}. The only difference is the definition of $\HsplitTilde$ compared to $\Hsplit$. In analogy to lemma \ref{lem:PropertyTilde_a} we will define $\tilde{a}\defeq \pi_0\circ\alpha_0\circ\Theta(a)$. The main property we will use of this operator is that it satisfies the following lemma:
\begin{lemma}\label{lem:PropertyTilde_aTwoTranslations}
	Let $A\in\UU(\AA_{W(C_\theta)\cap\sigma})$ then
	\begin{equation}
	\Ad{\tilde{a}}\circ\pi_0\circ\alpha_0(A)=\Ad{\tilde{a}}\circ\pi_0\circ\alpha_0\circ\Theta(A)=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{\HsplitTilde}_{1;0}(A).
	\end{equation}
\end{lemma}
\begin{proof}
	Analogous to the proof of lemma \ref{lem:PropertyTilde_a}.
\end{proof}
We now need a slightly modified version of lemma \ref{lem:DefinitionOfGroupMorphism}:
\begin{lemma}\label{lem:DefinitionOfGroupMorphismTwoTranslations}
	Take $\tilde{a}\defeq \pi_0\circ\alpha_0\circ\Theta(a)$ and define the map
	\begin{align}
		\phiTilde_{1,\sigma}&:\IAC_{\sigma}(\alpha_0,\theta,\Theta) \rightarrow \UU(\HH)\\
		\nonumber
		&:x=\pi_0\circ\alpha_0\circ\Theta(A)y\mapsto \phiTilde_{1,\sigma}(x)=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{\HsplitTilde}_{1;0}(A)\tilde{a}y\tilde{a}^\dagger
	\end{align}
	where $A\in\AA_{\sigma}$ and $y\in\textrm{Cone}_{\sigma}(\alpha_0,\theta)$. This map satisfies that
	\begin{enumerate}
		\item  for (the unique) $\xi\in\Aut{\AA_{C_\theta\cap \sigma}}$ such that
		\begin{equation}
			\Ad{y}\circ\pi_0\circ\alpha_0=\pi_0\circ\alpha_0\circ\xi
		\end{equation}
		we get that
		\begin{equation}\label{eq:ConditionDefinitionOfGroupMorphismTwoTranslations}
			\Ad{\phiTilde_1(x)}\circ\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{\HsplitTilde}_{1;0}=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{\HsplitTilde}_{1;0}\circ\Ad{A}\circ\xi.
		\end{equation}
		\item it is well defined (independent of the choice of $A$ and $y$).
		\item it is a group homomorphism.
		\item we have that
			\begin{equation}
				\tilde{a}^\dagger\phiTilde_1(x)\tilde{a}\in\IAC_\sigma(\alpha_0,\theta,\Theta\circ \Phi^U_{0;1}\otimes\Phi^D_{0;1}).
			\end{equation}
			If on top of this $x\in\IAC_{\nu^\sigma(\sigma)}$ then
			\begin{equation}
				\tilde{a}^\dagger\phiTilde_1(x)\tilde{a}\in\IAC_{\nu^\sigma(\sigma)}(\alpha_0,\theta,\Theta\circ \Phi^U_{0;1}\otimes\Phi^D_{0;1}).
			\end{equation}
		\item when additionally $x\in\IAC_{\sigma}^W(\alpha_0,\theta,\Theta\circ \Phi^U_{0;1}\otimes\Phi^D_{0;1})$ or when $x\in\IAC_{\nu^\sigma(\sigma)}^W(\alpha_0,\theta,\Theta\circ \Phi^U_{0;1}\otimes\Phi^D_{0;1})$ we obtain a similar result.
	\end{enumerate}
\end{lemma}
\begin{proof}
	The proof of this lemma is analogous to the proof of lemma \ref{lem:DefinitionOfGroupMorphism}.
\end{proof}
We now have to extend the above definition to the group
\begin{equation}
	\IAC_{L\times R}(\alpha_0,\theta,\Theta)=\{ab=ba|a\in\IAC_{L}(\alpha_0,\theta,\Theta),b\in\IAC_{R}(\alpha_0,\theta,\Theta)\}.
\end{equation}
\begin{lemma}\label{lem:PropertyTilde_aTwoTranslationsLeftAndRight}
	Define
	\begin{equation}
		\phiTilde_1:\IAC_{L\times R}(\alpha_0,\theta,\Theta)\rightarrow\UU(\HH):ab\mapsto \phiTilde_{1,L}(a)\phiTilde_{1,R}(b)
	\end{equation}
	where $a\in \IAC_{L}(\alpha_0,\theta,\Theta)$ and $b\in \IAC_{R}(\alpha_0,\theta,\Theta)$. This is well defined, by which we mean that
	\begin{equation}
		\phiTilde_{1,L}(a)\phiTilde_{1,R}(b)=\phiTilde_{1,R}(b)\phiTilde_{1,L}(a).
	\end{equation}
	This is still a group homomorphism.
\end{lemma}
\begin{proof}
	Identical to the proof of lemma \ref{lem:extensionOfPhi1Definition}.
\end{proof}
\begin{lemma}\label{lem:DefinitionOfWgMapTwoTranslations}
	Define again $\tilde{a}\defeq \pi_0\circ\alpha_0\circ\Theta(a)$, with $a$ defined through equation \eqref{eq:DefinitionOfGroupMorphismVAutEquationTwoTranslations}. Let
	\begin{align}
		\phiTilde_2:&\{\Ad{w^{-p}v^{-s}}(W_g)|g\in G,p,s\in\{-1,0,1\}\}\rightarrow \UU(\HH):\\
		\nonumber
		&\Ad{w^{-p}v^{-s}}(W_g) \mapsto \Ad{\tilde{a} w^{-p}v^{-s}}(W_g).
	\end{align}
	This satisfies
	\begin{align}\label{eq:lemDefinitionOfWgMapConditionTwoTranslations}
		&\Ad{\phiTilde_2(w^{-p}v^{-s}W_g v^{s} w^p)}\circ\pi_0\circ\alpha_0\circ\Theta\\
		\nonumber
		&=\pi_0\circ \alpha_0\circ\Theta\circ\gamma^{H}_{0;1}\circ\gamma^{\HsplitTilde}_{1;0}\circ\nu^{-p}\circ\tau^{-s}\circ\eta_g\circ\beta_g^U\circ\tau^s\circ\nu^p\circ\gamma^{\HsplitTilde}_{0;1}\circ\gamma^{H}_{1;0}.
	\end{align}
\end{lemma}
\begin{proof}
	The proof of this lemma is analogous to the proof of lemma \ref{lem:DefinitionOfWgMap}.
\end{proof}
\begin{lemma}\label{lem:phi1phi2matchingConditionH1ValuedIndex}
The $\phiTilde_1$ and $\phiTilde_2$ defined previously satisfy that for any $x\in\IAC_{\sigma}(\alpha_0,\theta,\Theta)$ we have that
	\begin{align}
		\phiTilde_1(\Ad{w^{-p} W_g w^{p}}(x))&=\Ad{\phiTilde_2(w^{-p} W_g w^{p})}(\phiTilde_1(x))\\
		\phiTilde_1(\Ad{v^{s}}(x))&=\Ad{v^{s}}(\phiTilde_1(x))\\
		\phiTilde_2(\Ad{v^s}(w^{-p} W_gw^{p}))&=\Ad{v^s}(\phiTilde_2(w^{-p} W_g w^{p}))
	\end{align}
	for any $p,s\in\{0,1\}$. For the second equation we need the stronger condition that $x\in\IAC_{\sigma}^W(\alpha_0,\theta,\Theta)$.
\end{lemma}
\begin{proof}
	This lemma is proven under lemma \ref{lem:phi1phi2matchingConditionH1ValuedIndexAppendix}.
\end{proof}
\begin{lemma}\label{lem:TranslatingSplittedTimeEvolution}
	There exist maps
	\begin{align}
		A_L&:[0,1]\rightarrow \UU(\AA_L):\lambda\mapsto A_{L}(\lambda)&A_R&:[0,1]\rightarrow \UU(\AA_R):\lambda\mapsto A_{R}(\lambda)
	\end{align}
	both continuous in norm topology and
	\begin{align}
		\Phi^{\mu\nu}:[0,1]\rightarrow\Aut{\AA_{W(C_\theta)^c\cap\mu\cap\nu}}:\lambda\mapsto \Phi^{\mu\nu}(\lambda)
	\end{align}
	where $\mu\in\{U,D\}$ and $\nu\in\{L,\nu(R)\}$, all four continuous in strong\footnote{Meaning that $\Phi^{\mu\nu}(\lambda)(A)$ is continuous for all $A\in\AA$.} topology, satisfying that
	\begin{align}
		\nu\circ\gamma^{\HsplitTilde}_{0;\lambda}\circ\nu^{-1}\circ\gamma^{\HsplitTilde}_{\lambda;0}&=\gamma^{H_L}_{0;\lambda}\otimes\gamma^{H_{\nu\circ\nu(R)}}_{0;\lambda}\circ\gamma^{\HsplitTilde}_{\lambda;0}\\
		\label{eq:TranslatingSplittedTimeEvolution}
		&=\Ad{A_L(\lambda)}\otimes\Ad{A_R(\lambda)}\circ\bigotimes_{\substack{\mu\in\{U,D\},\\\nu\in\{L,\nu(R)\}}}\Phi^{\mu\nu}(\lambda)
	\end{align}
	and that $\Phi^{\mu\nu}\circ\beta_g=\beta_g\circ\Phi^{\mu\nu}$.
\end{lemma}
\begin{proof}
	This lemma is proven in \ref{lem:SplittedAutomorphismAfterTranslatedIsVertical}.
\end{proof}
In what follows, let $A_L\defeq A_L(1)$, $A_R\defeq A_R(1)$ and $\Phi^{\mu\nu}=\Phi^{\mu\nu}(1)$. We will now show some properties for these operators. The first one is that they can be used to exchange $w$ and $\phiTilde_1/\phiTilde_2$:
\begin{lemma}\label{lem:TranslationOutOfPhi_KW}
	Define
	\begin{align}
		a_L&\defeq \pi_0\circ\alpha_0\circ\Theta(A_L)&a_R&\defeq \pi_0\circ\alpha_0\circ\Theta(A_R)
	\end{align}
	then for any $K\in\text{Cone}_{L\times\nu(R)}(\alpha_0,\theta)$ we get that
	\begin{equation}\label{eq:TranslationOutOfPhi_K}
		w^\dagger \phiTilde_1(K)w=\phiTilde_1(w^\dagger \: a_L\otimes a_R \: K \: a_L^\dagger\otimes a_R^\dagger \: w).
	\end{equation}
	Similarly we have that
	\begin{equation}\label{eq:TranslationOutOfPhi_W}
		w^\dagger \phiTilde_2(W_g)w=\phiTilde_1(w^\dagger \: a_L\otimes a_R \: w)\phiTilde_2(w^\dagger W_g w)\phiTilde_1(w^\dagger \: a_L^\dagger\otimes a_R^\dagger \: w).
	\end{equation}
\end{lemma}
\begin{proof}
	The proof is presented after lemma \ref{lem:TranslationOutOfPhi_KW_Appendix}.
\end{proof}
The second property is that the following lemma holds:
\begin{lemma}\label{lem:DefinitionOfEpsilons}
	Define $\epsilon^L_g\in\IAC_L(\alpha_0,\theta)$ and $\epsilon^R_g\in\IAC_R(\alpha_0,\theta)$ through
	\begin{align}
		\epsilon_g^\sigma\defeq \pi_0\circ\alpha_0\circ\Theta\circ\nu^{-1}(A_\sigma\:\eta_g^\sigma\circ\beta_{g}^{U\sigma}(A_\sigma^\dagger))
	\end{align}
	(where $A_\sigma$ was defined in lemma \ref{lem:TranslatingSplittedTimeEvolution}) then
	\begin{align}
		w^\dagger \phiTilde_2(W_g)w &= \phiTilde_1(\epsilon_g^L\otimes\epsilon_g^R)\phiTilde_2(w^\dagger W_g w)\\
		\label{eq:TransformationOfKUnderEpsilon}
		w^\dagger \phiTilde_1(K_g^\sigma)w&=v^\dagger\phiTilde_1(\epsilon_g^\sigma)v\phiTilde_1(w^\dagger K_g^\sigma w)\phiTilde_1(\epsilon_g^\sigma)^\dagger.
	\end{align}
\end{lemma}
\begin{proof}
	This lemma is proven after lemma \ref{lem:DefinitionOfEpsilonsAppendix}. The proof of \ref{lem:DefinitionOfEpsilonsAppendix} hinges on lemma \ref{lem:EqualityTwoTranslationsUsingConnectedPath}. We also remark that this last lemma is the only place where the compactness of the group is used in the main body of this paper.
\end{proof}
\begin{theorem}
	$\textrm{Index}_{\text{2 trans}}(\omega)=\textrm{Index}_{\text{2 trans}}(\omega\circ\gamma^H_{0;1}).$
\end{theorem}
\begin{proof}
	The start of the proof is identical to the proof of theorem \ref{thrm:IndexInvariantUnderLGA}. Take $\alpha\in\QAut{\AA}$ such that $\omega=\omega_0\circ\alpha$ for some product state $\omega_0$. Take $0<\theta_1<\theta_2<\theta_3<\pi/2$ arbitrary. Take $\alpha_L\in\Aut{\AA_L},\alpha_R\in\Aut{\AA_R},V_1\in\UU(\AA)$ and $\Theta\in\Aut{\AA_{W\left(C_{\theta_3}\right)^c}}$ such that
	\begin{equation}
		\alpha=\Ad{V_1}\circ\alpha_L\otimes\alpha_R\circ\Theta.
	\end{equation}
	Take $\tilde{\beta}_{g,1}$ such that $\omega\circ\tilde{\beta}_{g,1}=\omega$ and such that there exists some $V_{2,g}\in\UU(\AA)$ and some $\eta_g^{\sigma}\in\Aut{\AA_{\nu^{\sigma}(C_{\theta_1}\cap\sigma)}}$ (for $\sigma\in\{L,R\}$) satisfying
	\begin{equation}
		\tilde{\beta}_{g,1}=\Ad{V_{2,g}}\circ\eta_{g}^L\otimes\eta_{g}^R\circ\beta_g^U.
	\end{equation}
	Take $W_g,v,w,K_g^{L/R}$ and $b_g^{L/R}$ operators belonging to these automorphisms. Clearly $\alpha\circ\gamma^H_{0;1}$ satisfies $\omega\circ\gamma^{H}_{0;1}=\omega_0\circ\alpha\circ\gamma^{H}_{0;1}$. We also have that $\alpha\circ\gamma^H_{0;1}\in\QAut{\AA}$. To show this notice that
	\begin{align}
		\alpha\circ\gamma^H_{0;1}&=\Ad{V_1}\circ(\alpha_L\circ\gamma^{H_L}_{0;1}\otimes\alpha_R\circ\gamma^{H_R}_{0;1})\circ\gamma^{\HsplitTilde}_{1;0}\circ\Theta\circ\gamma^H_{0;1}\\
		&=\Ad{V_1}\circ(\alpha_L\circ\gamma^{H_L}_{0;1}\otimes\alpha_R\circ\gamma^{H_R}_{0;1})\circ\gamma^{\HsplitTilde}_{1;0}\circ\gamma^{H}_{0;1}\circ\gamma^{H}_{1;0}\circ\Theta\circ\gamma^H_{0;1}.
	\end{align}
	Because of lemma \ref{lem:TwoAngleLemmaPart1} and lemma \ref{lem:PropertiesLocallyGeneratedAutomorphisms} part 2 there exists a $\tilde{\Theta}\in\Aut{\AA_{W(C_{\theta_2})^c}}$ and some $\tilde V_1,A_1\in\UU(\AA)$ such that
	\begin{align}
		\alpha\circ\gamma^H_{0;1}&=\Ad{\tilde V_1}\circ(\alpha_L\circ\gamma^{H_L}_{0;1}\otimes\alpha_R\circ\gamma^{H_R}_{0;1})\circ\tilde\Theta\\
		(\alpha_L\circ\gamma^{H_L}_{0;1}\otimes\alpha_R\circ\gamma^{H_R}_{0;1})\circ\tilde\Theta&=\Ad{A_1}\circ \alpha_L\otimes\alpha_R\circ\Theta\circ\gamma^{H}_{0;1}.
	\end{align}
	If we now define the automorphism $\tilde{\beta}_{g,2}=\gamma^{H}_{1;0}\circ\tilde\beta_{g,1}\circ\gamma^{H}_{0;1}$ then this indeed satisfies that $\omega\circ\gamma^{H}_{0;1}\circ\tilde{\beta}_{g,2}=\omega\circ\gamma^{H}_{0;1}$. Define $\tilde\eta_g^\sigma$ through lemma \ref{lem:TwoAngleLemmaPart3ForTwoTranlations}. It satisfies that there exists a $\tilde V_{2,g}\in\UU(\AA),A_{2,g}^{\sigma}\in\UU(\AA_{\nu^{\sigma}(\sigma)})$ such that
	\begin{align}
		\label{eq:IndexInvariantUnderLGAEtaTildeDefiniton1TwoTrans}
		\gamma^{H}_{1;0}\tilde{\beta}_g\gamma^{H}_{0;1}&=\Ad{\tilde V_{2,g}}\circ\tilde{\eta}_g^L\otimes\tilde{\eta}_g^R\circ\beta_g^U\\
		\label{eq:IndexInvariantUnderLGAEtaTildeDefiniton2TwoTrans}
		\tilde{\eta}_g^\sigma&=\Ad{A_{2,g}^\sigma}\circ\gamma^{H_{\nu^{\sigma}(\sigma)}}_{1;0}\circ\eta_g^\sigma\circ\beta_g^{\sigma U}\circ\gamma^{H_{\nu^{\sigma}(\sigma)}}_{0;1}\circ(\beta_g^{\sigma U})^{-1}.
	\end{align}
	Take $\Phi$ satisfying equation \ref{eq:DefinitionOfGroupMorphismVAutEquationTwoTranslations} arbitrary and define 
	\begin{equation}
		\delta_g^\sigma:=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^{\HsplitTilde}_{0;1}(A_{2,g}^\sigma).
	\end{equation}
	Let
	\begin{equation}
		\phiTilde_1:\IAC_{L\times R}(\alpha_0,\Theta) \rightarrow \UU(\HH)
	\end{equation}
	be the group homomorphism defined from lemma \ref{lem:PropertyTilde_aTwoTranslationsLeftAndRight}. Take similarly
	\begin{equation}
		\phiTilde_2:\{\Ad{w^{-p}v^{-s}}(W_g)|g\in G,p,s\in\{-1,0,1\}\}\rightarrow \UU(\HH)
	\end{equation}
	the map defined in \ref{lem:DefinitionOfWgMapTwoTranslations}. The following operators now belong to $\omega\circ\gamma^{H}_{0;1}:$
	\begin{align}
		\tilde{v}&=\pi_0(A_1)v\pi_0(A_1)^\dagger\\
		\tilde{w}&=\pi_0(A_1)w\pi_0(A_1)^\dagger\\
		\tilde{W}_g&=\pi_0(A_1)\phi_1(\delta^L_g\otimes\delta^R_g)\phi_2( W_g)\pi_0(A_1^\dagger)\\
		\tilde{K}_g^\sigma&=\pi_0(A_1)\phi_1(v^\dagger \delta_g^\sigma v K_g^\sigma (\delta_g^\sigma)^\dagger) \pi_0(A_1)^\dagger\\
		\tilde{b}_g^\sigma&=\pi_0(A_1)w^\dagger \phi_1(\delta_g^R)w \phi_1(\epsilon_g^R)\phi_1(b_g^R)\phi_1(\delta_g^R)^\dagger\pi_0(A_1)^\dagger\\
		\tilde{h}_g&=\pi_0(A_1)\phi_1(h_g)\pi_0(A_1).
	\end{align}
	First we will show that this transformation indeed leaves the index invariant, then we will show that these operators indeed belong to $\omega\circ\gamma^H_{0;1}$. Let $\alpha\in\hom(G,U(1))$ be the old index and $\tilde{\alpha}\in\hom(G,U(1))$ the new one (of course I can only speak about the new index if these new operators are operators belonging to $\omega\circ\gamma^H_{0;1}$. Let us assume this for now and prove it later.). We have that
\begin{align}
\alpha(g)&=v^\dagger b_g^R v h_g K_g^R (b_g^R)^\dagger w^\dagger (K_g^R)^\dagger w\\
&=\phi_1(v^\dagger b_g^R v h_g K_g^R (b_g^R)^\dagger w^\dagger (K_g^R)^\dagger w)\\
&=\phi_1(v^\dagger b_g^R v h_g K_g^R (b_g^R)^\dagger)\phi_1( w^\dagger (K_g^R)^\dagger w).
\end{align}
Using equation \eqref{eq:TransformationOfKUnderEpsilon} on this gives us
\begin{align}
&=\phi_1(v^\dagger b_g^R v h_g K_g^R (b_g^R)^\dagger)\phi_1((\epsilon_g^R)^\dagger)w^\dagger\phi_1(  (K_g^R)^\dagger )wv^\dagger \phi_1(\epsilon_g^R)v\\
&=\phi_1(v^\dagger \epsilon_g^R b_g^R v h_g K_g^R (b_g^R)^\dagger (\epsilon_g^R)^\dagger)w^\dagger\phi_1(  (K_g^R)^\dagger )w.
\end{align}
This shows that the index is invariant under the $\phi_1$ and $\epsilon^R_g$ part (simultaneously). The fact that the index is invariant under the $\phi_1(\delta_g)$ part is now completely equivalent to the proof of lemma \ref{lem:TransformationUnderDeltaTwoTranslations}. The fact that the index remains unchanged by the $\Ad{\pi_0(A_1)}$ transformation is trivial. This concludes this part of the proof. Now we only need to show that these operators indeed belong to $\omega\circ\gamma^H_{0;1}$. The proof that the first four operators belong to $\omega\circ\gamma^H_{0;1}$ is completely analogous to what was done in the proof of \ref{thrm:IndexInvariantUnderLGA} and we will therefore focus on the $\tilde{b}_g^\sigma$ part. To show this, observe that we have
	\begin{align}
		&\Ad{\phi_1(\epsilon_g^R b_g^R)}\circ\pi_0\circ\alpha_0\circ\Theta\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{\HsplitTilde}_{1;0}\circ\nu^{-1}\circ\Ad{A_R\: \eta_g^R\circ\beta_g^{RU}(A_R^\dagger)}\circ\stkout{\nu\circ\nu^{-1}}\circ\eta_g^R\circ\nu\\
		\nonumber
		&\qquad\circ(\eta_g^R)^{-1}\circ\gamma^{\HsplitTilde}_{0;1}\circ\gamma^{H}_{1;0}\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{\HsplitTilde}_{1;0}\circ\nu^{-1}\circ\Ad{A_R\: \eta_g^R\circ\beta_g^{RU}(A_R^\dagger)}\circ\eta_g^R\circ\underline{\beta_g^{RU}}\circ\nu\\
		\nonumber
		&\qquad\circ\underline{(\beta_g^{\nu^{-1}(RU)})^{-1}}\circ(\eta_g^R)^{-1}\circ\gamma^{\HsplitTilde}_{0;1}\circ\gamma^{H}_{1;0}\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{\HsplitTilde}_{1;0}\circ\nu^{-1}\circ\Ad{A_R}\circ\eta_g^R\circ\beta_g^{RU}\circ\Ad{A_R^\dagger}\circ\nu\\
		\nonumber
		&\qquad\circ(\beta_g^{\nu^{-1}(RU)})^{-1}\circ(\eta_g^R)^{-1}\circ\gamma^{\HsplitTilde}_{0;1}\circ\gamma^{H}_{1;0}\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\underline{\nu^{-1}\circ\nu}\circ\gamma^{\HsplitTilde}_{1;0}\circ\nu^{-1}\circ\Ad{A_R}\circ\eta_g^R\circ\beta_g^{RU}\circ\Ad{A_R^\dagger}\circ\nu\circ\underline{\gamma^{\Hsplit}_{0;1}}\\
		\nonumber
		&\qquad \circ\underline{\nu^{-1}\circ\nu\circ\gamma^{\HsplitTilde}_{1;0}}\circ(\beta_g^{\nu^{-1}(RU)})^{-1}\circ(\eta_g^R)^{-1}\circ\gamma^{\HsplitTilde}_{0;1}\circ\gamma^{H}_{1;0}.
	\end{align}
After using the restriction to $R$ of equation \eqref{eq:TranslatingSplittedTimeEvolution}, this leads to
	\begin{align}
		&=\pi_0\circ\alpha_0\circ\Theta\circ\nu^{-1}\circ\gamma^H_{0;1}\circ\underline{\gamma^{\HsplitTilde}_{1;0}\circ\stkout{(\otimes_\mu\Phi^{\mu\nu(R)})^{-1}}}\circ\eta_g^R\circ\beta_g^{RU}\circ\underline{\stkout{(\otimes_\mu\Phi^{\mu\nu(R)})}\circ\gamma^{\HsplitTilde}_{0;1}}\circ\nu\\
		\nonumber
		&\qquad \circ\gamma^{\HsplitTilde}_{1;0}\circ(\beta_g^{\nu^{-1}(RU)})^{-1}\circ(\eta_g^R)^{-1}\circ\gamma^{\HsplitTilde}_{0;1}\circ\gamma^{H}_{1;0}.
	\end{align}
	On the other hand we have that
	\begin{equation}
		\Ad{w^\dagger \phi_1(\delta_g^\sigma)w}\circ\pi_0\circ\alpha_0\circ\Theta=\pi_0\circ\alpha_0\circ\Theta\circ\nu^{-1}\circ\gamma^H_{0;1}\circ\Ad{A^\sigma_{2,g}}\circ\gamma^H_{1;0}\circ\nu.
	\end{equation}
	This leads us to
	\begin{align}
		&\Ad{w^\dagger\phi_1(\delta_g^R)w\phi_1(\epsilon_g^R b_g^R)}\circ\pi_0\circ\alpha_0\circ\Theta\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\nu^{-1}\circ\gamma^H_{0;1}\circ\Ad{A_{2,g}^R}\circ\gamma^{\HsplitTilde}_{1;0}\circ\eta_g^R\circ\beta_g^{RU}\circ\gamma^{\HsplitTilde}_{0;1}\circ\nu\\
		\nonumber
		&\qquad \circ\gamma^{\HsplitTilde}_{1;0}\circ(\beta_g^{\nu^{-1}(RU)})^{-1}\circ(\eta_g^R)^{-1}\circ\gamma^{\HsplitTilde}_{0;1}\circ\gamma^{H}_{1;0}\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\nu^{-1}\circ\tilde\eta_g^R\circ\beta_g^{RU}\circ\nu\\
		\nonumber
		&\qquad \circ\gamma^{\HsplitTilde}_{1;0}\circ(\beta_g^{\nu^{-1}(RU)})^{-1}\circ(\eta_g^R)^{-1}\circ\gamma^{\HsplitTilde}_{0;1}\circ\gamma^{H}_{1;0}.
	\end{align}
	Now define $S=\{(0,y)|y\in\ZZ\}$ then
	\begin{align}
		&=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\nu^{-1}\circ\tilde\eta_g^R\circ\beta_g^{\nu(RU)}\circ\stkout{\beta_g^S}\circ\nu\\
		\nonumber
		&\qquad \circ\gamma^{\HsplitTilde}_{1;0}\circ\stkout{(\beta_g^{\nu^{-1}(S)})^{-1}}\circ(\beta_g^{RU})^{-1}\circ(\eta_g^R)^{-1}\circ\gamma^{\HsplitTilde}_{0;1}\circ\gamma^{H}_{1;0}.
	\end{align}
	Doing the same thing on the right will give us
	\begin{align}
		&\Ad{w^\dagger\phi_1(\delta_g^R)w\phi_1(\epsilon_g^R b_g^R)\phi_1(\delta_g^R)^\dagger}\circ\pi_0\circ\alpha_0\circ\Theta\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\nu^{-1}\circ\tilde\eta_g^R\circ\beta_g^{\nu(RU)}\circ\nu\circ\gamma^{\HsplitTilde}_{1;0}\circ(\beta_g^{RU})^{-1}\circ(\eta_g^R)^{-1}\circ\gamma^{\HsplitTilde}_{0;1}\circ\Ad{(A_{2,g}^R)^\dagger}\circ\gamma^{H}_{1;0}\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\nu^{-1}\circ\tilde\eta_g^R\circ\stkout{\beta_g^{\nu(RU)}}\circ\nu\circ\stkout{(\beta_g^{RU})^{-1}}\circ(\tilde\eta_g^R)^{-1}\circ\circ\gamma^{H}_{1;0}.
	\end{align}
	The role that the $A_1$ will play is analogous to the proof of \ref{thrm:IndexInvariantUnderLGA}, concluding the proof.
\end{proof}
\subsection{The $H^1(G,\TT)$-valued index is invariant under rotations by $90^\circ$}\label{sec:H1ValuedIndexInvariantUnderRotations}
Take
\begin{equation}
	\omega\in\left\{\omega\in\PP(\AA)\left| \begin{matrix}\omega\text{ is an SRE state,}\\\omega\circ\beta_g=\omega,\:\omega\circ\tau=\omega\text{ and }\omega\circ\nu=\omega\end{matrix} \right.\right\}
\end{equation}
arbitrary and let $\mu$ be the automorphism that rotates the lattice by $90^\circ$. This section will be dedicated to proving that
\begin{equation}
	\textrm{Index}_{\text{2 trans}}^{\AA,U(g)}(\omega)=\textrm{Index}_{\text{2 trans}}^{\AA,U(g)}(\omega\circ\mu).
\end{equation}
In what follows, let $\omega_0$ be the product state and let $\gamma^\Phi_{0;1}$ be the disentangler such that
\begin{equation}
	\omega=\omega_0\circ\gamma^\Phi_{0;1}.
\end{equation}
\input{Figures/Figure2}
Sometimes we will need a specific decomposition of this locally generated Automorphism:
\begin{lemma}\label{lem:DecompositionOfLGAInCross}
	Let $\{1,2,3,4\}$ be regions indicated in figure \ref{fig:IndexInvariantUnderRotationDecomposition} (including the red areas) and let $\AA_{\text{red}}$ be the part of the $C^*$ algebra that has support in the red regions of figure \ref{fig:IndexInvariantUnderRotationDecomposition}. There exists a $B\in\UU(\AA)$ and a $\Theta\in\Aut{\AA_{\text{red}}}$ such that $\beta^{\mu\nu}_g\circ\Theta=\Theta\circ\beta^{\mu\nu}_g$ (for all $\mu\in\{U,D\}$ and $\nu\in\{L,R\}$) satisfying
	\begin{equation}
		\gamma^\Phi_{0;1}=\Ad{B}\circ\gamma^{\sum_{i=1}^4\Phi_i}_{0;1}\circ\Theta
	\end{equation}
	where $\Phi_i$ is the restriction of $\Phi$ to region $i\in\{1,2,3,4\}$.
\end{lemma}
\begin{proof}
	Completely analogous to the proof of (for example) \ref{lem:PropertiesLocallyGeneratedAutomorphisms}.
\end{proof}
Let $A_{g,1},A_{g,2}\in\UU(\AA),\eta^\sigma_g\in\Aut{\AA_{\nu^{\sigma}(C_\theta\cap\sigma)}}$ and $\eta^\rho_{2,g}\in\Aut{\AA_{\tau^{\rho}(\mu(C_\theta)\cap\rho)}}$ be such that the automorphisms
\begin{align}
	\tilde{\beta}_{g,1}&=\Ad{A_{g,1}}\circ\eta_g^L\otimes\eta_g^R\circ\beta_g^U&\tilde{\beta}_{g,2}&=\Ad{A_{g,2}}\circ\eta_{2,g}^U\otimes\eta_{2,g}^D\circ\beta_g^L
\end{align}
satisfy $\omega\circ\tilde{\beta}_{g,1}=\omega\circ\tilde{\beta}_{g,2}=\omega$. Let $(\HH_0=\bigotimes_i\HH_{0,i},\pi_0=\bigotimes_{i=1}^4\pi_{0,i},\bigotimes_i\Omega_{0,i})$ be a GNS triple for $\omega_0$ (see the caption of figure \ref{fig:IndexInvariantUnderRotationDecomposition}). The following now holds:
\begin{lemma}\label{lem:DefinitionX_gLemma}
	There exists an $X_g\in\UU(\HH_0)$ satisfying that
	\begin{equation}\label{eq:DefinitionX_gLemma}
		\Ad{X_g}\circ\pi_0\circ\gamma^\Phi_{0;1}=\pi_0\circ\gamma^\Phi_{0;1}\circ\tilde{\eta}^U_g\circ\eta^R_g\circ\beta_g^{RU}
	\end{equation}
	where $\tilde{\eta}_g=\beta_g^U\circ\eta_{2,g^{-1}}\circ(\beta_g^U)^{-1}$.
\end{lemma}
\begin{proof}
	Let $W_g$ and $\tilde W_g$ be such that
	\begin{align}
		\Ad{W_g}\circ\pi_0\circ\gamma^\Phi_{0;1}& =\pi_0\circ\gamma^\Phi_{0;1}\circ\eta_g\circ\beta_g^U
		&\Ad{\tilde W_g} \circ\pi_0\circ\gamma^\Phi_{0;1}& =\pi_0\circ\gamma^\Phi_{0;1}\circ\eta_{2,g}\circ\beta_g^L
	\end{align}
	then
	\begin{align}
		\Ad{W_g\tilde{W}_{g^{-1}}}\circ\pi_0\circ\gamma^\Phi_{0;1}&=\pi_0\circ\gamma^\Phi_{0;1}\circ\eta_g\circ\beta_g^U\circ\eta_{2,g^{-1}}\circ(\beta_g^L)^{-1}\\
		&=\pi_0\circ\gamma^\Phi_{0;1}\circ\eta_g\circ\tilde{\eta}_g\circ\beta_g^{RU}\circ(\beta_g^{LD})^{-1}.
	\end{align}
	Now we use lemma \ref{lem:DecompositionOfLGAInCross} and obtain
	\begin{align}
		\Ad{W_g\tilde{W}_{g^{-1}}}\circ\pi_0\circ\Ad{B}\circ\gamma^{\sum_i\Phi_i}_{0;1}\circ\stkout{\Theta}&=\pi_0\circ\Ad{B}\circ\gamma^{\sum_i\Phi_i}_{0;1}\circ\stkout{\Theta}\circ\eta_g\circ\tilde{\eta}_g\circ\beta_g^{RU}\circ(\beta_g^{LD})^{-1}\\
		\Ad{\pi_0(B^\dagger)W_g\tilde{W}_{g^{-1}}\pi_0(B)}\circ\pi_0\circ\gamma^{\sum_i\Phi_i}_{0;1}&=\pi_0\circ\gamma^{\sum_i\Phi_i}_{0;1}\circ\eta_g\circ\tilde{\eta}_g\circ\beta_g^{RU}\circ(\beta_g^{LD})^{-1}\\
		\Ad{\pi_0(B^\dagger)W_g\tilde{W}_{g^{-1}}\pi_0(B)}\circ\pi_0&=\left(\pi_{0,1}\otimes\pi_{0,2}\circ\gamma^{\Phi_1+\Phi_2}_{0;1}\circ\eta_g^R\circ\tilde{\eta}_g^U\circ\beta_g^{RU}\circ\gamma^{\Phi_1+\Phi_2}_{1;0}\right)\\
		\nonumber
		&\qquad\otimes \left(\pi_{0,3}\otimes\pi_{0,4}\circ\gamma^{\Phi_3+\Phi_4}_{0;1}\circ\eta_g^L\circ\tilde{\eta}_g^D\circ(\beta_g^{LD})^{-1}\circ\gamma^{\Phi_3+\Phi_4}_{1;0}\right).
	\end{align}
	By appendix \ref{lem:SplittingOfUnitary}, there exist $\tilde{X}_g\in\UU(\HH_{0,1}\otimes\HH_{0,2})$ and $\tilde{Y}_g\in\UU(\HH_{0,3}\otimes\HH_{0,4})$ such that
	\begin{equation}
		\tilde{X}_g\otimes\tilde{Y}_g=\pi_0(B^\dagger)W_g\tilde{W}_{g^{-1}}\pi_0(B).
	\end{equation}
	Define $X_g=\pi_0(B)(\tilde{X}_g\otimes\id)\pi_0(B^\dagger)$. This indeed satisfies equation \eqref{eq:DefinitionX_gLemma} concluding the proof.
\end{proof}
\begin{lemma}
	Let $v,w,K_g^R$ and $b_g^R$ be such that
	\begin{align}
		\Ad{v}\circ\pi_0\circ\gamma^\Phi_{0;1}&=\pi_0\circ\gamma^\Phi_{0;1}\circ\tau\\
		\Ad{w}\circ\pi_0\circ\gamma^\Phi_{0;1}&=\pi_0\circ\gamma^\Phi_{0;1}\circ\nu\\
		\Ad{K_g^R}\circ\pi_0\circ\gamma^\Phi_{0;1}&=\pi_0\circ\gamma^\Phi_{0;1}\circ\tau^{-1}\circ\eta_g^R\circ\beta_g^{RU}\circ\tau\circ(\beta_g^{RU})^{-1}\circ(\eta_g^R)^{-1}\\
		\Ad{b_g^R}\circ\pi_0\circ\gamma^\Phi_{0;1}&=\pi_0\circ\gamma^\Phi_{0;1}\circ\nu^{-1}\circ\eta_g^R\circ\nu\circ(\eta_g^R)^{-1}
	\end{align}
	then
	\begin{equation}\label{eq:H^1IndexRotationInvariantHorizontalIndex}
		v^\dagger b_g^R vh_g K_g^R (b_g^R)^\dagger=\alpha(g)w^\dagger K_g^R w
	\end{equation}
	holds. Moreover $\alpha=\textrm{Index}_{\text{2 trans}}(\omega)$. If one now defines $\tilde{b}_g^R$ and $\tilde{K}_g^U$ such that
	\begin{align}
		\label{eq:H^1IndexRotationInvariantFirstDefinition}
		\tilde{b}_g^UK_g^R X_g&=v^\dagger X_g v\\
		\label{eq:H^1IndexRotationInvariantSecondDefinition}
		b_g^R\tilde{K}_g^UX_g&=w^\dagger X_g w
	\end{align}
	then
	\begin{equation}\label{eq:H^1IndexRotationInvariantVerticalIndex}
		w^\dagger \tilde b_g^U wh_g \tilde K_g^U (\tilde b_g^U)^\dagger=\tilde\alpha(g)v^\dagger \tilde K_g^U v
	\end{equation}
	holds. Moreover $\tilde\alpha=\textrm{Index}_{\text{2 trans}}(\omega\circ\mu)$.
\end{lemma}
\begin{proof}
	The existence of the $v,w,K_g^R$ and $b_g^R$ is due to the fact that $\gamma^\Phi_{0;1}\in \QAut{\AA}$. This follows from lemma \ref{lem:PropertiesLocallyGeneratedAutomorphisms} and from the fact that $\textrm{SQAut}_1(\AA)\subset \QAut{\AA}$. By construction this also implies that indeed $\alpha=\textrm{Index}_{\text{2 trans}}(\omega)$. We now only have to show the second part of the proof. We have that
	\begin{align}
		\Ad{\tilde{K}_g^U}\circ\pi_0\circ\gamma^\Phi_{0;1}&=\Ad{(b_g^R)^\dagger w^\dagger X_g w X_g^\dagger}\circ\pi_0\circ\gamma^\Phi_{0;1}\\
		&=\Ad{(b_g^R)^\dagger w^\dagger X_g w}\circ\pi_0\circ\gamma^\Phi_{0;1}\circ(\beta_g^{RU})^{-1}\circ(\eta_g^R)^{-1}\circ(\tilde{\eta}_g^U)^{-1}\\
		&=\Ad{(b_g^R)^\dagger}\circ\pi_0\circ\gamma^\Phi_{0;1}\circ\nu^{-1}\circ\tilde{\eta}_g^U\circ\eta_g^R\circ\beta_g^{RU}\circ\nu\circ(\beta_g^{RU})^{-1}\circ(\eta_g^R)^{-1}\circ(\tilde{\eta}_g^U)^{-1}\\
		&=\pi_0\circ\gamma^\Phi_{0;1}\circ\nu^{-1}\circ\tilde{\eta}_g^U\circ\beta_g^{RU}\circ\nu\circ(\beta_g^{RU})^{-1}\circ(\tilde{\eta}_g^U)^{-1}.
	\end{align}
	By similar arguments we get that
	\begin{equation}
		\Ad{\tilde{b}_g^U}\circ\pi_0\circ\gamma^\Phi_{0;1}=\pi_0\circ\gamma^\Phi_{0;1}\circ\tau^{-1}\circ\tilde{\eta}_g^U\circ\tau\circ(\tilde{\eta}_g^U)^{-1}.
	\end{equation}
	This also shows that
	\begin{equation}
		\Ad{\tilde{K}_g^U}\circ\pi_0\circ\gamma^\Phi_{0;1}\circ\mu=\pi_0\circ\gamma^\Phi_{0;1}\circ\mu\circ\mu^{-1}\circ\nu^{-1}\circ\tilde{\eta}_g^U\circ\beta_g^{RU}\circ\nu\circ(\beta_g^{RU})^{-1}\circ(\tilde{\eta}_g^U)^{-1}\circ\mu
	\end{equation}
	and similarly for $\tilde{b}_g^U$ and therefore these operators also belong to $\omega\circ\mu$. This together with the independence of the choice of $\tilde{\eta}_g$ proves the second result.
\end{proof}
\begin{lemma}
	The following equalities hold
	\begin{align*}
		[h_g ,w^\dagger \tilde{b}_g^U w]&=0 \Label{eq:H^1IndexRotationInvariantCommutator1}& [w^\dagger \tilde{b}_g^U w,v^\dagger b_g^R v]&=0 \Label{eq:H^1IndexRotationInvariantCommutator4}\\
		[h_g, v^\dagger b_g^R v]&=0 \Label{eq:H^1IndexRotationInvariantCommutator2}& [K_g^R,\tilde{b}_g^U] &= 0 \Label{eq:H^1IndexRotationInvariantCommutator5}\\
		[h_g ,K_g^R]&=0 \Label{eq:H^1IndexRotationInvariantCommutator3}& [K_g^R,v^\dagger \tilde{K}^U_g v] &= 0 \Label{eq:H^1IndexRotationInvariantCommutator6}
	\end{align*}
\end{lemma}
\begin{proof}
	All of the above commute as automorphisms on the $C^*$ algebra, we now have to show that the operators in the GNS space commute as well. First we will start by proving equations \eqref{eq:H^1IndexRotationInvariantCommutator1}, \eqref{eq:H^1IndexRotationInvariantCommutator2} and \eqref{eq:H^1IndexRotationInvariantCommutator3}. For any operator $x\in\UU(\HH_0)$ satisfying that there exists a $\xi\in\Aut{\AA}$ such that
	\begin{equation}
		\Ad{x}\circ\pi_0\circ\gamma^{\Phi}_{0;1}=\pi_0\circ\gamma^{\Phi}_{0;1}\circ\xi
	\end{equation}
	we get that
	\begin{equation}
		\Ad{x}(h_g)=\pi_0\circ\gamma^\Phi_{0;1}\circ\xi(U_{(-1,-1)}(g)).
	\end{equation}
	Applying this to these equations gives the desired result. To show the remaining equations decompose $\pi_0$ and $\gamma^\Phi_{0;1}$ as
	\begin{align}
		\gamma^\Phi_{0;1}&=\Ad{B}\circ\bigotimes_{i=1}^4\gamma^{\Phi_i}_{0;1}\circ\Theta&\pi_0&=\bigotimes_{i=1}^4\pi_{0,i}
	\end{align}
	where the $\pi_{0,i}$ are irreducible representations in $\AA_i$, the areas $i$ are indicated in figure \ref{fig:IndexInvariantUnderRotationDecomposition} and the $\Theta$ have support in the areas shaded red. This shows that up to some inner automorphisms the operators with an $R$ on top act on different parts of the decomposition of $\pi_0$ then the operators with a $U$ on top do. Combining this with lemma \ref{lem:SplittingOfUnitary} concludes the proof.
\end{proof}
\begin{lemma}
	$\tilde{\alpha}(g)=\alpha(g)$.
\end{lemma}
\begin{proof}
	We will work out the expression
	\begin{equation}\label{eq:H^1IndexRotationInvariantExpression}
		h_g v^\dagger b_g^R v w^\dagger\tilde{b}_g^U w K_g^R\tilde{K}_g^U X_g
	\end{equation}
	in two different ways. On the one hand we will use \eqref{eq:H^1IndexRotationInvariantCommutator4} together with equation \eqref{eq:H^1IndexRotationInvariantCommutator1} to get
	\begin{equation}
		\eqref{eq:H^1IndexRotationInvariantExpression}= \underline{w^\dagger\tilde{b}_g^U w h_g v^\dagger b_g^R v} K_g^R\tilde{K}_g^U X_g.
	\end{equation}
	Now using equation \eqref{eq:H^1IndexRotationInvariantHorizontalIndex} we get
	\begin{align}
		\eqref{eq:H^1IndexRotationInvariantExpression}&=\alpha(g)w^\dagger\tilde{b}_g^U w w^\dagger K_g^R w b_g^R\tilde{K}_g^U X_g\\
		&=\alpha(g)w^\dagger\tilde{b}_g^U  K_g^R X_g w\\
		&=\alpha(g)w^\dagger v^\dagger X_g v w
	\end{align}
	where we've used equation \eqref{eq:H^1IndexRotationInvariantSecondDefinition} in the first equality and \eqref{eq:H^1IndexRotationInvariantFirstDefinition} in the second equality. On the other hand, starting with equation \eqref{eq:H^1IndexRotationInvariantCommutator2}, \eqref{eq:H^1IndexRotationInvariantCommutator5} and \eqref{eq:H^1IndexRotationInvariantCommutator3} gives
	\begin{align}
		\eqref{eq:H^1IndexRotationInvariantExpression}&= \underline{v^\dagger b_g^R v h_g} w^\dagger\tilde{b}_g^U w K_g^R\tilde{K}_g^U X_g\\
		&=v^\dagger b_g^R v \underline{K_g^R h_g w^\dagger\tilde{b}_g^U w} \tilde{K}_g^U X_g.
	\end{align}
	Now using equation \eqref{eq:H^1IndexRotationInvariantVerticalIndex} we get
	\begin{align}
		\eqref{eq:H^1IndexRotationInvariantExpression}&=\tilde{\alpha}(g)v^\dagger b_g^R v K_g^R v^\dagger \tilde{K}_g^U v \tilde{b}_g^U X_g\\
		&=\tilde{\alpha}(g)v^\dagger b_g^R v \underline{v^\dagger \tilde{K}_g^U v \tilde{b}_g^U K_g^R} X_g\\
		&=\tilde{\alpha}(g)v^\dagger b_g^R \stkout{v v^\dagger} \tilde{K}_g^U \stkout{v v^\dagger} X_g v\\
		&=\tilde{\alpha}(g) v^\dagger w^\dagger X_g w v
	\end{align}
	where we've used equation \eqref{eq:H^1IndexRotationInvariantCommutator6} and \eqref{eq:H^1IndexRotationInvariantCommutator5} in the first equality, equation \eqref{eq:H^1IndexRotationInvariantFirstDefinition} in the second equality and equation \eqref{eq:H^1IndexRotationInvariantSecondDefinition} in the last equality. These two results can only be consistent if $\alpha(g)=\tilde{\alpha}(g)$ for all $g\in G$.
\end{proof}
\subsection{Stacking in the $H^1(G,\TT)$-valued index}\label{sec:StackingTwoTranslations}
Take $\AA$ a quasi local $C^*$ algebra on a two dimensional lattice and take $U(g)$ an on site group action arbitrary. Let
\begin{equation}
	\omega_1,\omega_2\in\{\omega\in\PP(\AA)| \omega\text{ satisfies assumption \ref{assumption:2Translations}}\}
\end{equation}
be two states. The goal of this section is to prove that
\begin{equation}\label{eq:IndexMorphismUnderStackingTwoTranslations}
	\textrm{Index}^{\AA^2,U(g)\otimes U(g)}_{\text{2 trans}}(\omega_1\otimes_{\text{stack}}\omega_2)=\textrm{Index}^{\AA,U(g)}_{\text{2 trans}}(\omega_1)\textrm{Index}^{\AA,U(g)}_{\text{2 trans}}(\omega_2).
\end{equation}
The proof of this is completely analogous to what was in section \ref{sec:StackingOneTranslation}.
\subsection{The $H^1$-valued index is invariant of choice of basis of on site Hilbert space}\label{sec:the-h2-valued-index-is-invariant-of-choice-of-basis-of-on-site-hilbert-space-TwoTranslations}
Let $V \in U(\CC^d)$ be a unitary operator on the on site Hilbert space and take $i_V$ as defined in subsection \ref{sec:QuasiLocalC*Algebra}. In this subsection we will prove that
\begin{align}
	&\textrm{Index}^{\AA,\Ad{V^\dagger}(U)}_{2\text{ trans}}(\theta,i_V^{-1}\circ\tilde{\beta}_g\circ i_V,i_V^{-1}\circ\eta_g\circ i_V,i_V^{-1}\circ\alpha_0\circ i_V,i_V^{-1}\circ\Theta\circ i_V,\omega\circ i_V,\omega_0\circ i_V)\\
	&=\textrm{Index}^{\AA,U}_{2\text{ trans}}(\theta,\tilde{\beta}_g,\eta_g,\alpha_0,\Theta,\omega,\omega_0).
\end{align}
The proof is completely analogous to the proof presented in subsection \ref{sec:the-h2-valued-index-is-invariant-of-choice-of-basis-of-on-site-hilbert-space}.
\subsection{Proof of theorem \ref{thrm:ExistenceSecondIndex}}\label{sec:ProofOf:thrm:ExistenceSecondIndex}
In this section we summarise the proof of theorem \ref{thrm:ExistenceSecondIndex}:
\begin{proof}
	The 2-cochain was defined in subsection \ref{sec:DefinitionH1Index}. The proof that it wasn't dependent on any of the choices made in assumption \ref{assumption:2Translations} was done in subsection \ref{sec:IndexIsInvariantUnderChoicesTwoTranslations}. The first item in the list concerning the invariance under locally generated automorphisms was shown in subsection \ref{sec:H1ValuedIndexInvariantUnderLGA's}. The proof of the second item concerning the relation between the 1d SPT index and the 2d translation SPT index is done in subsection \ref{sec:TwoTranslationDirectionsExample}. The proof of the third item concerning the stacking is done in subsection \ref{sec:StackingTwoTranslations}. The proof of the last item concerning a change of basis of the on site Hilbert space is done in subsection \ref{sec:the-h2-valued-index-is-invariant-of-choice-of-basis-of-on-site-hilbert-space-TwoTranslations}. This concludes the proof.
\end{proof}
\subsection{Proof of lemma \ref{lem:SRE_Implies_QDisentanglable_TwoTranslations}}\label{sec:ProofOfMainResult2}
In this subsection we prove lemma \ref{lem:SRE_Implies_QDisentanglable_TwoTranslations}.
\begin{proof}
	Completely analogous to the proof of lemma \ref{lem:SRE_Implies_QDisentanglable_OneTranslation} except that the support area of the $\eta_g$ automorphism has become smaller. To deal with this, replace the $\textrm{SQAut}(\AA)$ in theorem 3.1 of \cite{ogata2021h3gmathbb} by $\textrm{SQAut}_2(\AA)$ (see definition \ref{def:SQAut2}) and observe that the resulting $\eta_g$ has the right support.
\end{proof}
\bibliography{TSPT}
\bibliographystyle{plain}
\end{document}