\documentclass[12pt,a4paper,twoside]{article}
\usepackage{graphicx,xcolor,textpos}
\usepackage{helvet}
\usepackage[english]{babel}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bbm}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{relsize}
\usepackage[margin=0.7in]{geometry}
\usepackage{physics}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{changepage}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{verbatim}
\usepackage{url}
\usepackage{tikz}
\usetikzlibrary{calc}


\newcommand{\stkout}[1]{\ifmmode\text{\sout{\ensuremath{#1}}}\else\sout{#1}\fi}
\renewcommand{\d}{\text{d}}
\renewcommand{\O}{\mathcal{O}}
\newcommand{\e}{\mathlarger{e}}
\newcommand{\defeq}{\vcentcolon=}
\let\originalleft\left
\let\originalright\right
\renewcommand{\left}{\mathopen{}\mathclose\bgroup\originalleft}
\renewcommand{\right}{\aftergroup\egroup\originalright}
\title{1D SPT classification with translation symmetry}
\author{Tijl Jappens}
\date{\today}

\newcommand{\UU}{\mathcal U}
\newcommand{\KK}{\mathcal K}
\newcommand{\BB}{\mathcal B}
\newcommand{\PP}{\mathcal P}
\newcommand{\HH}{\mathcal H}
\newcommand{\ZZ}{\mathbb Z}
\newcommand{\CC}{\mathbb C}
\newcommand{\TT}{\mathbb T}
\renewcommand{\AA}{\mathcal A}
\newcommand{\LL}{\mathcal L}
\newcommand{\RR}{\mathbb R}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\one}{\mathbbm{1}}

\newcommand{\Ad}[1]{\textrm{Ad}\left(#1\right)}
\newcommand{\Aut}[1]{\textrm{Aut}\left(#1\right)}
\newcommand{\QAut}[1]{\textrm{QAut}\left(#1\right)}

\newcommand{\qe}{\underset{\text{q.e.}}{\sim}}
\newcommand{\ue}{\underset{\text{u.e.}}{\sim}}

\newcommand{\Mod}[1]{\mathrm{mod} #1}

\theoremstyle{definition}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{Definition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{remark}[theorem]{Remark}

\numberwithin{equation}{section}
\begin{document}
\section{Setup and definitions}
In what follows let $\AA$ be a 2-dimensional quasi-local $C^*$ algebra. Let
\begin{equation}
	C_\theta\defeq \left\{(x,y)\in\ZZ^2\left|\tan(\theta)\leq\abs{\frac{y}{x}}\right.\right\}
\end{equation}
be the horizontal cone. We will use $\tau$ to denote the automorphism that moves every element one site upward. Of course this is only an automorphism if the $C^*$ algebra is translation invariant in the vertical direction which we will assume. In what follows we will sometimes need to widen our cone vertically by one site we therefore define $W$ such that
\begin{equation}
	W(\AA_{C_\theta})\defeq\AA_{C_\theta}\cup\tau(\AA_{C_\theta})\cup\tau^{-1}(\AA_{C_\theta}).
\end{equation}
\subsection{Disentangle by $\textrm{QAut}(\AA)$}
Similarly what was done in \cite{ogata2021h3gmathbb} we will define an index on the space of states that can be disentangled by a Q-automorphism. This class of automorphisms is defined as:
\begin{definition}
	Take $\alpha\in\Aut{\AA}$. We say that $\alpha\in\QAut{\AA}$ if and only if $\forall\theta\in]0,\pi/2[$ there exists an $\alpha_L\in\Aut{\AA_L},\alpha_R\in\Aut{\AA_R},V_1\in\UU(\AA)$ and a $\Theta\in\Aut{W(\AA_{C_\theta})^c}$\footnote{Note that our definition of $\textrm{QAut}(\AA)$ is slightly different from \cite{ogata2021h3gmathbb} because of this widening $W$.} such that
	\begin{equation}
	\alpha=\Ad{V_1}\circ\alpha_L\otimes\alpha_R\circ\Theta.
	\end{equation}
\end{definition}
We will often write $\alpha_0$ to mean $\alpha_L\otimes\alpha_R$. Take $\omega\in\PP(\AA)$ to be such that
\begin{enumerate}
	\item  there exists an automorphism $\alpha\in\QAut{\AA}$ and a product state $\omega_0\in\PP(\AA)$ satisfying
	\begin{align}
		\omega=\omega_0\circ\alpha.
	\end{align}
	\item $\forall \theta\in]0,\pi/2[$ there exists a map
	\begin{equation}
		\tilde\beta:G\rightarrow\Aut{\AA}:g\mapsto\tilde\beta_g
	\end{equation}
	satisfying
	\begin{align}
		\omega\circ\tilde\beta_g&=\omega&\tilde\beta_g=\Ad{V_2}\circ\eta^L_g\otimes\eta^R_g\circ\beta^U_g
	\end{align}
	where $V_{g,2}\in\UU(\AA),\eta^L_g\in\Aut{\AA_L\cap\AA_{C_\theta}}$ and $\eta^R_g\in\Aut{\AA_R\cap\AA_{C_\theta}}$.
\end{enumerate}
Take $(\HH_0=\HH_L\otimes\HH_R,\pi_0=\pi_L\otimes\pi_R,\Omega_0)$ a GNS triple of $\omega_0$. In this paper we will deal with states that are translation invariant ($\omega\circ\tau=\omega$) and can be disentangled by a Q-automorphism. Because we will be working with states that are translation invariant it make sense to define the translation action on the GNS space of $\omega_0$:
\begin{lemma}
	There exists a unique $v\in\UU(\HH_0)$ such that
	\begin{align}
		\Ad{v}\circ\pi_0&=\pi_0\circ\alpha_0\circ\Theta\circ\tau\circ\Theta^{-1}\circ\alpha_0^{-1}&&\text{and}&\pi_0(V_1)v\pi_0(V_1^\dagger)\Omega_0&=\Omega_0.
	\end{align}
\end{lemma}
\begin{proof}
	Since $\omega\circ\tau=\omega$ we get by uniqueness of the GNS triple that
	\begin{equation}
		(\HH_0,\pi_0\circ\alpha\circ\tau,\Omega_0)\ue (\HH_0,\pi_0\circ\alpha,\Omega_0).
	\end{equation}
	This shows that there exists a $\tilde{v}\in\UU(\HH_0)$ satisfying
	\begin{align}
		\Ad{\tilde{v}}\circ\pi_0\circ\alpha&=\pi_0\circ\alpha\circ\tau&\tilde{v}\Omega_0&=\Omega_0.
	\end{align}
	Since $\alpha=\Ad{V_1}\circ\alpha_0\circ\Theta$ we get that
	\begin{align}
		\Ad{\pi_0(V_1^\dagger)\tilde{v}\pi_0(V_1)}\circ\pi_0\circ\alpha_0\circ\Theta&=\pi_0\circ\alpha_0\circ\Theta\circ\tau&\tilde{v}\Omega_0&=\Omega_0.
	\end{align}
	Choosing $v=\pi_0(V_1^\dagger)\tilde{v}\pi_0(V_1)$  concludes the proof.
\end{proof}
\subsection{Cone operators}
 We now define a subgroup of $\UU(\HH_0)$ that includes the representations of cone automorphisms:
\begin{definition}
	Take $0<\theta<\pi/2$ and $\alpha_\sigma\in\Aut{\AA_{\sigma}}$. Take $x\in\UU(\HH_{R/L})\otimes\mathbbm{1}_{\HH_{L/R}}$ then we say that $x$ is a cone operator on the right/left (or in short $x\in\textrm{Cone}_{\sigma}(\alpha_0,\theta)$ for $\sigma\in\{L,R\}$) if there exists a $\xi\in\Aut{W(\AA_{C_\theta})\cap\AA_\sigma}$ such that
	\begin{equation}
		\Ad{x}\circ\pi_0\circ\alpha_0=\pi_0\circ\alpha_0\circ\xi.
	\end{equation}
	$\textrm{Cone}_\sigma(\alpha_0,\theta)$ is a subgroup of $\UU(\HH_\sigma)\otimes\mathbbm{1}_{\sigma^c}$. We have that
	\begin{align}\label{eq:CommutantPropertyCones}
		\textrm{Cone}_R(\alpha_0,\theta)&\subseteq\textrm{Cone}_L(\alpha_0,\theta)'&\textrm{Cone}_L(\alpha_0,\theta)&\subseteq\textrm{Cone}_R(\alpha_0,\theta)'.
	\end{align}
\end{definition}
\begin{proof}
	The proof of equation \eqref{eq:CommutantPropertyCones} just follows from the fact that we defined $\textrm{Cone}_\sigma(\alpha_0,\theta)$ such that
	\begin{align}
		\textrm{Cone}_L(\alpha_0,\theta)&\subseteq \UU(\HH_L)\otimes\mathbbm{1}_{\HH_R}&\textrm{Cone}_R(\alpha_0,\theta)&\subseteq \mathbbm{1}_{\HH_L} \otimes \UU(\HH_R).
	\end{align}
\end{proof}
We will also define the a generalisation of this. We will define a subgroup of $\UU(\HH_0)$ that includes both the group $\UU(\pi_0\circ\alpha_0\circ\Theta(\AA_R))$ and the representations of cone automorphisms:
\begin{definition}
	Take $0<\theta<\pi/2$, $\alpha_\sigma\in\Aut{\AA_{\sigma}}$ and $\Theta\in\Aut{W(\AA_{C_\theta})^c}$. Take $x\in\UU(\HH_0)$ then we say that $x$ is an inner after cone operator on the right (or in short $x\in \textrm{IAC}_R(\alpha_0,\theta,\Theta)$) if there exists an $A\in\AA_R$ and a $y\in\textrm{Cone}_R(\alpha_0,\theta)$ such that
	\begin{equation}
		x=\pi_0\circ\alpha_0\circ\Theta(A)y.
	\end{equation}
	$\textrm{IAC}_R$ is a subgroup of $\UU(\HH_0)$. If we define similarly $\textrm{IAC}_L$ we get that
	\begin{align}\label{eq:CommutantProperty}
		\textrm{IAC}_R(\alpha_0,\theta,\Theta)&\subseteq\textrm{IAC}_L(\alpha_0,\theta,\Theta)'&\textrm{IAC}_L(\alpha_0,\theta,\Theta)&\subseteq\textrm{IAC}_R(\alpha_0,\theta,\Theta)'.
	\end{align}
\end{definition}
\begin{proof}
	Take $u_L\in\textrm{IAC}_L(\alpha_0,\theta,\Theta)$ and $u_R\in\textrm{IAC}_R(\alpha_0,\theta,\Theta)$ arbitrary. Take $A_\sigma\in\AA_\sigma$ and $v_\sigma\in\textrm{IAC}_\sigma(\alpha_0,\theta,\Theta)$ (for $\sigma\in\{L,R\}$) such that $u_\sigma=\pi_0\circ\alpha_0\circ\Theta(A_\sigma)v_\sigma$. We then get
	\begin{align}
		&[u_L,u_R]=u_Lu_R-u_Ru_L\\
		&=\pi_0\circ\alpha_0\circ\Theta(A_L)v_L\pi_0\circ\alpha_0\circ\Theta(A_R)v_R-\pi_0\circ\alpha_0\circ\Theta(A_R)v_R\pi_0\circ\alpha_0\circ\Theta(A_L)v_L\\
		&=\pi_0\circ\alpha_0\circ\Theta(A_L)\Ad{v_L}\circ\pi_0\circ\alpha_0\circ\Theta(A_R)v_Lv_R-\pi_0\circ\alpha_0\circ\Theta(A_R)v_R\pi_0\circ\alpha_0\circ\Theta(A_L)v_L.
	\end{align}
	If we now take $\xi_\sigma\in\Aut{\AA_{C_\theta}\cap\AA_\sigma}$ such that $\Ad{v_\sigma}\circ\pi_0\circ\alpha_0=\pi_0\circ\alpha_0\circ\xi_\sigma$ we get that
	\begin{align}
		&=\pi_0\circ\alpha_0\circ\Theta(A_L)\pi_0\circ\alpha_0\circ\Theta\circ\xi_L(A_R)v_Lv_R-\pi_0\circ\alpha_0\circ\Theta(A_R)v_R\pi_0\circ\alpha_0\circ\Theta(A_L)v_L\\
		&=\pi_0\circ\alpha_0\circ\Theta(A_L)\pi_0\circ\alpha_0\circ\Theta(A_R)v_Lv_R-\pi_0\circ\alpha_0\circ\Theta(A_R)v_R\pi_0\circ\alpha_0\circ\Theta(A_L)v_L\\
		&=\pi_0\circ\alpha_0\circ\Theta(A_R)\pi_0\circ\alpha_0\circ\Theta(A_L)v_Lv_R-\pi_0\circ\alpha_0\circ\Theta(A_R)v_R\pi_0\circ\alpha_0\circ\Theta(A_L)v_L.
	\end{align}
	Using property \eqref{eq:CommutantPropertyCones} we now get that
	\begin{align}
		&=\pi_0\circ\alpha_0\circ\Theta(A_R)\pi_0\circ\alpha_0\circ\Theta(A_L)v_Rv_L-\pi_0\circ\alpha_0\circ\Theta(A_R)v_R\pi_0\circ\alpha_0\circ\Theta(A_L)v_L\\
		&=\pi_0\circ\alpha_0\circ\Theta(A_R)v_R\pi_0\circ\alpha_0\circ\Theta\circ\xi_R^{-1}(A_L)v_L-\pi_0\circ\alpha_0\circ\Theta(A_R)v_R\pi_0\circ\alpha_0\circ\Theta(A_L)v_L\\
		&=0
	\end{align}
	concluding the proof.
\end{proof}
The following lemma shows that if a unitary on the GNS space of $\omega_0$ has an adjoint action that is the product of cones then it is a product of cone operators:
\begin{lemma}\label{lem:UsingIrreducibilityAndWignerTheorem}
	Take $x\in\UU(\HH_0)$ such that there exist $\xi_\sigma\in\Aut{\AA_{C_\theta}\cap\AA_\sigma}$ (for $\sigma\in\{L,R\}$) satisfying
	\begin{equation}
		\Ad{x}\circ\pi_0\circ\alpha_0=\pi_0\circ\alpha_0\circ\xi_L\otimes\xi_R
	\end{equation}
	then there exist $x_\sigma\in\textrm{Cone}_\sigma(\alpha_0,\theta)$ such that
	\begin{equation}
		x=x_L\otimes x_R.
	\end{equation}
	These are unique up to a phase.
\end{lemma}
\begin{proof}
	Clearly we have that for all $a\in\AA_R$
	\begin{equation}
		\Ad{x}(\mathbbm{1}_{\HH_L}\otimes \pi_R\circ\alpha_R(A))=\mathbbm{1}_{\HH_L}\otimes \pi_R\circ\alpha_R\circ\xi_R(A).
	\end{equation}
	Because $\pi_R$ is irreducible this means that $\Ad{u}$ gives rise to a $*-$isomorphism on $\BB(\HH_R)$. By the Wigner theorem such a $*-$isomorphism must be represented by a unitary. The irreducibly of $\pi_R$ then proves that this unitary is in fact unique. Doing the same thing on the left concludes the proof.
\end{proof}
Following Yoshiko Ogata \cite{ogata2021h3gmathbb} we now define objects using the following lemma:
\begin{lemma}\label{lem:Definition_W_And_u}
	There unitaries $W_g\in\UU(\HH_0)$ and $u_{\sigma}(g,h)\in\UU(\HH_{\sigma})$ for all $g,h\in G$ and for all $\sigma\in\{L,R\}$ satisfying
	\begin{align}
		\Ad{W_g}\circ\pi_0&=\pi_0\circ\alpha_0\circ\Theta\circ\eta_g\circ\beta_g^U\circ\Theta^{-1}\circ\alpha_0^{-1}\\
		\Ad{u_\sigma(g,h)}\circ\pi_\sigma&=\pi_\sigma\circ\alpha_\sigma\circ\eta_g^\sigma\circ\beta_g^{\sigma R}\circ\eta_h^{\sigma U}\circ(\beta_g^{\sigma R})^{-1}\circ(\eta^\sigma_{gh})^{-1}\circ\alpha_\sigma\\
		u_L(g,h)\otimes u_R(g,h)&=W_gW_hW_{gh}^{-1}.
	\end{align}
\end{lemma}
\begin{proof}
	See \cite{ogata2021h3gmathbb}, lemma 2.1.
\end{proof}
These objects will be the starting point for our definition. Clearly the $u_\sigma(g,h)$ are elements of $\textrm{Cone}_\sigma(\alpha_0,\theta)$. The $W_g$ have the following property:
\begin{lemma}\label{lem:AdjointOverConeIsInCone}
	Take $\Xi^{\sigma}\in\textrm{Cone}_\sigma(\alpha_0,\theta)$ (for all $\sigma\in\{L,R\}$) then $\Ad{W_g}(\Xi^\sigma)\in\textrm{Cone}_\sigma(\alpha_0,\theta)$ (for all $g\in G$).	If more generally we take $\Xi^\sigma\in\textrm{IAC}_\sigma(\alpha_0,\Theta)$ then $\Ad{W_g}(\Xi^\sigma)\in\textrm{IAC}_\sigma(\alpha_0,\Theta)$.
\end{lemma}
\begin{proof}
	Take $\tilde{\Xi}^\sigma$ such that $\Xi^\sigma=\tilde{\Xi}^\sigma\otimes\mathbbm{1}_{\HH_{\sigma^c}}$. Take $\xi_\sigma\in\Aut{W(\AA_{C_\theta})\cap\AA_\sigma}$ such that
	\begin{equation}
		\Ad{\tilde\Xi^\sigma}\circ\pi_\sigma\circ\alpha_\sigma=\pi_\sigma\circ\alpha_\sigma\circ \xi_\sigma.
	\end{equation}
	We have that
	\begin{equation}
		\Ad{\Ad{W_g}(\Xi^R)}\circ\pi_0\circ\alpha_0\circ\Theta=\pi_0\circ\alpha_0\circ\Theta\circ\zeta_{g,R}
	\end{equation}
	where
	\begin{equation}
		\zeta_{g,\sigma}\defeq \eta_g\circ\beta_g^{U}\circ\xi_\sigma\circ(\beta_g^{U})^{-1}\circ\eta_g^{-1}.
	\end{equation}
	Since $\zeta_{g,\sigma}\in\Aut{\AA_{C_\theta}\cap\AA_{\sigma}}$ we get that
	\begin{equation}
		\Ad{\Ad{W_g}(\Xi^R)}\circ\pi_0\circ\alpha_0=\pi_L\circ\alpha_L\otimes\pi_R\circ\alpha_R\circ\zeta_{g,R}.
	\end{equation}
	This together with the irreducibility of $\pi_R$ proves that $\Ad{\Ad{W_g}(\Xi^R)}$ gives rise to a $*$-isomorphism on $\BB(\HH_R)$. By the Wigner theorem this can be implemented by some unitary say $Z_{g,R}\in\UU(\HH_R)$. We now only have to show that $\Ad{W_g}(\Xi^R)=\mathbbm{1}_{\HH_L}\otimes Z_{g,R}$. This follows (up to a phase) from the irreducibility of $\pi_0$. To show the second result we only need to observe that for any $A\in\AA_R$ we get that
	\begin{align}
		\Ad{W_g}\left(\pi_0\circ\alpha_0\circ\Theta(A)\Xi_R\right)&=\Ad{W_g}\circ\pi_0\circ\alpha_0\circ\Theta(A)\Ad{W_g}(\Xi_R)\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\xi_R(A)\Ad{W_g}(\Xi_R).
	\end{align}
	By the previous result, this is clearly in $\textrm{IAC}_R(\alpha_0,\theta,\Theta)$ concluding the proof.
\end{proof}
We now have to define one more object
\begin{lemma}\label{lem:Definition_K}
	There exist $K_g^L\in\UU(\HH_L)$ and $K_g^R\in\UU(\HH_R)$ such that
	\begin{equation}
		v^\dagger W_g v W_g^\dagger=K_g^L\otimes K_g^R=K_g
	\end{equation}
	and they are unique (up to a phase). They satisfy the identity
	\begin{equation}
		\Ad{K^R_g}\circ\pi_0=\pi_0\circ \alpha_0\circ \tau^{-1}\circ \eta_g^R\circ\beta_g^{RU}\circ\tau\circ(\beta_g^{RU})^{-1}\circ(\eta_g^{R})^{-1}\circ\alpha_0^{-1}.\quad\footnote{Observe in particular that $\Theta$ has cancelled out}
	\end{equation}
\end{lemma}
\begin{proof}
	By some straightforward calculation we have that
	\begin{align}
		\Ad{K_g}\circ\pi_0&=\Ad{v^\dagger W_g v W_g^\dagger}\circ\pi_0\\
		&=\bigotimes_{\sigma=L,R}\pi_\sigma\circ\alpha_\sigma\circ\tau^{-1}\circ \eta_g^\sigma\circ\beta_g^{\sigma U}\circ\tau\circ(\beta_g^{\sigma U})^{-1}\circ(\eta_g^{\sigma})^{-1}\circ\alpha_\sigma^{-1}.
	\end{align}
	Using lemma \ref{lem:UsingIrreducibilityAndWignerTheorem} concludes the proof that these unitaries exist and are unique up to a $G-$dependent phase.
\end{proof}
These $K_g^\sigma$ are also elements of $\textrm{Cone}_\sigma(\alpha_0,\theta)$. 
\section{Definition of the index}
\begin{lemma}\label{lem:Definition2Cochain}
	There exists a $C:G^2\rightarrow U(1)$ such that 
	\begin{equation}\label{eq:Definition2Cochain}
		K_g^R\Ad{W_g}\left(K_h^R\Ad{W_hW_{gh}^\dagger}\left((K_{gh}^R)^\dagger\right)\right)u_
		R(g,h)=C(g,h)v^\dagger u_R(g,h)v
	\end{equation}
	for all $g,h\in G.$
\end{lemma}
\begin{proof}
	Since the GNS representation is irreducible this is equivalent to showing that the left and righthandside of equation \eqref{eq:Definition2Cochain} have the same adjoint action on the GNS representation. We first prove the result for the full tensor product:
	\begin{align}
		&v^\dagger u_L(g,h)v v^\dagger u_R(g,h) v\\
		&=v^\dagger (u_L(g,h)\otimes u_R(g,h)) v\\
		&=v^\dagger W_g W_h W_{gh}^{-1}v\\
		&=K_gW_g v^\dagger W_h W_{gh}^{-1}v\\
		&=K_gW_g K_h W_h v^\dagger W_{gh}^{-1}v\\
		&=K_gW_g K_h W_h W_{gh}^\dagger K_{gh}^\dagger\\
		&=K_gW_g K_h W_h W_{gh}^\dagger K_{gh}^\dagger W_{gh}W_h^\dagger W_g^\dagger W_gW_hW_{gh}^\dagger\\
		&=K_g\Ad{W_g}\left(K_h\Ad{W_hW_{gh}^\dagger}\left(K_{gh}^\dagger\right)\right)u_L(g,h)\otimes u_
			R(g,h).
	\end{align}
	Using lemma \ref{lem:AdjointOverConeIsInCone} we get that
	\begin{align}
		&(K_g^L\otimes K_g^R)\Ad{W_g}\left((K_h^L\otimes K_h^R)\Ad{W_hW_{gh}^\dagger}\left((K_{gh}^L\otimes K_{gh}^R)^{-1}\right)\right)\\
		&=K_g^L\Ad{W_g}\left(K_h^L\Ad{W_hW_{gh}^\dagger}\left((K_{gh}^L)^\dagger\right)\right)\otimes K_g^R\Ad{W_g}\left(K_h^R\Ad{W_hW_{gh}^\dagger}\left((K_{gh}^R)^\dagger\right)\right)
	\end{align}
	concluding the proof.
\end{proof}
\begin{lemma}
	The function $C$ as defined in lemma \ref{lem:Definition2Cochain} is a 2-cochain.
\end{lemma}
\begin{proof}
	Take lemma 2.4 from \cite{ogata2021h3gmathbb} there it is stated that there exists a 3-cochain $C'$ such that
	\begin{equation}\label{eq:defintion3CochainProof2Cochain}
		u_R(g,h)u_R(gh,k)u_R(g,hk)^\dagger\Ad{W_g}(u_R(h,k)^\dagger)=C'(g,h,k)\mathbbm{1}.
	\end{equation}
	It is clear that this 3-cochain is invariant under the substitution
	\begin{align}
		W_g&\rightarrow v^\dagger W_g v&u_R(g,h)&\rightarrow v^\dagger u_R(g,h)v.
	\end{align}
	If we now prove that it is also invariant under the substitution
	\begin{align}\label{eq:SubstitutionForProofCochain}
		W_g&\rightarrow K_g W_g&u_R(g,h)&\rightarrow K_g^R\Ad{W_g}\left(K_h^R\Ad{W_hW_{gh}^\dagger}\left((K_{gh}^R)^\dagger\right)\right)u_
		R(g,h)
	\end{align}
	we have proved our result because using equation \eqref{eq:Definition2Cochain} we then get that
	\begin{equation}
		\stkout{C'(g,h,k)}=C(h,k)C(gh,k)^{-1}C(g,hk)C(g,h)^{-1}\stkout{C'(g,h,k)}
	\end{equation}
	proving the result. Inserting substitution \eqref{eq:SubstitutionForProofCochain} into \eqref{eq:defintion3CochainProof2Cochain} gives
	\begin{align}
		&u_R(g,h)u_R(gh,k)u_R(g,hk)^\dagger\Ad{W_g}\left(u_R(h,k)^\dagger\right)\\
		\rightarrow&K_g^R\Ad{W_g}\left(K_h^R\Ad{W_hW_{gh}^\dagger}\left((K_{gh}^R)^\dagger\right)\right)u_
		R(g,h)\\
		\nonumber
		&K_{gh}^R\Ad{W_{gh}}\left(K_k^R\Ad{W_kW_{ghk}^\dagger}\left((K_{ghk}^R)^\dagger\right)\right)u_
		R(gh,k)\\
		\nonumber
		&u_R(g,hk)^\dagger \Ad{W_g}\left( \Ad{W_{hk}W_{ghk}^\dagger}(K^R_{ghk})(K^R_{hk})^{\dagger} \right)(K^R_g)^\dagger\\
		\nonumber
		&\Ad{K_gW_g}\left(u_R(h,k)^\dagger \Ad{W_h}\left(\Ad{W_kW_{hk}^\dagger}\left(K_{hk}^R\right)(K^R_k)^\dagger\right)(K^R_h)^\dagger\right).
	\end{align}
	Using the fact that $W_gW_hW_{gh}^\dagger=u_L\otimes u_R(g,h)$ one now gets
	\begin{align}
		=&K_g^R\Ad{W_g}\left(K_h^R\Ad{W_hW_{gh}^\dagger}\left((K_{gh}^R)^\dagger\right)\right)W_gW_hW_{gh}^\dagger u_L(g,h)^\dagger\\
		\nonumber
		&K_{gh}^R\Ad{W_{gh}}\left(K_k^R\Ad{W_kW_{ghk}^\dagger}\left((K_{ghk}^R)^\dagger\right)\right) W_{gh}W_kW_{ghk}^\dagger u_L(gh,k)^\dagger\\
		\nonumber
		&W_{ghk}W_{hk}^\dagger W_{g}^\dagger u_L(g,hk) \Ad{W_g}\left( \Ad{W_{hk}W_{ghk}^\dagger}(K^R_{ghk})(K^R_{hk})^{\dagger} \right)\stkout{(K^R_g)^\dagger}\\
		\nonumber
		&\:\stkout{K^R_g}\Ad{W_g}\left(u_R(h,k)^\dagger \Ad{W_h}\left(\Ad{W_kW_{hk}^\dagger}\left(K_{hk}^R\right)(K^R_k)^\dagger\right)(K^R_h)^\dagger\right)(K^R_g)^\dagger.
	\end{align}
	We will now use the fact that the $u_L$ commutes with everything that has support only on the right. Combining this with lemma \ref{lem:AdjointOverConeIsInCone} gives
	\begin{align}
		=&K_g^R\Ad{W_g}\left(K_h^R\Ad{W_hW_{gh}^\dagger}\left((K_{gh}^R)^\dagger\right)\right)W_gW_hW_{gh}^\dagger u_L(g,h)^\dagger\\
		\nonumber
		&K_{gh}^R\Ad{W_{gh}}\left(K_k^R\Ad{W_kW_{ghk}^\dagger}\left((K_{ghk}^R)^\dagger\right)\right) W_{gh}W_kW_{ghk}^\dagger u_L(gh,k)^\dagger\\
		\nonumber
		&\Ad{W_{ghk}W_{hk}^\dagger W_{g}^\dagger}  \left(\Ad{W_g}\left( \Ad{W_{hk}W_{ghk}^\dagger}(K^R_{ghk})(K^R_{hk})^{\dagger} \right)\right)\\
		\nonumber
		&u_R(g,hk)^\dagger\Ad{W_g}\left(u_R(h,k)^\dagger \Ad{W_h}\left(\Ad{W_kW_{hk}^\dagger}\left(K_{hk}^R\right)(K^R_k)^\dagger\right)(K^R_h)^\dagger\right)(K^R_g)^\dagger\\
		=&K_g^R\Ad{W_g}\left(K_h^R\Ad{W_hW_{gh}^\dagger}\left((K_{gh}^R)^\dagger\right)\right)W_gW_hW_{gh}^\dagger u_L(g,h)^\dagger\\
		\nonumber
		&K_{gh}^R\Ad{W_{gh}}\left(K_k^R\Ad{W_kW_{ghk}^\dagger}\left((K_{ghk}^R)^\dagger\right)\right)  \\
		\nonumber
		&\Ad{W_{gh}W_kW_{hk}^\dagger W_{g}^\dagger}  \left(\Ad{W_g}\left( \Ad{W_{hk}W_{ghk}^\dagger}(K^R_{ghk})(K^R_{hk})^{\dagger} \right)\right)\\
		\nonumber
		&u_R(gh,k)u_R(g,hk)^\dagger\Ad{W_g}\left(u_R(h,k)^\dagger \Ad{W_h}\left(\Ad{W_kW_{hk}^\dagger}\left(K_{hk}^R\right)(K^R_k)^\dagger\right)(K^R_h)^\dagger\right)(K^R_g)^\dagger\\
		=&K_g^R\Ad{W_g}\left(K_h^R\Ad{W_hW_{gh}^\dagger}\left((K_{gh}^R)^\dagger\right)\right)W_gW_hW_{gh}^\dagger (K^R_g)^\dagger\\
		\nonumber
		&K_{gh}^R\Ad{W_{gh}}\left(K_k^R\Ad{W_kW_{ghk}^\dagger}\left((K_{ghk}^R)^\dagger\right)\right)\\
		\nonumber
		&\Ad{W_{gh}W_kW_{hk}^\dagger W_{g}^\dagger}  \left(\Ad{W_g}\left( \Ad{W_{hk}W_{ghk}^\dagger}(K^R_{ghk})(K^R_{hk})^{\dagger} \right)\right)\\
		\nonumber
		&W_{gh}W_h^\dagger W_g^\dagger u_R(g,h) u_R(gh,k)u_R(g,hk)^\dagger\Ad{W_g}\left(u_R(h,k)^\dagger\right)\\
		\nonumber
		&\Ad{W_g}\left(\Ad{W_h}\left(\Ad{W_kW_{hk}^\dagger}\left(K_{hk}^R\right)(K^R_k)^\dagger\right)(K^R_h)^\dagger\right)(K^R_g)^\dagger
	\end{align}
	Filling in the equation for the 3-cochain (equation \eqref{eq:defintion3CochainProof2Cochain}) now gives
	\begin{align}
		=&C'(g,h,k)K_g^R\Ad{W_g}\left(K_h^R\Ad{W_hW_{gh}^\dagger}\left((K_{gh}^R)^\dagger\right)\right)W_gW_hW_{gh}^\dagger \\
		\nonumber
		&K_{gh}^R\Ad{W_{gh}}\left(K_k^R\Ad{W_kW_{ghk}^\dagger}\left((K_{ghk}^R)^\dagger\right)\right)\\
		\nonumber
		&\Ad{W_{gh}W_kW_{hk}^\dagger \stkout{W_{g}^\dagger}}  \left(\stkout{\Ad{W_g}}\left( \Ad{W_{hk}W_{ghk}^\dagger}(K^R_{ghk})(K^R_{hk})^{\dagger} \right)\right)\\
		\nonumber
		&W_{gh}W_h^\dagger W_g^\dagger\Ad{W_g}\left(\Ad{W_h}\left(\Ad{W_kW_{hk}^\dagger}\left(K_{hk}^R\right)(K^R_k)^\dagger\right)(K^R_h)^\dagger\right)(K^R_g)^\dagger.
	\end{align}
	Fully writing out the adjoints now gives:
	\begin{align}
	=&C'(g,h,k)K_g^RW_gK_h^RW_hW_{gh}^\dagger (K_{gh}^R)^\dagger W_{gh}W_h^\dagger W_g^\dagger W_gW_hW_{gh}^\dagger \\
	\nonumber
	&K_{gh}^RW_{gh}K_k^RW_kW_{ghk}^\dagger(K_{ghk}^R)^\dagger W_{ghk}W_k^\dagger W_{gh}^\dagger  \\
	\nonumber
	&W_{gh}W_kW_{hk}^\dagger W_{hk}W_{ghk}^\dagger K^R_{ghk} W_{ghk}W_{hk}^\dagger(K^R_{hk})^{\dagger} W_{hk}W_k^\dagger W_{gh}^\dagger\\
	\nonumber
	&W_{gh}W_h^\dagger W_g^\dagger W_gW_h W_kW_{hk}^\dagger K_{hk}^RW_{hk}W_k^\dagger(K^R_k)^\dagger W_h^\dagger (K^R_h)^\dagger W_g^\dagger (K^R_g)^\dagger\\
	=&\mathbbm{1}C'(g,h,k)
	\end{align}
	concluding the proof.
\end{proof}
Our translation index is now defined as
\begin{definition}
	Take $C$ to be the 2-cochain defined \ref{lem:Definition2Cochain} then we define the index as
	\begin{equation}
	\textrm{Index}(\theta,\tilde{\beta}_g,\eta_g,\alpha_0,\Theta,\omega,\omega_0)\defeq\expval{C}\in H^2(G,\TT)
	\end{equation}
	and (as advertised) it is only a function of the automorphisms (and the product state) not on the choice of the GNS triple of $\omega_0$ or on the choice of phases in $W_g,u_L(g,h),u_R(g,h),v,K_g^L$ and $K_g^R$.
\end{definition}
\begin{proof}
	Clearly the construction is invariant under the choice of GNS triple. Now we will show that it is invariant under the choice of phases of our operators. Clearly the 2-cochain $C$ is invariant under
	\begin{align}
		u_L(g,h)&\rightarrow \alpha(g)\alpha(g)\alpha(gh)^{-1}\beta(g,h)^{-1} u_L(g,h)&u_R(g,h)&\rightarrow \beta(g,h)u_R(g,h)\\
		W_g&\rightarrow\alpha(g)W_g&v&\rightarrow \gamma v.
	\end{align}
	Under the transformation
	\begin{align}
		K_g^L&\rightarrow \delta(g)^{-1}K_g^L&K_g^R&\rightarrow \delta(g)K_g^R
	\end{align}
	we get $C(g,h)\rightarrow \delta(g)\delta(h)\delta(gh)^{-1}C(g,h)$ which is clearly still in the same equivalence class concluding the proof.
\end{proof}
\section{The index is independent of the choices we made}
In this section we will show that the index is only dependent on $\omega$ and $\omega_0$ and not on the choices of our automorphisms. First we show independence of $\alpha$ and its decomposition.
\begin{lemma}
	Take $\omega_{01},\omega_{02}\in\PP(\AA)$ product states, take $\alpha_1,\alpha_2\in\Aut{\AA}$, take $V_{11},V_{12}\in\UU(\AA)$, take $\alpha_{L/R,1},\alpha_{L/R,2}\in\Aut{\AA_{L/R}}$ and take $\Theta_1,\Theta_2\in \Aut{\AA_{W(C_\theta)^c}}$ to be such that
	\begin{align}
		\alpha_1&=\Ad{V_{11}}\circ\alpha_{01}\circ\Theta_1&\alpha_2&=\Ad{V_{12}}\circ\alpha_{02}\circ \Theta_2
	\end{align}
	and satisfying
	\begin{equation}
		\omega_{01}\circ\alpha_1=\omega_{02}\circ\alpha_2=\omega
	\end{equation}
	then
	\begin{equation}
		\textrm{Index}(\theta,\tilde{\beta}_g,\eta_g,\alpha_{0,1},\Theta_1,\omega,\omega_{01})=\textrm{Index}(\theta,\tilde{\beta}_g,\eta_g,\alpha_{0,2},\Theta_2,\omega,\omega_{02}).
	\end{equation}
\end{lemma}
\begin{proof}
	We will first prove the result in the case that $\omega_0=\omega_{01}=\omega_{02}$ and then generalise this result. Since $\omega_0\circ\alpha_2\circ\alpha_1^{-1}=\omega_0$ there exists a $\tilde{w}\in\UU(\HH_0)$ such that
	\begin{equation}
		\pi_0\circ\alpha_2\circ\alpha_1^{-1}=\Ad{\tilde{w}}\circ\pi_0.
	\end{equation}
	Now define $w\in\UU(\HH_0)$ to be
	\begin{equation}
		w\defeq \pi_0(V_{11})\tilde{w} \pi_0(V_{11}^\dagger)
	\end{equation}
	then
	\begin{equation}
		\pi_0\circ\alpha_{02}\circ\Theta_2=\Ad{w}\circ\pi_0\circ\alpha_{01}\circ\Theta_1.
	\end{equation}
	Now take $W_{g,1},u_{R,1}(g,h)$ and $K^R_{g,1}$ to be the operators belonging to the first choice (with arbitrary phases). 
	We have (see \cite{ogata2021h3gmathbb} lemma 2.11)
	\begin{align}
		\Ad{wW_{g,1}w^\dagger}\circ\pi_0&=\pi_0\circ \alpha_{02}\circ\Theta_2\circ\eta_g\circ\beta_g^U\circ\Theta_2^{-1}\circ\alpha_{02}^{-1},\\
		\Ad{wu_{R,1}(g,h)w^\dagger}\circ\pi_0&=\pi_0\circ \alpha_{02}\circ\eta_g^R\circ\beta_g^{RU}\eta_h^R\beta_{h}^{RU}(\beta_{gh}^{RU})^{-1}(\eta_{gh}^R)^{-1}\circ\alpha_{02}^{-1}
	\end{align}
	and through similar arguments we get
	\begin{align}
		\Ad{wvw^\dagger}\circ\pi_0&=\pi_0\circ\alpha_{02}\circ\Theta_2\circ\tau\circ\Theta_2^{-1}\circ\alpha_{02}^{-1}\\
		\Ad{wK^R_{g,1}w^\dagger}\circ\pi_0&=\pi_0\circ \alpha_{02}\circ\tau^{-1}\circ\eta_g^R\circ\beta_g^{RU}\circ\tau\circ(\beta_g^{RU})^{-1}\circ(\eta^R_g)^{-1}\circ\alpha_{02}^{-1}.
	\end{align}
	This shows that $wW_{g,1}w^\dagger,wu_{R,1}(g,h)w^\dagger$ and $wK^R_{g,1}w^\dagger$ are operators belonging to the second choice (with our new translation operator). Since our index is invariant under this substitution this concludes the proof when $\omega_0=\omega_{01}=\omega_{02}$. Now suppose that $\omega_{01}\neq\omega_{02}$. Since they are both product states there exists a $\gamma\in\Aut{\AA}$ satisfying $\omega_{02}=\omega_{01}\circ\gamma$ that is of the form $\gamma=\gamma^L\otimes\gamma^R$. We now have
	\begin{equation}
		\textrm{Index}(\theta,\tilde{\beta}_g,\eta_g,\alpha_{0,2},\Theta_2,\omega,\omega_{02})=\textrm{Index}(\theta,\tilde{\beta}_g,\eta_g,\alpha_{0,2},\Theta_2,\omega,\omega_{01}\circ\gamma)=\textrm{Index}(\theta,\tilde{\beta}_g,\eta_g,\gamma\circ\alpha_{0,2},\Theta_2,\omega,\omega_{01})
	\end{equation}
	concluding the proof.
\end{proof}
We now show that the index is invariant under some transformation parametrised by the group $\textrm{IAC}_R$:
\begin{lemma}\label{lem:TransformationUnderDelta}
	Take $\omega_0,\theta,\alpha_0,\Theta$ and $\eta_g$ as usual, take $v,W_{g,1},u_{\sigma,1}(g,h)$ and $K_{g,1}^\sigma$ the operators corresponding to these automorphisms and take $\delta^\sigma_g\in\textrm{IAC}_\sigma(\alpha_0,\theta,\Theta)$ (for all $\sigma\in\{L,R\}$ and all $g\in G$). Define
	\begin{align}
		W_{g,2}&\defeq\delta_g W_{g,1}\\
		u_{\sigma,2}(g,h)&\defeq \delta_g^\sigma W_{g,1}\delta_h^\sigma W_{g,1}^\dagger u_{\sigma,1}(g,h)(\delta_{gh}^\sigma)^\dagger\\
		K^\sigma_{g,2}&\defeq v^\dagger \delta_g^\sigma v K_{g,1}^\sigma (\delta_g^\sigma)^\dagger
	\end{align}
	then the index of $v,W_{g,1},u_{\sigma,1}(g,h)$ and $K_{g,1}^\sigma$ is equal to the index of $v,W_{g,2},u_{\sigma,2}(g,h)$ and $K_{g,2}^\sigma$.
\end{lemma}
\begin{proof}
	First we will prove that we still have that
	\begin{equation}\label{eq:TransformationUnderDeltaProofNewUIsSplit}
		u_{L,2}(g,h)u_{R,2}(g,h)=W_{gh,2}W_{h,2}^\dagger W_{g,2}^\dagger.
	\end{equation}
	To do this first insert the definition to obtain
	\begin{align}
		u_{L,2}(g,h)u_{R,2}(g,h)=\delta_g^L W_{g,1}\delta_h^L W_{g,1}^\dagger u_{L,1}(g,h)(\delta_{gh}^L)^\dagger \delta_g^R W_{g,1}\delta_h^R W_{g,1}^\dagger u_{R,1}(g,h)(\delta_{gh}^R)^\dagger.
	\end{align}
	Since by lemma \ref{lem:AdjointOverConeIsInCone}, $\delta_g^R W_{g,1}\delta_h^R W_{g,1}^\dagger\in\textrm{IAC}_R(\alpha_0,\theta,\Theta)$ we get because of equation \eqref{eq:CommutantProperty} that
	\begin{align}
		&=\delta_g^L W_{g,1}\delta_h^L W_{g,1}^\dagger \delta_g^R W_{g,1}\delta_h^R W_{g,1}^\dagger u_{L,1}(g,h)(\delta_{gh}^L)^\dagger  u_{R,1}(g,h)(\delta_{gh}^R)^\dagger\\
		&=\delta_g^L \delta_g^R W_{g,1}\delta_h^L \stkout{ W_{g,1}^\dagger W_{g,1}}\delta_h^R W_{g,1}^\dagger u_{L,1}(g,h)  u_{R,1}(g,h)(\delta_{gh}^L)^\dagger(\delta_{gh}^R)^\dagger
	\end{align}
	concluding the proof of equation \eqref{eq:TransformationUnderDeltaProofNewUIsSplit}. Using this we obtain:
	\begin{align}
		&K_{g,2}^RW_{g,2}K_{h,2}^{R}W_{h,2}W_{gh,2}^\dagger(K_{gh,2}^R)^\dagger W_{gh,2}W_{h,2}^\dagger W_{g,2}^\dagger u_{R,2}(g,h)\\
		=&K_{g,2}^RW_{g,2}K_{h,2}^{R}W_{h,2}W_{gh,2}^\dagger(K_{gh,2}^R)^\dagger u_{L,2}(g,h)^\dagger\\
		=&K_{g,2}^RW_{g,2}K_{h,2}^{R}W_{h,2}W_{gh,2}^\dagger u_{L,2}(g,h)^\dagger (K_{gh,2}^R)^\dagger\\
		=&K_{g,2}^RW_{g,2}K_{h,2}^{R}\stkout{W_{h,2}W_{gh,2}^\dagger W_{gh,2}W_{h,2}^\dagger} W_{g,2}^\dagger u_{R,2}(g,h) (K_{gh,2}^R)^\dagger.
	\end{align}
	Filling this in the definition of the 2-cochain gives
	\begin{align}
		C_2(g,h)&=K_{g,2}^RW_{g,2}K_{h,2}^{R}W_{g,2}^\dagger u_{R,2}(g,h) (K_{gh,2}^R)^\dagger v^\dagger u_{R,2}(g,h)^\dagger v\\
		&=v^\dagger \delta_g^R v K_{g,1}^R (\delta_g^R)^\dagger \delta_g W_{g,1}v^\dagger \delta_h^R v K_{h,1}^R (\delta_h^R)^\dagger W_{g,1}^\dagger \delta_g^\dagger\\
		\nonumber
		&\qquad \delta_g^R W_{g,1}\delta_h^R W_{g,1}^\dagger u_{R,1}(g,h)\stkout{(\delta_{gh}^R)^\dagger \delta_{gh}^R} (K_{gh,1}^R)^\dagger v^\dagger \stkout{(\delta_{gh}^R)^\dagger v  v^\dagger \delta^R_{gh}} u_{R,1}(g,h)^\dagger W_{g,1}(\delta^R_h)^\dagger W_{g,1}^\dagger(\delta_g^R)^\dagger v.
	\end{align}
	We now insert $(K_{h,1}^R)^\dagger W_{g,1}^\dagger (K_{g,1}^R)^\dagger K_{g,1}^R W_{g,1}K_{h,1}^R=\mathbbm{1}:$
	\begin{align}	
		C_2(g,h)&=v^\dagger \delta_g^R v K_{g,1}^R (\delta_g^R)^\dagger \delta_g W_{g,1}v^\dagger \delta_h^R v K_{h,1}^R (\delta_h^R)^\dagger W_{g,1}^\dagger \delta_g^\dagger\\
		\nonumber
		&\qquad \delta_g^R W_{g,1}\delta_h^R \left((K_{h,1}^R)^\dagger W_{g,1}^\dagger (K_{g,1}^R)^\dagger K_{g,1}^R W_{g,1}K_{h,1}^R\right) W_{g,1}^\dagger u_{R,1}(g,h) (K_{gh,1}^R)^\dagger v^\dagger u_{R,1}(g,h)^\dagger v\\
		\nonumber
		&\qquad v^\dagger W_{g,1}(\delta^R_h)^\dagger W_{g,1}^\dagger(\delta_g^R)^\dagger v.
	\end{align}
	Filling in the old index now gives:
	\begin{align}
		C_2(g,h)&=C_1(g,h)v^\dagger \delta_g^R v K_{g,1}^R (\delta_g^R)^\dagger \delta_g W_{g,1}v^\dagger \delta_h^R v K_{h,1}^R (\delta_h^R)^\dagger W_{g,1}^\dagger \delta_g^\dagger\\
		\nonumber
		&\qquad \delta_g^R W_{g,1}\delta_h^R (K_{h,1}^R)^\dagger W_{g,1}^\dagger (K_{g,1}^R)^\dagger v^\dagger W_{g,1}(\delta^R_h)^\dagger W_{g,1}^\dagger(\delta_g^R)^\dagger v
	\end{align}
	Using equation \eqref{eq:CommutantProperty} we now get:
	\begin{align}
		C_2(g,h)&=C_1(g,h)v^\dagger \delta_g^R v K_{g,1}^R \stkout{\delta_g^L} W_{g,1}v^\dagger \delta_h^R v K_{h,1}^R (\delta_h^R)^\dagger W_{g,1}^\dagger \stkout{(\delta_g^L)^\dagger}\\
		\nonumber
		&\qquad  W_{g,1}\delta_h^R (K_{h,1}^R)^\dagger W_{g,1}^\dagger (K_{g,1}^R)^\dagger v^\dagger W_{g,1}(\delta^R_h)^\dagger W_{g,1}^\dagger(\delta_g^R)^\dagger v\\
		&=C_1(g,h)v^\dagger \delta_g^R v K_{g,1}^\stkout{R} W_{g,1}v^\dagger \delta_h^R v \stkout{K_{h,1}^R (\delta_h^R)^\dagger W_{g,1}^\dagger W_{g,1}\delta_h^R (K_{h,1}^R)^\dagger} W_{g,1}^\dagger (K_{g,1}^\stkout{R})^\dagger v^\dagger W_{g,1}(\delta^R_h)^\dagger W_{g,1}^\dagger(\delta_g^R)^\dagger v\\
		&=C_1(g,h)v^\dagger \delta_g^R v K_{g,1} W_{g,1}v^\dagger \delta_h^R v W_{g,1}^\dagger (K_{g,1})^\dagger v^\dagger W_{g,1}(\delta^R_h)^\dagger W_{g,1}^\dagger(\delta_g^R)^\dagger v\\
		&=C_1(g,h)v^\dagger \delta_g^R W_{g,1} \delta_h^R W_{g,1}^\dagger  W_{g,1}(\delta^R_h)^\dagger W_{g,1}^\dagger(\delta_g^R)^\dagger v\\
		&=C_1(g,h)
	\end{align}
	concluding the proof.
\end{proof}
We will now show that the index is independent on the choice of $\tilde{\beta}_g$ and its decomposition.
\begin{lemma}\label{lem:InvarianceUnderChoiceBeta}
	Take $\tilde{\beta}_{g,1},\tilde{\beta}_{g,1}\in\Aut{\AA},V_{g,21},V_{g,22}\in\UU(\AA),\eta_{g,1}^L,\eta_{g,2}^L\in \Aut{\AA_L\cap\AA_{C_\theta}}$ and $\eta_{g,1}^R,\eta_{g,2}^R\in \Aut{\AA_R\cap\AA_{C_\theta}}$ such that there exist $V_{g,21},V_{g,22}\in\UU(\AA)$ satisfying
	\begin{align}\label{eq:InvarianceUnderChoiceBetaTwoBetas}
		\tilde{\beta}_{g,1}&=\Ad{V_{g,21}}\circ\eta_{g,1}\circ\beta^U_g&\tilde{\beta}_{g,2}&=\Ad{V_{g,22}}\circ\eta_{g,2}\circ\beta^U_g
	\end{align}
	and
	\begin{equation}
		\omega\circ\tilde{\beta}_{g,1}=\omega\circ\tilde{\beta}_{g,2}=\omega
	\end{equation}
	then
	\begin{equation}
		\textrm{Index}(\theta,\tilde{\beta}_{g,1},\eta_{g,1},\alpha_{0},\Theta,\omega,\omega_0)=\textrm{Index}(\theta,\tilde{\beta}_{g,2},\eta_{g,2},\alpha_{0},\Theta,\omega,\omega_0).
	\end{equation}
\end{lemma}
\begin{proof}
	Take 
	\begin{equation}\label{eq:InvarianceUnderChoiceBetaAlphaDecomposition}
		\alpha=\Ad{V_1}\circ\alpha_{0}\circ\Theta
	\end{equation}
	the usual decomposition. Since
	\begin{equation}
		\omega_0\circ\alpha\circ\tilde{\beta}_{g,1}\circ(\tilde{\beta}_{g,2})^{-1}=\omega_0\circ\alpha
	\end{equation}
	there exist $\tilde{\delta}_g\in\UU(\HH_0)$ such that
	\begin{equation}
		\Ad{\tilde{\delta}_g}\circ\pi_0\circ\alpha=\pi_0\circ\alpha\circ\tilde{\beta}_{g,2}(\tilde{\beta}_{g,1})^{-1}.
	\end{equation}
	Inserting equation \eqref{eq:InvarianceUnderChoiceBetaTwoBetas} and \eqref{eq:InvarianceUnderChoiceBetaAlphaDecomposition} in this gives
	\begin{equation}
		\Ad{\tilde{\delta}_g}\circ\pi_0\circ\Ad{V_1}\circ\alpha_0\circ\Theta=\pi_0\circ\Ad{V_1}\circ\alpha_0\circ\Theta\circ\Ad{V_{g,21}}\circ\eta_{g,1}\circ\eta_{g,2}^{-1}\circ\Ad{V_{g,22}^\dagger}.
	\end{equation}
	Putting the $V$'s to the other side gives:
	\begin{equation}
		\Ad{\pi_0\circ\alpha_0\circ\Theta(V_{g,22}^\dagger)\pi_0(V_1^\dagger)\tilde{\delta}_g\pi_0(V_1)\pi_0\circ\alpha_0\circ\Theta(V_{g,21})}\circ\pi_0=\pi_0\circ\alpha_0\circ\eta_{g,2}\circ(\eta_{g,1})^{-1}\circ\alpha_0^{-1}.
	\end{equation}
	Since the last equation is split we have again by the irreducibility of $\pi_\sigma$ and the Wigner theorem that we can take $\delta_g^L\in\textrm{Cone}_L(\alpha_0,\theta)$ and $\delta_g^R\in\textrm{Cone}_R(\alpha_0,\theta)$ such that
	\begin{equation}
		\delta_g^L\otimes\delta_g^R=\alpha_0\circ\Theta(V_{g,21}^\dagger)\pi_0(V_1^\dagger)\tilde{\delta}_g\pi_0(V_1)\pi_0\circ\alpha_0\circ\Theta(V_{g,22}).
	\end{equation}
	Take $W_{g,1},u_{R,1}(g,h)$ and $K^R_{g,1}$ to be the operators belonging to the first choice (with arbitrary phases). Define
	\begin{align}
		W_{g,2}&\defeq\delta_g W_{g,1}\\
		u_{R,2}(g,h)&\defeq \delta_g^R W_{g,1}\delta_h^R W_{g,1}^\dagger u_{R,1}(g,h)(\delta_{gh}^R)^\dagger\\
		K^R_{g,2}&\defeq v^\dagger \delta_g^R v K_{g,1}^R (\delta_g^R)^\dagger
	\end{align}
	then $W_{g,2},u_{R,2}(g,h)$ and $K^R_{g,2}$ are operators belonging to the second choice. Now using lemma \ref{lem:TransformationUnderDelta} concludes the proof.
\end{proof}
\begin{lemma}
	The index is independent of the choice of angle $\theta$.
\end{lemma}
\begin{proof}
	After what we've shown so far this proof is trivial.
\end{proof}
Due to all these considerations we will write the index as $\textrm{index}(\omega)$ from here on onward.
\section{Index is invariant under locally generated automorphisms}\label{sec:IndexInvariantUnderLGA}
Take $H:(t\in\RR, I\subset \ZZ^2)\mapsto H(t,I)\in\AA_I\subset\AA_{\text{loc}}$ to be a one parameter family of interactions such that
\begin{align}
\beta_g(H(t,I))&=H(t,I)&\tau(H(t,I))&=H(t,I')
\end{align}
where $I'$ is just $I$ shifted upwards. For any $I\subset\ZZ^2$ define the interaction $H_I$ as
\begin{equation}
	H_I:(t\in\RR,J\subset\ZZ)\mapsto\left\{\begin{matrix}H(t,J)&\text{if }J\subset I\\0&\text{otherwise.}\end{matrix}\right.
\end{equation}
The following norm will measure the locality of an interaction:
\begin{definition}
For any monotonically decreasing positive function $f:\NN\rightarrow\RR^+$ we define an $f$-norm on the space of interactions by
\begin{equation}
	\norm{H}_f=\sup_{x,y\in\ZZ^2}\frac{1}{F(\textrm{dist}(x_1-x_2))}\sum_{Z\subset\ZZ^2,\:x,y\in Z}\norm{H(Z)}.
\end{equation}
\end{definition}
Following \cite{ogata2021h3gmathbb} we will assume that there exists a $0<\phi<1$ such that $\sup_t \norm{H(t,\cdot)}_{f_\phi}\leq 1$ where $f_\phi$ is defined as
\begin{equation}
	f_\phi:\NN\rightarrow\RR^+:r\mapsto \frac{\exp(-r^\phi)}{(1+r)^4}.
\end{equation}
For any interaction with such a bounded $f_\phi$ norm we will use $\gamma^H_{s;t}$ to denote the automorphism satisfying that for any $a\in\AA$, $\gamma^H_{t;s}(a)$ is the solution to the differential equation
\begin{equation}
	\frac{\d}{\d s}\gamma^H_{t;s}(a)=i\sum_{I\subset \ZZ^2}\gamma^H_{t;s}([H(s,I),a])
\end{equation}
with initial condition $\gamma^H_{t;t}(a)=a$. {\color{red}A reference is needed here that this automorphism indeed exists.} If our interaction satisfies that $\sup_t\sum_{I\subset\ZZ^2}H(I,t)\in\AA$ then we have an identity
\begin{align}
	\gamma^H_{s;t}&=\Ad{u^H_{t;s}}&u^H_{t;s}&\defeq \mathcal{T}\exp(-i\int_t^s\d s'\sum_{I\subset \ZZ^2}H(s',I)).
\end{align}
The goal of this section is now to show that the index we constructed is invariant under such locally generated automorphisms (see theorem \ref{thrm:IndexInvariantUnderLGA}).
\begin{lemma}\label{lem:DefinitionOfGroupMorphism}
	Take $0<\theta<\pi/2$ and $\Theta\in \Aut{(\tau(\AA_{C_\theta})\cup\AA_{C_\theta})^c}$. Take $\Phi^U_{s;t}\in\Aut{\tau(\AA_{C_\theta^c}\cap\AA_{U})}$ and $\Phi^D_{s;t}\in\Aut{\AA_{C_\theta^c}\cap\AA_{D}}$ such that there exists some $a\in\AA$ satisfying that
	\begin{equation}\label{eq:DefinitionOfGroupMorphismHAutEquation}
		\gamma^H_{s;t}\circ\gamma^{H_L}_{t;s}\otimes\gamma^{H_R}_{t;s}=\Ad{a}\circ \Phi^U_{s;t}\otimes\Phi^D_{s;t}.
	\end{equation}
	This can be done using lemma \ref{lem:PropertiesLocallyGeneratedAutomorphisms} part 2. Define the map
	\begin{align}
		\phi_1&:\textrm{IAC}_R(\alpha_0,\theta,\Theta) \rightarrow \textrm{IAC}_R(\alpha_0,\theta,\Theta\circ \Phi^U_{0;1}\otimes\Phi^D_{0;1})\\
		\nonumber
		&:x=\pi_0\circ\alpha_0\circ\Theta(A)y\mapsto \phi_1(x)=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}(A)\pi_0\circ\alpha_0\circ\Theta(a)y\pi_0\circ\alpha_0\circ\Theta(a)^\dagger
	\end{align}
	where $A\in\AA_R$ and $y\in\textrm{Cone}_R(\alpha_0,\theta)$. This map satisfies that
	\begin{enumerate}
		\item  for any $\xi\in\Aut{\AA_{C_\theta}\cap\AA_R}$ such that
		\begin{equation}
			\Ad{y}\circ\pi_0\circ\alpha_0=\pi_0\circ\alpha_0\circ\xi
		\end{equation}
		we get that
		\begin{equation}\label{eq:ConditionDefinitionOfGroupMorphism}
			\Ad{\phi_1(x)}\circ\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}\circ\Ad{A}\circ\xi.
		\end{equation}
		\item it is well defined (independent of the choice of $A$ and $y$).
		\item it is a group homomorphism.
	\end{enumerate}
\end{lemma}
\begin{proof}
	Take $x\in \textrm{IAC}_R(\alpha_0,\theta,\Theta)$ arbitrary. Take $A\in\AA_R$ and $y\in\textrm{Cone}_R(\alpha_0,\theta,\Theta)$ such that
	\begin{equation}
	x=\pi_0\circ\alpha_0\circ\Theta(A)y
	\end{equation}
	where $y$ is such that there exists a $\xi\in\Aut{\AA_{C_\theta}\cap \AA_R}$ such that
	\begin{equation}
	\Ad{y}\circ\pi_0\circ\alpha_0\circ\Theta=\pi_0\circ\alpha_0\circ\Theta\circ\xi.
	\end{equation}
	Take $a$ and $\Phi$ as given in equation \eqref{eq:DefinitionOfGroupMorphismHAutEquation}. We now define
	\begin{equation}
		\phi_1(x)\defeq \pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}(A)\pi_0\circ\alpha_0\circ\Theta(a)y\pi_0\circ\alpha_0\circ\Theta(a)^\dagger.
	\end{equation}
	We now have to prove three things:
	\begin{enumerate}
		\item It satisfies equation \eqref{eq:ConditionDefinitionOfGroupMorphism}.
		\item This map is well defined (independent of our choices).
		\item This is a group homomorphism.
	\end{enumerate}
	To show the first item just observe that
	\begin{align}
		&\Ad{\phi_1(x)}\circ\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}\\
		&=\Ad{\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}(A)\pi_0\circ\alpha_0\circ\Theta(a)y\pi_0\circ\alpha_0\circ\Theta(a)^\dagger}\circ\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}\\
		&=\Ad{\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}(A)}\circ\pi_0\circ\alpha_0\circ\Theta\circ\Ad{a}\circ\xi\circ\Ad{a^\dagger}\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}.
	\end{align}
	Now we insert $\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}\circ\gamma^{H_L}_{0;1}\otimes\gamma^{H_R}_{0;1}\circ\gamma^H_{1;0}=\text{Id}:$
	\begin{align}
		&=\Ad{\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}(A)}\circ\pi_0\circ\alpha_0\circ\Theta\circ(\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}\circ\gamma^{H_L}_{0;1}\otimes\gamma^{H_R}_{0;1}\circ\gamma^H_{1;0})\\
		\nonumber
		&\quad\circ\Ad{a}\circ\xi\circ\Ad{a^\dagger}\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}\circ\Ad{A}\circ\gamma^{H_L}_{0;1}\otimes\gamma^{H_R}_{0;1}\circ\gamma^H_{1;0}\circ\Ad{a}\circ\xi\circ\Ad{a^\dagger}\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}\circ\Ad{A}\circ\Theta_2\circ\xi\circ\Theta_2^{-1}\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}\circ\Ad{A}\circ\xi
	\end{align}
	concluding the proof of the first item. To show the second item notice that since $\pi_0\circ\alpha_0\circ\Theta$ is irreducible the solution (if it exists which we just showed) of equation \eqref{eq:ConditionDefinitionOfGroupMorphism} is unique up to a phase. This means that to show that our map is independent of the choices we only need to show that we can't obtain another phase by picking a different representative. {\color{red}This should be obvious but what argument do I need here?} To then show the last item take $x_1,x_2\in \textrm{IAC}_R(\alpha_0,\Theta)$ arbitrary. Take $A_1,A_2\in\AA_R,y_1,y_2\in \textrm{Cone}_R(\alpha_0,\Theta)$ and $\xi_1,\xi_2\in\Aut{\AA_{C_\theta}\cap\AA_R}$ such that
	\begin{align}
		x_i&=\pi_0\circ\alpha_0\circ\Theta(A_i)y_i&\Ad{y_i}\circ\pi_0\circ\alpha_0\circ\Theta&=\pi_0\circ\alpha_0\circ\Theta\circ\xi_i.
	\end{align}
	On the one hand we have
	\begin{align}
		x_1x_2&=\pi_0\circ\alpha_0\circ\Theta(A_1)y_1\pi_0\circ\alpha_0\circ\Theta(A_2)y_2\\
		&=\pi_0\circ\alpha_0\circ\Theta(A_1)y_1\pi_0\circ\alpha_0\circ\Theta(A_2)y_1^{\dagger}y_1y_2\\
		&=\pi_0\circ\alpha_0\circ\Theta(A_1\xi_1(A_2))y_1y_2
	\end{align}
	giving
	\begin{equation}
		\phi_1(x_1x_2)=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}(A_1\xi_1(A_2))\tilde{a}y_1y_2\tilde{a}^\dagger.
	\end{equation}
	where $\tilde{a}=\pi_0\circ\alpha_0\circ\Theta(a)$. Filling this in gives
	\begin{align}
		&\phi_1(x_1x_2)\phi_1(x_2)^\dagger\phi_1(x_1)^\dagger\\
		\label{eq:HomeomorphismCondition}
		&=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}(A_1\xi_1(A_2))\tilde{a}y_1\stkout{y_2}\tilde{a}^\dagger \stkout{\tilde{a}y_2\tilde{a}^\dagger}\\
		\nonumber
		&\quad\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}(A_2)\tilde{a}y_1\tilde{a}^\dagger \pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}(A_1).
	\end{align}
	Writing out a part of this gives:
	\begin{align}
		&\Ad{\tilde{a}y_1\tilde{a}^\dagger}\circ\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}(A_2)\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\Ad{a}\circ\xi_1\circ\Ad{a^\dagger}\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}(A_2).
	\end{align}
	Using equation \eqref{eq:DefinitionOfGroupMorphismHAutEquation} now yields:
	\begin{align}
		&=\pi_0\circ\alpha_0\circ\Theta\circ\Ad{a}\circ\xi_1\circ\Phi(A_2)\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\Ad{a}\circ\Phi\circ\xi_1(A_2)\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}\circ\xi_1(A_2).
	\end{align}
	Inserting this in equation \eqref{eq:HomeomorphismCondition} shows that
	\begin{equation}
		\phi_1(x_1x_2)\phi_1(x_1)^\dagger\phi_1(x_2)^\dagger=\mathbbm{1}
	\end{equation}
	concluding the proof.
\end{proof}
\begin{lemma}\label{lem:DefinitionOfWgMap}
	There exists a map
	\begin{equation}
		\phi_2:\{W_g|g\in G\}\rightarrow \UU(\HH)
	\end{equation}
	satisfying
	\begin{equation}\label{eq:lemDefinitionOfWgMapCondition}
		\Ad{\phi_2(W_g)}\circ\pi_0=\pi_0\circ \alpha_0\circ\Theta\circ\gamma^{H}_{0;1}\circ(\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0})\circ\eta_g\circ\beta_g^U\circ(\gamma^{H_L}_{0;1}\otimes\gamma^{H_R}_{0;1})\circ\gamma^{H}_{1;0}\circ\Theta^{-1}\circ\alpha_0^{-1}.
	\end{equation}
	It is unique up to a $G$-dependent phase.
\end{lemma}
\begin{proof}
	Take the $a\in\UU(\AA)$, $\Phi^U_{0;1}$ and $\Phi^D_{0;1}$ defined such that
	\begin{equation}\label{eq:proofDefinitionOfWgMapVAut}
		\gamma^H_{0;1}\otimes\gamma^{H_L}_{1;0}\otimes\gamma^{H_L}_{1;0}=\Ad{a}\circ\Phi^U_{0;1}\otimes\Phi^D_{0;1}.
	\end{equation}
	This exists because of lemma \ref{lem:PropertiesLocallyGeneratedAutomorphisms} part 2. We will define
	\begin{equation}
		\phi_2(W_g)\defeq \pi_0\circ\alpha_0\circ\Theta(a)W_g\pi_0\circ\alpha_0\circ\Theta(a)^\dagger.
	\end{equation}
	To show that this indeed satisfies equation \eqref{eq:lemDefinitionOfWgMapCondition} observe that using equation \eqref{eq:proofDefinitionOfWgMapVAut} we obtain:
	\begin{align}
		\Ad{\phi_2(W_g)}\circ\pi_0&=\pi_0\circ \alpha_0\circ\Theta\circ\Ad{a}\circ\eta_g\circ\beta_g^U\circ\Ad{a^{\dagger}}\circ\Theta^{-1}\circ\alpha_0^{-1}\\
		&=\pi_0\circ \alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_L}_{1;0}\circ\Phi_{0;1}^{-1}\circ\eta_g\circ\beta_g^U\circ\Phi_{0;1}\circ\gamma^{H_L}_{0;1}\otimes\gamma^{H_R}_{0;1}\circ\gamma^H_{1;0}\circ\Theta^{-1}\circ\alpha_0^{-1}.
	\end{align}
	Since $\Phi$ commutes with both the $\eta_g$ and with the $\beta_g^U$ the result follows.
\end{proof}
\begin{lemma}\label{lem:phi1phi2matchingCondition}
	The $\phi_1$ and $\phi_2$ defined previously satisfy that for any $x\in\textrm{IAC}_R(\alpha_0,\theta,\Theta)$ we have that
	\begin{align}
		\phi_1(\Ad{W_g}(x))&=\Ad{\phi_2(W_g)}(\phi_1(x))\\
		\phi_1(\Ad{v}(x))&=\Ad{v}(\phi_1(x)).
	\end{align}
\end{lemma}
\begin{proof}
	Take $x\in \textrm{IAC}_R(\alpha_0,\theta,\Theta)$ arbitrary. Take $A\in\AA_R$ and $y\in\textrm{IAC}_R(\alpha_0,\theta,\Theta)$ such that
	\begin{equation}
		x=\pi_0\circ\alpha_0\circ\Theta(A)y
	\end{equation}
	where $y$ is such that there exists a $\xi\in\Aut{\AA_{C_\theta}\cap \AA_R}$ such that
	\begin{equation}
		\Ad{y}\circ\pi_0\circ\alpha_0\circ\Theta=\pi_0\circ\alpha_0\circ\Theta\circ\xi.
	\end{equation}
	Take $a$ and $\Phi$ as given in equation \eqref{eq:DefinitionOfGroupMorphismHAutEquation} and take $\tilde{a}=\pi_0\circ\alpha_0\circ\Theta(a)$. We now get
	\begin{align}
		W_g x W_g^\dagger&=\Ad{W_g}\circ\pi_0\circ\alpha_0\circ\Theta(A) W_gyW_g^\dagger\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\eta_g\circ\beta_g^U(A) W_gyW_g^\dagger.
	\end{align}
	Since $W_g uW_g^\dagger$ satisfies that there exists an $\tilde{\xi}\in\Aut{\AA_{C_\theta}\cap \AA_R}$ such that
	\begin{equation}
		\Ad{W_gyW_g^\dagger}\circ \pi_0\circ\alpha_0\circ\Theta=\pi_0\circ\alpha_0\circ\Theta\circ\tilde\xi
	\end{equation}
	(one can just take $\tilde\xi=\eta_g\circ\beta_g^U\circ\xi\circ\beta_{g^{-1}}^U\circ\eta_g^{-1}$) we get that
	\begin{equation}
		\phi_1(W_gxW_g^{\dagger})=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^{H}_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}\circ\eta_g\circ\beta_g^U(A)\tilde{a}W_gyW_g^\dagger\tilde{a}^\dagger.
	\end{equation}
	Filling this in gives
	\begin{align}
		&\phi_1(W_gxW_g^\dagger)\phi_2(W_g)^\dagger\phi_1(x)^\dagger\phi_2(W_g)^\dagger\\
		\label{eq:phi1phi2matchingConditionEquation}
		&=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^{H}_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}\circ\eta_g\circ\beta_g^U(A)\tilde{a}W_g\stkout{yW_g^\dagger\tilde{a}^\dagger}\\
		\nonumber
		&\quad\stkout{\tilde{a}W_g\tilde{a}^\dagger\tilde{a}y}\tilde{a}^\dagger\pi_0\circ\alpha_0\circ\Theta\circ\gamma^{H}_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}(A)^\dagger\tilde{a}W_g^\dagger\tilde{a}^\dagger.
	\end{align}
	To prove that this is the identity observe that
	\begin{align}
		&\Ad{\tilde{a}W_g\tilde{a}^\dagger}\circ\pi_0\circ\alpha_0\circ\Theta\circ \gamma^{H}_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}(A)\\
		&=\Ad{\tilde{a}W_g}\circ\pi_0\circ\alpha_0\circ\Theta\circ\Ad{a^\dagger}\circ \gamma^{H}_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}(A)\\
		&=\Ad{\tilde{a}W_g}\circ\pi_0\circ\alpha_0\circ\Theta\circ\Phi(A)\\
		&=\Ad{\tilde{a}}\circ\pi_0\circ\alpha_0\circ\Theta\circ\eta_g\circ\beta_g^U\circ\Phi(A)\\
		&=\Ad{\tilde{a}}\circ\pi_0\circ\alpha_0\circ\Theta\circ\Phi\circ\eta_g\circ\beta_g^U(A)\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\Ad{a}\circ\Phi\circ\eta_g\circ\beta_g^U(A)\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ \gamma^{H}_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0} \circ\eta_g\circ\beta_g^U(A).
	\end{align}
	Filling this in equation \eqref{eq:phi1phi2matchingConditionEquation} concludes the proof.
\end{proof}
\begin{theorem}\label{thrm:IndexInvariantUnderLGA}
	$\textrm{index}(\omega)=\textrm{index}(\omega\circ\gamma^H_{0;1})$
\end{theorem}
\begin{proof}
	Take $\alpha\in\QAut{\AA}$ such that $\omega=\omega_0\circ\alpha$ for some product state $\omega_0$. Take $0<\theta_1<\theta_2<\theta_3<\pi/2$ arbitrary. Take $\alpha_L\in\Aut{\AA_L},\alpha_R\in\Aut{\AA_R},V_1\in\UU(\AA)$ and $\Theta\in\Aut{\left(\AA_{C_{\theta_3}} \cup \tau(\AA_{C_{\theta_3}})\right)^c}$ such that
	\begin{equation}
		\alpha=\Ad{V_1}\circ\alpha_L\otimes\alpha_R\circ\Theta.
	\end{equation}
	Take $\tilde{\beta}_{g,1}$ such that $\omega\circ\tilde{\beta}_{g,1}=\omega$ and such that there exists some $V_{2,g}\in\UU(\AA)$ and some $\eta_g^{L/R}\in\Aut{\AA_{C_{\theta_1}}\cap\AA_{L/R}}$ satisfying
	\begin{equation}
		\tilde{\beta}_{g,1}=\Ad{V_{2,g}}\circ\eta_{g}^L\otimes\eta_{g}^R\circ\beta_g^U.
	\end{equation}
	Take $W_g,u_{L/R}(g,h),v$ and $K_g^{L/R}$ operators belonging to these automorphisms (see lemmas \ref{lem:Definition_W_And_u} and \ref{lem:Definition_K}). Clearly $\alpha\circ\gamma^H_{0;1}$ satisfies $\omega\circ\gamma^{H}_{0;1}=\omega_0\circ\alpha\circ\gamma^{H}_{0;1}$. We also have that $\alpha\circ\gamma\in\QAut{\AA}$. To show this notice that
	\begin{align}
		\alpha\circ\gamma&=\Ad{V_1}\circ(\alpha_L\circ\gamma^{H_L}_{0;1}\otimes\alpha_R\circ\gamma^{H_R}_{0;1})\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}\circ\Theta\circ\gamma^H_{0;1}\\
		&=\Ad{V_1}\circ(\alpha_L\circ\gamma^{H_L}_{0;1}\otimes\alpha_R\circ\gamma^{H_R}_{0;1})\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}\circ\gamma^{H}_{0;1}\circ\gamma^{H}_{1;0}\circ\Theta\circ\gamma^H_{0;1}.
	\end{align}
	Because of lemma \ref{lem:TwoAngleLemmaPart1} and lemma \ref{lem:PropertiesLocallyGeneratedAutomorphisms} part 2 there exists a $\tilde{\Theta}\in\Aut{\AA_{C_{\theta_2}}\cup\tau(\AA_{C_{\theta_2}})}$ and some $\tilde V_1,A_1\in\UU(\AA)$ such that
	\begin{align}
		\alpha\circ\gamma^H_{0;1}&=\Ad{\tilde V_1}\circ(\alpha_L\circ\gamma^{H_L}_{0;1}\otimes\alpha_R\circ\gamma^{H_R}_{0;1})\circ\tilde\Theta\\
		(\alpha_L\circ\gamma^{H_L}_{0;1}\otimes\alpha_R\circ\gamma^{H_R}_{0;1})\circ\tilde\Theta&=\Ad{A_1}\circ \alpha_L\otimes\alpha_R\circ\Theta\circ\gamma^{H}_{0;1}.
	\end{align}
	If we now define the automorphism $\tilde{\beta}_{g,2}=\gamma^{H}_{1;0}\tilde\beta_{g,1}\gamma^{H}_{0;1}$ then this indeed satisfies that $\omega\circ\gamma^{H}_{0;1}\circ\tilde{\beta}_{g,2}=\omega\circ\gamma^{H}_{0;1}$. Define $\tilde\eta_g^\sigma$ through lemma \ref{lem:TwoAngleLemmaPart2}. Because of lemma \ref{lem:PropertiesLocallyGeneratedAutomorphisms} part 4 there exists a $\tilde V_{2,g}\in\UU(\AA),A_{2,g}^{\sigma}\in\UU(\AA_\sigma)$ such that
	\begin{align}
		\label{eq:IndexInvariantUnderLGAEtaTildeDefiniton1}
		\gamma^{H}_{1;0}\tilde{\beta}_g\gamma^{H}_{0;1}&=\Ad{\tilde V_{2,g}}\circ\tilde{\eta}_g^L\otimes\tilde{\eta}_g^R\circ\beta_g^U\\
		\label{eq:IndexInvariantUnderLGAEtaTildeDefiniton2}
		\tilde{\eta}_g^\sigma&=\Ad{A_{2,g}^\sigma}\circ\gamma^{H_L}_{1;0}\circ\eta_g^\sigma\circ\beta_g^{\sigma U}\circ\gamma^{H_R}_{0;1}\circ(\beta_g^{\sigma U})^{-1}.
	\end{align}
	Take $\Phi$ like in equation \eqref{eq:DefinitionOfGroupMorphismHAutEquation} and define
	\begin{equation}
		\phi_1:\textrm{IAC}_R(\alpha_0,\Theta) \rightarrow \textrm{IAC}_R(\alpha_0,\Theta\circ \Phi)
	\end{equation}
	the group homomorphism defined from lemma \ref{lem:DefinitionOfGroupMorphism}. Take similarly
	\begin{equation}
		\phi_2:\{W_g|g\in G\}\rightarrow \UU(\HH)
	\end{equation}
	the map defined in \ref{lem:DefinitionOfWgMap} with arbitrary phase. The following operators now belong to $\omega\circ\gamma^{H}_{0;1}:$
	\begin{align}
		\label{eq:IndexInvariantUnderLGANewOperator1}
		\tilde{v}&=\pi_0(A_1)v\pi_0(A_1)^\dagger\\
		\label{eq:IndexInvariantUnderLGANewOperator2}
		\tilde{W}_g&=\pi_0(A_1)\phi_1(\delta^L_g\otimes\delta^R_g)\phi_2( W_g)\pi_0(A_1^\dagger)\\
		\label{eq:IndexInvariantUnderLGANewOperator3}
		\tilde u_\sigma(g,h)&=\pi_0(A_1) \phi_1\left(\delta^\sigma_g W_g\delta^\sigma_h W_g^\dagger u_\sigma(g,h)(\delta^\sigma_{gh})^\dagger\right)\pi_0(A_1)^\dagger\\
		\label{eq:IndexInvariantUnderLGANewOperator4}
		\tilde{K}_g^L\otimes \tilde{K}_g^R&=\tilde{v}^\dagger \tilde{W}_g\tilde{v}\tilde{W}_g^\dagger
	\end{align}
	where $\delta^\sigma_g=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^{H_\sigma}_{0;1}(A^\sigma_{2,g}).$ The fact that the index is invariant under $\Ad{\pi_0(A_1)}$ and under $\phi(\cdot)$ is just due to the fact that both transformations are homomorphisms. To show that it is invariant under the transformation with de $\delta^\sigma_g$ we invoke lemma \ref{lem:TransformationUnderDelta}. All that is left to show is that operators \eqref{eq:IndexInvariantUnderLGANewOperator1} through \eqref{eq:IndexInvariantUnderLGANewOperator4} are indeed operators belonging to $\omega\circ\gamma^{H}_{0;1}$. To do this we first state that a small calculation shows that $\forall x\in\UU(\HH_0)$ satisfying that $\exists\xi\in\Aut{\AA}$ such that
	\begin{equation}
		\Ad{x}\circ\pi_0\circ\alpha_0\circ\Theta=\pi_0\circ\alpha_0\circ\Theta\circ\xi
	\end{equation}
	we get that
	\begin{equation}\label{eq:IndexInvariantUnderLGA_A1_Transformation}
		\Ad{\pi_0(A_1)x\pi_0(A_1^\dagger)}\circ\pi_0\circ\alpha_0\circ\gamma^{H_L}_{0;1}\otimes\gamma^{H_R}_{0;1}\circ\tilde{\Theta}=\pi_0\circ\alpha_0\circ\gamma^{H_L}_{0;1}\otimes\gamma^{H_R}_{0;1}\circ\tilde{\Theta}\circ\gamma^H_{1;0}\circ\xi\circ\gamma^H_{0;1}.
	\end{equation}
	This already proves that
	\begin{align}
		\Ad{\pi_0(A_1)v\pi_0(A_1^\dagger)}\circ\pi_0\circ\alpha_0\circ\gamma^{H_L}_{0;1}\otimes\gamma^{H_R}_{0;1}\circ\tilde{\Theta}&=\pi_0\circ\alpha_0\circ\gamma^{H_L}_{0;1}\otimes\gamma^{H_R}_{0;1}\circ\tilde{\Theta}\circ\gamma^H_{1;0}\circ\tau\circ\gamma^H_{0;1}\\
		&=\pi_0\circ\alpha_0\circ\gamma^{H_L}_{0;1}\otimes\gamma^{H_R}_{0;1}\circ\tilde{\Theta}\circ\tau.
	\end{align}
	To show the second one we get that
	\begin{align}
		&\Ad{\phi_1(\delta_g)\phi_2(W_g)}\circ\pi_0\circ\alpha_0\circ\Theta\\
		&=\Ad{\phi_1(\delta_g)}\circ\pi_0\circ\alpha_0\circ\Theta\gamma^{H}_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}\circ\eta_g\circ\beta_g^U\circ\gamma^{H_L}_{0;1}\otimes\gamma^{H_R}_{0;1}\circ\gamma^H_{1;0}\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^{H}_{0;1}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}\circ\Ad{\gamma^{H_L}_{0;1}(A_{2,g}^L)\otimes\gamma^{H_R}_{0;1}(A_{2,g}^R)}\circ\eta_g\circ\beta_g^U\circ\gamma^{H_L}_{0;1}\otimes\gamma^{H_R}_{0;1}\circ\gamma^H_{1;0}\\
		&=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^{H}_{0;1}\circ\Ad{A_{2,g}^L\otimes A_{2,g}^R}\circ\gamma^{H_L}_{1;0}\otimes\gamma^{H_R}_{1;0}\circ\eta_g\circ\beta_g^U\circ\gamma^{H_L}_{0;1}\otimes\gamma^{H_R}_{0;1}\circ\gamma^H_{1;0}.
	\end{align}
	Using equation \eqref{eq:IndexInvariantUnderLGAEtaTildeDefiniton2} on this we obtain
	\begin{equation}
		=\pi_0\circ\alpha_0\circ\Theta\circ\gamma^H_{0;1}\circ\tilde{\eta}_g\circ\beta_g^U\circ\gamma^H_{1;0}.
	\end{equation}
	Inserting this in equation \eqref{eq:IndexInvariantUnderLGA_A1_Transformation} with $x=\phi_1(\delta_g)\phi_2(W_g)$ and $\xi=$ now proves the fact that $\tilde{W}_g$ is an operator belonging to $\omega\circ\gamma^H_{0;1}$. {\color{red}I need to do the same for $\tilde u_R(g,h)$.}
\end{proof}
\appendix
\section{Properties of locally generated automorphisms:}
 Take $H$ and $\gamma$ as defined in section \ref{sec:IndexInvariantUnderLGA}. We will now show some properties of this locally generated automorphism $\gamma$. In this section we will heavily rely on the framework and theorems of \cite{ogata2021h3gmathbb}. We will use the notation
 \begin{align}
 	C_{[0,\theta]}&\defeq C_{\theta}&C_{]\theta_1,\theta_2]}&\defeq C_{\theta_2}/C_{\theta_1}&C_{]\theta,\pi/2]}&\defeq \ZZ^2/C_{\theta}
 \end{align}
 where $0<\theta<\pi/2$ and $0<\theta_1<\theta_2<\pi_2$. In analogy with section 2.1 from \cite{ogata2021h3gmathbb} we will define some classes of automorphisms:
 \begin{definition}
 	Take $\alpha\in\Aut{\AA}$. We say that $\alpha\in\textrm{SQAut}(\AA)$ if and only if for any $0<\theta_{0.8}<\theta_{1}<\theta_{1.2}<\theta_{1.8}<\theta_{2}<\theta_{2.2}<\theta_{2.8}<\theta_3<\theta_{3.2}<\pi/2$ there exist $a\in\AA$, $\alpha_{[0,\theta_1], \sigma}\in\Aut{\AA_{C_{[0,\theta_1]}\cap\sigma}},\:\alpha_{]\theta_1,\theta_2],\sigma,\rho}\in\Aut{\AA_{C_{]\theta_1,\theta_2]}\cap\rho\cap\sigma}},\:\alpha_{]\theta_2,\theta_3],\sigma,\rho}\in\Aut{\AA_{(C_{]\theta_2,\theta_3]}\cap\rho\cap\sigma)\cup\tau^{\rho}(C_{]\theta_2,\theta_3]}\cap\rho\cap\sigma)}},\alpha_{]\theta_3,\pi/2],\rho}\in\Aut{\tau^\rho(\AA_{C_{[\theta_3,\pi/2]}\cap\rho})},\:\alpha_{]\theta_{0.8},\theta_{1.2}],\sigma,\rho}\in\Aut{\AA_{C_{]\theta_{0.8},\theta_{1.2}]}\cap\rho\cap\sigma}},\:\alpha_{]\theta_{1.8},\theta_{2.2}],\sigma,\rho}\in\Aut{\AA_{C_{]\theta_{1.8},\theta_{2.2}]}\cap\rho\cap\sigma}}$ and  $\alpha_{]\theta_{2.8},\theta_{3.2}],\sigma,\rho}\in\Aut{\tau^{\rho}(\AA_{C_{]\theta_{2.8},\theta_{3.2}]}\cap\rho\cap\sigma})}$ for any $\rho\in\{U,D\}$ and $\sigma\in\{L,R\}$ (here $\tau^U=\tau$ and $\tau^D=\tau^{-1}$) such that
 	\begin{equation}
 		\alpha=\Ad{a}\circ \bigotimes_{\sigma}\alpha_{[0,\theta_1],\sigma}\circ\bigotimes_{\sigma,\rho}\alpha_{]\theta_1,\theta_2],\sigma,\rho}\circ\bigotimes_{\rho}\alpha_{[\theta_3,\pi/2]}\circ\bigotimes_{\rho,\sigma}\left(\alpha_{]\theta_{0.8},\theta_{1.2}],\rho,\sigma}\otimes\alpha_{]\theta_{1.8},\theta_{2.2}],\rho,\sigma}\otimes\alpha_{]\theta_{2.8},\theta_{3.2}],\rho,\sigma} \right).
 	\end{equation}
 	If additionally everything (except $a$) commutes with $\beta_g^U$ we say that $\alpha\in \textrm{GSQAut}(\AA)$.
 \end{definition}
 As a remark, notice that this definition is not exactly identical to de definition given in \cite{ogata2021h3gmathbb} due to the translation operators.
 \begin{definition}
 	Take $\alpha\in\Aut{\AA}$. We say that $\alpha\in\textrm{HAut}(\AA)$ if and only if for any $0<\theta<\pi/2$ there exists an $a\in\AA$ and some $\alpha_\sigma\in\Aut{\AA_{C_\theta}\cap\AA_\sigma}$ for each $\sigma\in\{L,R\}$ such that
 	\begin{equation}
 		\alpha=\Ad{a}\circ\alpha_L\otimes\alpha_R.
 	\end{equation}
 \end{definition}
We will need one additional class of automorphisms:
\begin{definition}
	Take $\alpha\in\Aut{\AA}$. We say that $\alpha\in\textrm{VAut}(\AA)$ if and only if there exists some $a\in\AA$, $\alpha_U\in\Aut{\tau(\AA_{C_\theta^c}\cap\AA_{U})}$ and an $\alpha_D\in\Aut{\tau^{-1}(\AA_{C_\theta^c}\cap\AA_{D})}$ such that
	\begin{equation}
		\alpha=\Ad{a}\circ\alpha_U\otimes\alpha_D.
	\end{equation}
	If furthermore $\alpha_U\circ\beta_g^U=\beta_g^U\circ\alpha_U$ we say that $\alpha\in\textrm{GVAut}(\AA)$.
\end{definition}
Now we will state some properties of locally generated automorphisms:
\begin{lemma}\label{lem:PropertiesLocallyGeneratedAutomorphisms}
	Take $H$ a $G-$invariant interaction such that there exists a $0<\phi<1$ satisfying that $\norm{H}_{f_\phi}\leq 1$. The following statements now hold (for any $s,t\in\RR$):
	\begin{enumerate}
		\item $\gamma^H_{s;t}\circ\gamma^{H_D}_{t;s}\otimes\gamma^{H_U}_{t;s}\in\textrm{HAut}(\AA)$.
		\item $\gamma^H_{s;t}\circ\gamma^{H_L}_{t;s}\otimes\gamma^{H_R}_{t;s}\in\textrm{GVAut}(\AA)$.
		\item $\gamma^{H_U}_{s;t}\otimes\gamma^{H_D}_{s;t}\in\textrm{GSQAut}(\AA)$.
		\item $\gamma^{H}_{t;s}\circ\beta_g^U\circ\gamma^{H}_{s;t}\circ(\beta_g^U)^{-1}\in\textrm{HAut}(\AA)$.
	\end{enumerate}
\end{lemma}
\begin{proof}
	Part 1 is done in Proposition 5.5 in \cite{ogata2021h3gmathbb} and part 4 follows trivially from Part 1. Except for the translation operators in my definition of the $\textrm{SQAut}(\AA)$, part 3 follows from Theorem 5.2 in \cite{ogata2021h3gmathbb}. To show part 3 we therefore have to show that Theorem 5.2 in \cite{ogata2021h3gmathbb} still holds if we replace $\mathcal{C}_0$ and $\mathcal{C}_1$ in the proof by
	\begin{align}
		\mathcal{C}_0&\defeq \left\{C_{[0,\theta_1],\sigma},C_{]\theta_1,\theta_2],\sigma,\rho},C_{]\theta_2,\theta_3],\sigma,\rho}\cup\tau^{\rho}(C_{]\theta_2,\theta_3],\sigma,\rho}),\tau^\rho(C_{]\theta_3,\pi/2],\rho})|\sigma=\{L,R\},\rho=\{U,D\}\right\}\\
		\mathcal{C}_1&\defeq\{C_{[\theta_{0.8},\theta_{1.2}]\cap\sigma\cap\tau},C_{[\theta_{1.8},\theta_{2.2}]\cap\sigma\cap\tau},\tau^\rho(C_{[\theta_{2.8},\theta_{3.2}]\cap\sigma\cap\rho})|\sigma=\{L,R\},\rho=\{U,D\}\}.
	\end{align}
	Take the $\Psi$ from this proof to be our $H$ and take $\Psi^{(1)}$ to be $H-H_{\mathcal{C}_0}$ with our new definition of $\mathcal{C}_0$. Now define $\Xi^{(s)}(Z,t)$ completely analogous. We now want so show that for every $t$, $\sum_{Z\subset\ZZ^2}(\Xi^{(s)}(Z,t)-\Xi^{(s)}|_{\mathcal{C}_1}(Z,t))$ is bounded. Following the arguments in equation (5.22) to (5.24) in \cite{ogata2021h3gmathbb} we still get that
	\begin{equation}
		\sum_{\substack{Z\subset\ZZ^2,\\\nexists C\in\mathcal{C}_1:Z\subset C}}\sup_{t\in[0,1]}\norm{\Xi^{(1)}(Z,t)}\leq \frac{8}{C_F}(e^{2I_F(\Psi)}-1)\sum_{\substack{C_1,C_2\in\mathcal{C}_0,\\ C_1\neq C_2}}M(C_1,C_2)
	\end{equation}
	where
	\begin{equation}
		M(C_1,C_2)\defeq \sum_{m\geq 0}\sum_{\substack{X:\\\forall C\in\mathcal{C}_1,X\cap((C^c)(m))\neq\emptyset,\\C\cap C_1\neq\emptyset,X\cap C_2\neq\emptyset}}\left(\sup_{t\in[0,1]}(\norm{\Psi^{(1)}(X;t)})\abs{X}G_F(m)\right)
	\end{equation}
	is now defined using the new $\mathcal{C}_1$. To bound these $M(C_1,C_2)$ we will (just like in \cite{ogata2021h3gmathbb}) differentiate between two cases. That is, the case where $C_1$ and $C_1$ are adjacent\footnote{We say that $C_1$ and $C_2$ are adjacent if and only if $\#(C_1(1)\cap C_2(1))=\infty$.} and the case where they are. We begin with the latter. In this case we still have in complete analogy with the proof in \cite{ogata2021h3gmathbb} that
	\begin{equation}
		M(C_1,C_2)\leq b_0(C_1,C_2) \defeq \norm{\Psi_1}_F\sum_{\substack{x\in C_1\\y\in C_2}}F(d(x,y))\sum_{m=0}^\infty G_F(m)<\infty.
	\end{equation}
	What is now left to show is the case where $C_1$ and $C_2$ are adjacent. Take $\tilde{C}\in\mathcal{C}_1$ such that $C_1\cap\tilde{C}\neq\emptyset$ and $C_2\cap\tilde{C}\neq\emptyset$. Take $L_1=\partial\tilde{C}/C_2$\footnote{Here $\partial \tilde{C}$ means the boundary of $\tilde C$.} and $L_2=\partial\tilde{C}/C_1$. By following the same reasoning that led to equation (5.36) in \cite{ogata2021h3gmathbb} we get that
	\begin{align}
		M(C_1,C_2)\leq b_0(C_1,C_2/\tilde{C})+b_0(C_1/\tilde{C},C_2)+b_0(\tilde{C}\cap C_2,(C_1\cup C_2)^c)+b_1(C_1\cap\tilde{C},C_2\cap\tilde{C},L_1,L_2)
	\end{align}
	where
	\begin{equation}
		b_1(C_1\cap\tilde{C},C_2\cap\tilde{C},L_1,L_2)\defeq \norm{\Psi_1}_F\sum_{m=0}^{\infty}G_F(m)\left(\sum_{\substack{x\in C_2\cap\tilde{C},\\y\in L_1(m)}}+\sum_{\substack{x\in C_1\cap\tilde{C},\\y\in L_2(m)}}\right)F(d(x,y))<\infty.
	\end{equation}
	\footnote{Here $\Psi_1$ is defined through $\Psi_1(X)=\abs{X}^1 \Psi(X)$.} Since the remainder of the proof can remain unchanged from \cite{ogata2021h3gmathbb}, this concludes the proof of item 3. We now only need to comment on item 2. We must show that
	\begin{equation}
		(\gamma^H_{s;t}\circ\gamma^{H_L}_{t;s}\otimes\gamma^{H_R}_{t;s})^{-1}=\gamma^{H_L}_{s;t}\otimes\gamma^{H_R}_{s;t}\circ\gamma^H_{t;s}\in\textrm{GVAut}(\AA).
	\end{equation}
	The proof of this starts analogously to the proof of item 1 and 3. We have for any $A\in\AA$ that
	\begin{align}
		&\frac{\d}{\d t}\gamma^{H_L}_{s;t}\otimes\gamma^{H_R}_{s;t}\circ\gamma^H_{t;s}(A)\\
		&=i\sum_{I\subset\ZZ^2}\gamma^{H_L}_{s;t}\otimes\gamma^{H_R}_{s;t}([\partial H(t,I),\gamma^H_{t;s}(A)])
	\end{align}
	where $\partial H(t,I)=H(t,I)-H_D(t,I)-H_U(t,I)$. Working this out further gives
	\begin{align}
		&=i\sum_{I\subset\ZZ^2}\gamma^{H_L}_{s;t}\otimes\gamma^{H_R}_{s;t}\circ\gamma^H_{t;s}\left([\gamma^H_{s;t}(\partial H(t,I)),A]\right).
	\end{align}
	Clearly $I\mapsto \gamma^H_{s;t}(\partial H(t,I))$ is not strictly speaking an interaction. However there is a $G$-invariant interaction with bounded $f_\phi$ norm that leads to the same locally generated automorphism. This can be defined by
	\begin{equation}
		\Xi^{(s)}(t,Z)\defeq \sum_{m\geq 0}\sum_{\substack{X\subset Z,\\X(m)=Z}}\Delta_{X(m)}\left(\gamma^H_{s;t}(\partial H(t,I))\right)
	\end{equation}
	where for any $X\subset\ZZ^2$ we mean by $X(m)\subset\ZZ^2$ the set of points that are at most at distance $m$ from some point in $X$ and we mean by
	\begin{equation}
		\Delta_{X(m)}\defeq\left\{\begin{matrix}
			\Pi_X&\text{if }m=0\\
			\Pi_{X(m)}-\Pi_{X(m-1)}&\text{otherwise.}
		\end{matrix}\right.
	\end{equation}
	Here the $\Pi_X$ is defined as the operator that traces away all the degrees of freedom that are not situated in the region $X$. This interaction is clearly still $G-$invariant and we do have
	\begin{align}
		&\frac{\d}{\d t}\gamma^{H_L}_{s;t}\otimes\gamma^{H_R}_{s;t}\circ\gamma^H_{t;s}(A)\\
		&=i\sum_{I\subset\ZZ^2}\gamma^{H_L}_{s;t}\otimes\gamma^{H_R}_{s;t}\circ\gamma^H_{t;s}\left([\Xi^{(s)}(t,I),A]\right)
	\end{align}
	and hence the interaction does generate our locally generated automorphism.
\end{proof}
From these four statements we can prove the following results:
\begin{lemma}\label{lem:TwoAngleLemmaPart1}
	Take $\theta_1$ and $\theta_2$ such that $0<\theta_1<\theta_2<\pi/2$ then for all $\Theta\in\Aut{\AA_{W(C_{\theta_2})^c}}$ and $s,t\in\RR$ there exists an $a_1\in\UU(\AA)$ and a $\tilde{\Theta}\in \Aut{\AA_{W(C_{\theta_1})^c}}$ such that
		\begin{equation}\label{eq:TwoAngleLemmaPart1Equation1}
			\gamma^{H}_{t;s}\circ\Theta\circ\gamma^{H}_{s;t}=\Ad{a_1}\circ\tilde{\Theta}.
		\end{equation}
\end{lemma}
\begin{proof}
	We have that
	\begin{equation}
		\gamma^{H}_{t;s}\circ\Theta\circ\gamma^{H}_{s;t}=\gamma^{H_D}_{t;s}\otimes\gamma^{H_U}_{t;s}\circ\gamma^{H_D}_{s;t}\otimes\gamma^{H_U}_{s;t}\circ\gamma^{H}_{t;s}\circ\Theta\circ\gamma^{H}_{s;t}\circ\gamma^{H_D}_{t;s}\otimes\gamma^{H_U}_{t;s}\circ\gamma^{H_D}_{s;t}\otimes\gamma^{H_U}_{s;t}.
	\end{equation}
	Using that $\gamma^{H}_{s;t}\circ\gamma^{H_D}_{t;s}\otimes\gamma^{H_U}_{t;s}\in\textrm{HAut}(\AA)$ we get that there exists some $a\in\AA$ and $\eta\in\Aut{\AA_{C_\theta}}$ such that
	\begin{align}
		\gamma^{H}_{t;s}\circ\Theta\circ\gamma^{H}_{s;t}&=\Ad{a}\circ \gamma^{H_D}_{t;s}\otimes\gamma^{H_U}_{t;s}\circ\eta_{s;t}^{-1}\circ\Theta\circ\eta_{s;t}\circ\gamma^{H_D}_{s;t}\otimes\gamma^{H_U}_{s;t}\\
		&=\Ad{a}\circ \gamma^{H_D}_{t;s}\otimes\gamma^{H_U}_{t;s}\circ\Theta\circ\gamma^{H_D}_{s;t}\otimes\gamma^{H_U}_{s;t}.
	\end{align}
	Since by \ref{lem:PropertiesLocallyGeneratedAutomorphisms} part 3 $\gamma^{H_D}_{s;t}\otimes\gamma^{H_U}_{s;t}\in\textrm{GSQAut}(\AA)$ the result follows. {\color{red}Do I have to explain this further?}
\end{proof}
\begin{lemma}\label{lem:TwoAngleLemmaPart2}
	Take $\theta_1$ and $\theta_2$ such that $0<\theta_1<\theta_2<\pi/2$. Then for all $\eta_{g}^{\sigma}\in\Aut{\AA_{C_{\theta_1}}\cap\AA_{\sigma}}$ (where $\sigma\in\{L,R\}$ and $g\in G$) and $s,t\in\RR$ there exist $a_2,\in\UU(\AA),a_3\in\UU(\AA_R)$ and some $\tilde{\eta}_{\sigma}^g\in \Aut{\AA_{C_{\theta_2}}\cap\AA_{\sigma}}$ such that
	\begin{align}
		\gamma^{H}_{t;s}\circ\eta_{g}^L\otimes\eta_{g}^R\circ\gamma^{H}_{s;t}&=\Ad{a_2}\circ(\tilde\eta_{g}^L \otimes\tilde\eta_{g}^R)\\
		\gamma^{H_\sigma}_{t;s}\eta_g^\sigma\gamma^{H_\sigma}_{s;t}&=\Ad{a_3}\circ \tilde\eta_{g}^\sigma.
	\end{align}
\end{lemma}
\begin{proof}
\end{proof}
\begin{lemma}\label{lem:AddingAutomorphismsIsContinuous}
	Endow $\Aut{\AA}$ with strong topology then the map
	\begin{equation}
		F:\Aut{\AA}\times\Aut{\AA}\rightarrow\Aut{\AA}:(\xi_1,\xi_2)\mapsto \xi_1\circ\xi_2
	\end{equation}
	is continuous.
\end{lemma}
\begin{proof}
	Take $(\xi_{1,n})_{n\in\NN}$, $(\xi_{2,n})_{n\in\NN}$, $\xi_1$ and $\xi_2$ (all in $\Aut{\AA}$) satisfying
	\begin{align}
		\lim_{n\rightarrow\infty}\xi_{n,1}&=\xi_1&\lim_{n\rightarrow\infty}\xi_{n,2}&=\xi_2.
	\end{align}
	We have to show that
	\begin{equation}
		\lim_{n\rightarrow\infty}\xi_{n,1}\circ\xi_{n,2}=\xi_1\circ\xi_2.
	\end{equation}
	This is equivalent to saying that $\forall a\in\AA:$
	\begin{equation}
		\lim_{n\rightarrow\infty}\norm{\xi_{n,1}\circ\xi_{n,2}(a)-\xi_1\circ\xi_2(a)}=0.
	\end{equation}
	Using the triangle inequality we obtain:
	\begin{align}
		&\norm{\xi_{n,1}\circ\xi_{n,2}(a)-\xi_1\circ\xi_2(a)}\\
		&\leq \norm{\xi_{1,n}\left(\xi_{2,n}(a)-\xi_{2}(a)\right)}+\norm{(\xi_1-\xi_{1,n})(\xi_2(a))}\\
		&=\norm{\xi_{2,n}(a)-\xi_{2}(a)}+\norm{\xi_1(b)-\xi_{1,n}(b)}
	\end{align}
	where $b=\xi_2(a).$ Since both converge to $0$ the result follows.
\end{proof}
\begin{lemma}\label{lem:AdjointIsContinuous}
	Endow $\AA$ with norm topology and $\Aut{\AA}$ with strong topology then the map
	\begin{equation}
		\text{Ad}:\AA\rightarrow \Aut{\AA}:a\mapsto \Ad{a}= a\cdot a^\dagger
	\end{equation}
	is continuous.
\end{lemma}
\begin{proof}
	content...
\end{proof}

\bibliography{TSPT}
\bibliographystyle{plain}
\end{document}